### 2020-04-20 Checkpoint3.Rmd
Create Checkpoint3.Rmd

---
title: "Checkpoint 3"
author: ""
date: '`r format(Sys.Date(), "%B %d, %Y")`'
header-includes:
  - \usepackage{tabularx}
output:
  pdf_document: default
  html_document: default
abstract: ""
---

### 2020-04-20 Checkpoint3.Rmd
Update Checkpoint3.Rmd

@@
 date: '`r format(Sys.Date(), "%B %d, %Y")`'
-header-includes:
-  - \usepackage{tabularx}
 output:
-  pdf_document: default
-  html_document: default
-abstract: ""
+  html_document:
+    toc:true
+    toc_float:true
 ---
+
+## About the Covid-tracking data sets
+https://covidtracking.com/about-data
+https://docs.google.com/spreadsheets/u/2/d/e/2PACX-1vRwAqp96T9sYYq2-i7Tj0pvTf6XVHjDSMIKBdZHXiCGGdNC0ypEU9NbngS8mxea55JuCFuua1MUeOj5/pubhtml

### 2020-04-20 Checkpoint3.Rmd
Update Checkpoint3.Rmd

--- 2020-04-20 Checkpoint3.Rmd
@@
 date: '`r format(Sys.Date(), "%B %d, %Y")`'
-header-includes:
-  - \usepackage{tabularx}
 output:
-  pdf_document: default
-  html_document: default
-abstract: ""
+  html_document:
+    toc:true
+    toc_float:true
 ---
+# Data
+```{r}
+save(states_cases_data, file = 'states_cases_data.RData')
+dim(states_cases_data)
+names(states_cases_data)
+head(states_cases_data)
+summary(states_cases_data)
+```

### 2020-04-21 Demographic_Data_DRAFT/demographics data.Rmd
DATA

---
title: "Project Checkpoint 3"
author: "Sofia Pozsonyiova"
date: "4/20/2020"
output: html_document
---

```{r}
library(dplyr)
political_originaldata <- read.csv("https://www.macalester.edu/~ajohns24/Data/electionDemographics16.csv")

# political %>% select(c(abb, winrep_2016)) %>% filter(abb == "AL")

# political_adjusted <- political %>% 
#    mutate(percent_white = percent_white/100) %>% 
#   mutate(perdem_2016 = perdem_2016/100) %>% 
#   mutate(percent_black = percent_black/100) %>% 
#   mutate(perrep_2016 = perrep_2016/100) %>% 
#   mutate(percent_asian = percent_asian/100) %>%
#   mutate(percent_hispanic = percent_hispanic/100)

Political_totalPopAdju <- political_originaldata %>% 
   mutate(total_white = ((percent_white*total_population)/310810155)) %>% 
  mutate(totaldem_2016 = ((perdem_2016*total_population)/310810155)) %>% 
  mutate(total_black = ((percent_black*total_population)/310810155)) %>% 
  mutate(totalrep_2016 = ((perrep_2016*total_population)/310810155)) %>% 
  mutate(total_asian = ((percent_asian*total_population)/310810155)) %>%
  mutate(total_hispanic = ((percent_hispanic*total_population)/310810155))

demographics_selected <- Political_totalPopAdju %>% select(c(county,percent_white,per_capita_income,abb,total_2016,perdem_2016,percent_black,StateColor,median_rent,dem_2016,perrep_2016,region,percent_asian,median_age,gop_2016,winrep_2016,total_population,percent_hispanic,polyname,StateColor))

Final_demographics_selected <- demographics_selected %>% group_by(polyname) %>% filter(!is.na(polyname)) %>% summarize_if(is.numeric, sum, na.rm=TRUE)

# demographics_adjusted <- demographics_selected_new %>% 
#   mutate(percent_white_adjusted = ((percent_white*total_population)/310810155)) %>% 
#   mutate(percent_democrat2016_adjusted = perdem_2016*.01) %>% 
#   mutate(percent_black_adjusted = percent_black*.01) %>% 
#   mutate(percent_republican2016_adjusted = perrep_2016*.01) %>% 
#   mutate(percent_asian_adjusted = percent_asian*.01) %>%
#   mutate(percent_hispanic_adjusted = percent_hispanic*.01)

#write.csv(demographics_selected, "demographics_selected.csv")
#save(demographics_selected, file = 'demographics_selected.RData')
```

### 2020-04-21 Demographic_Data_/Demographics DataSet.Rmd
updates

---
title: "Demographics"
author: "Sofia Pozsonyiova"
date: "4/21/2020"
output: html_document
---

```{r}
require(choroplethr)
require(dplyr)
require(readr)
```

State Specific Demographics 
```{r}
data("df_state_demographics")
```

Election Data
```{r}
election <- read.csv("https://raw.githubusercontent.com/tonmcg/County_Level_Election_Results_12-16/master/US_County_Level_Presidential_Results_08-16.csv")
election <- election %>% mutate(region = fips_code)
```

County Names + State: 
```{r}
data("df_county_demographics")
RedBlue <- read.csv("https://www.macalester.edu/~ajohns24/Data/RedBluePurple.csv")
```

Combining County and State: (df_county) + redblue 
```{r}
county_level_demographic_data <- left_join(df_county_demographics,RedBlue)
abb_added <- county_level_demographic_data %>% select(polyname,abb,StateColor,region)
```

Combining elect and abb:
```{r}
full_data_county <- left_join(election,abb_added)
County_level_data <- read.csv("/Users/sofiapozsonyiova/Desktop/COVID-19Bayes/Demographic_Data_DRAFT/full_data_by_county.csv")
County_level_data <-County_level_data %>% select(-x)
```

```{r}
county_final <- County_level_data %>% group_by(polyname, abb, StateColor) %>% summarise_if(is.numeric, sum, na.rm = TRUE)
state_demographics <- df_state_demographics %>% mutate(polyname = region) 
state_demographics <- state_demographics %>% select(-region)
county_final <- county_final %>% select(-region)

combineddata <- left_join(county_final,state_demographics, by = "polyname")
combineddata

Demographic_Data_variables <- combineddata %>% 
  select(-c(fips_code,total_2008,dem_2008,gop_2008,oth_2008,total_2012,dem_2012,gop_2012,oth_2012))%>% 
  mutate(percent_white = percent_white/100) %>%
  mutate(percent_black = percent_black/100) %>% 
  mutate(percent_asian = percent_asian/100) %>% 
  mutate(percent_hispanic = percent_hispanic/100) %>% 
  mutate(percent_democrat2016 = dem_2016/total_2016) %>% 
  mutate(percent_republican2016 = gop_2016/total_2016) %>% 
  mutate(percent_other2016 = oth_2016/total_2016) %>% 
  mutate(Winner = ifelse(percent_republican2016 > percent_democrat2016 & percent_republican2016 > percent_other2016, "Republican", "Democrat"))
Demographic_Data_variables
```

### 2020-04-22 Checkpoint3.Rmd

--- 2020-04-20 Checkpoint3.Rmd
@@
 date: '`r format(Sys.Date(), "%B %d, %Y")`'
-header-includes:
-  - \usepackage{tabularx}
 output:
-  pdf_document: default
-  html_document: default
-abstract: ""
+  html_document:
+    toc:true
+    toc_float:true
 ---
+```{r}
+library(dplyr)
+```
+
+# Data
+```{r}
+save(states_cases_data, file = 'states_cases_data.RData')
+dim(states_cases_data)
+names(states_cases_data)
+head(states_cases_data)
+summary(states_cases_data)
+
+```
+
+# Quinn Tries to Plot some stuff
+```{r}
+library(usmap)
+library(maps)
+library(ggplot2)
+library(tidyverse)
+library(ggmap)
+library(viridis)
+
+##Map for Positive Cases (Need to figure out how to make scale more feasible)
+plot_usmap(regions = "state", data=states_cases_data, values = "positive")+
+    labs(title = "Positive COVID-19 Tests") + 
+    theme(panel.background = element_rect(colour = "black"))+
+    scale_fill_continuous(low = "white", high ="darkblue", 
+                          name = "# of Positive Cases",label = scales::comma,
+                          limits = c(0,1000)) + 
+    theme(legend.position = "right") +facet_wrap(~date)
+
+##Map for Positive Cases but only for East Coast 
+plot_usmap(data = states_cases_data, values = "positive", include =  c(.south_atlantic, .mid_atlantic, .new_england ), color = "orange", labels=TRUE) + 
+  scale_fill_continuous( low = "white", high = "orange", 
+                         name = "Positive cases", label = scales::comma
+  ) + 
+  theme(legend.position = "right") + 
+  theme(panel.background = element_rect(colour = "black")) + 
+  labs(title = "US East Coast Positive COVID Cases")
+
+```
+
+```{r}
+### HOW DO i FIX THE SCALE SO THAT OUTLIARS WONT MESS EVERYTHING UP???
+library(statebins)
+statebins(state_data = states_cases_data, state_col = "state",
+                     text_color = "white", value_col = "positive",
+                     brewer_pal="Reds", font_size = 3,breaks =4,
+                     legend_title="# of Positive COVID-19 Cases",
+                 labels = c("0-5000", "5000-10000", "10000-20000", "20000-35000"))
+```

### 2020-04-22 merged data/merging_datasets.Rmd

---
title: "merging_datasets"
author: "Federico Chung"
date: "4/21/2020"
output: html_document
---

```{r}
library(ggplot2)
library(dplyr)
```

```{r}

```

### 2020-04-22 google_search.Rmd

---
title: "google_search"
author: "Federico Chung"
date: "4/21/2020"
output: html_document
---

```{r}
library(ggplot2)
library(dplyr)
```

```{r}
google_search<-read.csv("googlesearch.csv")

```

```{r}
google_search<-google_search%>%
  mutate(Day = paste(as.character(Day),"20",sep =""))%>%
  mutate(Day = as.Date(Day, format = "%m/%d/%Y"))
```

```{r}
ChinaVirus<-google_search%>%
  select(Day,contains("china.virus"))
KungFlu<-google_search%>%
  select(Day,contains("Kung.Flu"))
```

```{r}

states<- read.csv("us_states.csv")

states<-states%>%
  select(Alabama, AL)
states
colnames(states)<-(c("StateName","State"))

alabama<-c(NA,NA)

all_states<- rbind(states,alabama)

all_states

states_final_1<-all_states%>%
  mutate(StateName=as.character(StateName),State = as.character(State))%>%
  replace_na(list(StateName = "Alabama", State = "AL"))

states_final_2<-rbind(states_final_1,alabama)

states_final_2

states_final<-states_final_2%>%
  mutate(StateName=as.character(StateName),State = as.character(State))%>%
  replace_na(list(StateName = "District of Columbia", State = "DC"))%>%
  arrange(State)

states_final

colnames(ChinaVirus) <- c("Day",states_final$State)

Final_ChinaVirus<-ChinaVirus%>%
  gather("State","ChinaVirusInterest",2:ncol(ChinaVirus))

colnames(KungFlu) <- c("Day",states_final$State)

Final_KungFlu<-KungFlu%>%
  gather("State","KungFluInterest",2:ncol(KungFlu))

Time_series_Google<-Final_ChinaVirus%>%
  left_join(Final_KungFlu)

write.csv(Time_series_Google,"Time_series_Google.csv")
```

```{r}
day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
day2<-as.Date("03/24/2020",format = "%m/%d/%Y")

Google_final<-Time_series_Google%>%
  filter(Day<=day2)%>%
  group_by(State)%>%
  summarize(mean_ChinaVirusInterest = mean(ChinaVirusInterest),
            mean_KungFluInterest = mean(KungFluInterest))

write.csv(Google_final,"Google_final.csv")
```

### 2020-04-22 merged data/merging_datasets.Rmd

@@
 ```{r}
+demographic<-read.csv("Demographic_Data.csv")
+covid<-read.csv("states_current.csv")
+stayhome<-read.csv("quarantine.csv")
+google<-read.csv("Google_final.csv")
+```
 
+```{r}
+colnames(demographic)[2] <- "State"
+
+covid<-covid%>%
+  mutate(dateModified = as.Date(substr(dateModified,start = 0,stop = 10)),
+         dateChecked = as.Date(substr(dateChecked,start = 0,stop = 10)))%>%
+  select(-c(notes,hash))
+colnames(covid)[1] <- "State"
+
+stayhome<-stayhome %>% replace_with_na(replace = list(StayAtHome_date = "#N/A"))
+no_na<-subset(stayhome,stayhome$StayAtHome_date!="NA") 
+na<-stayhome%>%
+    anti_join(no_na)%>%
+    mutate(StayAtHome_date =as.Date(as.character(StayAtHome_date),format = "%m-%d-%Y"), na.rm = TRUE)
+no_na1<-no_na%>%
+  mutate(StayAtHome_date =as.Date(as.character(StayAtHome_date),format = "%m/%d/%Y"), na.rm = TRUE)
+stayhomefinal<-rbind(no_na1,na)
+
+all<-demographic%>%
+  left_join(covid)%>%
+  left_join(stayhomefinal)%>%
+  left_join(google)
+
+all
+
+write.csv(all,"FullDataSet.csv")
 ```

### 2020-04-22 Checkpoint3.Rmd

--- 2020-04-20 Checkpoint3.Rmd
@@
 title: "Checkpoint 3"
-author: ""
+author: "Quinn Rafferty, Ferderico Chung, Sofia Pozsonyiova, Will Madairy"
 date: '`r format(Sys.Date(), "%B %d, %Y")`'
@@
 ---
+```{r, warning=FALSE}
+library(dplyr)
+library(usmap)
+library(maps)
+library(ggplot2)
+library(tidyverse)
+library(ggmap)
+library(viridis)
+library(rgdal)
+```
+
 # Data
 ```{r}
-save(states_cases_data, file = 'states_cases_data.RData')
-dim(states_cases_data)
-names(states_cases_data)
-head(states_cases_data)
-summary(states_cases_data)
+save(FullDataSet, file ="FullDataSet.csv")
 ```
+
+```{r}
+dim(FullDataSet)
+names(FullDataSet)
+head(FullDataSet)
+summary(FullDataSet)
+colnames(FullDataSet)
+```

### 2020-04-22 Checkpoint3.Rmd
Update Checkpoint3.Rmd

--- 2020-04-20 Checkpoint3.Rmd
@@
 ---
+
+\
+\
+
+#Libraries
+
+```{r, warning=FALSE}
+library(dplyr)
+library(usmap)
+library(maps)
+library(ggplot2)
+library(tidyverse)
+library(ggmap)
+library(viridis)
+library(rgdal)
+```
+
+\
+\
+
 # Data
 ```{r}
-save(states_cases_data, file = 'states_cases_data.RData')
-dim(states_cases_data)
-names(states_cases_data)
-head(states_cases_data)
-summary(states_cases_data)
+load("FullDataSet.csv")
 ```
+
+Re-Cleaned 
+```{r}
+FullDataSet <- FullDataSet %>% select(-c(median_rent))
+```
+
+##Dataset Description 
+**Put in Data Descriptions Here**
+
+##Dataset Details 
+```{r}
+dim(FullDataSet)
+
+names(FullDataSet)
+
+head(FullDataSet)
+
+summary(FullDataSet)
+
+colnames(FullDataSet)
+```
+
+##Visualizations
+
+\
+\
+
+#Analysis

### 2020-04-22 Checkpoint3.Rmd
Update Checkpoint3.Rmd

@@
 library(rgdal)
+
+require(janitor)
+require(reshape2)
+require(tidyr)
+require(rstan)
+require(rstanarm)
+require(bayesplot)
 ```
@@
 **Put in Data Descriptions Here**
+
+`Demographic:`
+Our dataset, `Demographic`, was created by merging three other datasets which all contained different demographic and election information.
+We obtained the main portion of our demographic data from the US Census Bureau’s American Community Survey (ACS) which is an ongoing survey administered by the U.S.
+Census Bureau.
+It  gathers information on income, employment, housing characteristics, etc, annually for all the 50 U.S.
+States on the county and state level.
+To access the county-level dataset we used the R package called Choroplethr which provides API connections to data sources like the ACS.
+The ACS County-Level dataset was then merged with a county-level election outcome dataset that was created by Tony McGoven.
+Tony’s dataset contained presidential election results for 2008,2012, and 2016 but we chose to focus solely on the most recent election,2016.
+That said, the 2016 election results at the county-level were scraped from results published by Townhall.com.
+However, the State of Alaska reports results at the precinct or state level so there was no county-level data available.
+Therefore, another dataset had to be created that contained the election results for Alaska and this was done using the official election results provided by the Alaska Division of Elections and was later merged in.
+The final dataset that was used came from Alicia Johnson and it contained information on a state’s political leaning.
+Meaning it categorizes each county as belonging to a blue/red/purple state based on the state categorizations at 279towin.
 
@@
 #Analysis
+
+\
+\

### 2020-04-22 Checkpoint3.Rmd

@@
 library(rgdal)
-
-require(janitor)
-require(reshape2)
-require(tidyr)
-require(rstan)
-require(rstanarm)
-require(bayesplot)
 ```
@@
 #Analysis
-
-\
-\

### 2020-04-22 Demographic_Data/Demographics DataSet.Rmd

---
title: "Demographics"
author: "Sofia Pozsonyiova"
date: "4/21/2020"
output: html_document
---

According to Ton MCG...the state of alask resports results at the precinct or state level; no county level data available

```{r message=FALSE, warning=FALSE}
require(choroplethr)
require(dplyr)
require(readr)
```

State Specific Demographics 
```{r message=FALSE, warning=FALSE}
data("df_state_demographics")
```

Election Data
```{r message=FALSE, warning=FALSE}
election <- read.csv("https://raw.githubusercontent.com/tonmcg/County_Level_Election_Results_12-16/master/US_County_Level_Presidential_Results_08-16.csv")
election <- election %>% mutate(region = fips_code)

```

County Names + State: 
```{r message=FALSE, warning=FALSE}
data("df_county_demographics")
RedBlue <- read.csv("https://www.macalester.edu/~ajohns24/Data/RedBluePurple.csv")
```

Combining County and State: (df_county) + redblue 
```{r message=FALSE, warning=FALSE}
county_level_demographic_data <- left_join(df_county_demographics,RedBlue)
abb_added <- county_level_demographic_data %>% select(polyname,abb,StateColor,region)
```

Combining elect and abb:
```{r message=FALSE, warning=FALSE}
full_data_county <- left_join(election,abb_added, by = "region")
County_level_data <- read.csv("/Users/sofiapozsonyiova/Desktop/COVID-19Bayes/Demographic_Data_/full_data_by_county.csv")
County_level_data <-County_level_data 
```

```{r message=FALSE, warning=FALSE}
county_final<- County_level_data %>% group_by(polyname, abb, StateColor) %>% summarise_if(is.numeric, sum, na.rm = TRUE)
state_demographics <- df_state_demographics %>% mutate(polyname = region) 
state_demographics <- state_demographics %>% select(-region)
county_final <- county_final %>% select(-region)

combineddata <- left_join(county_final,state_demographics, by = "polyname")

Demographic_Data_variables <- combineddata %>% 
  select(-c(fips_code,total_2008,dem_2008,gop_2008,oth_2008,total_2012,dem_2012,gop_2012,oth_2012))%>% 
  mutate(percent_white = percent_white/100) %>%
  mutate(percent_black = percent_black/100) %>% 
  mutate(percent_asian = percent_asian/100) %>% 
  mutate(percent_hispanic = percent_hispanic/100) %>% 
  mutate(percent_democrat2016 = dem_2016/total_2016) %>% 
  mutate(percent_republican2016 = gop_2016/total_2016) %>% 
  mutate(percent_other2016 = oth_2016/total_2016) %>% 
  mutate(Winner = ifelse(percent_republican2016 > percent_democrat2016 & percent_republican2016 > percent_other2016, "Republican", "Democrat"))%>% filter(total_2016 != 635888)
#Saving 
#write.csv(Demographic_Data_variables,"Demographic_Data.csv")
```

OUR DATA 
```{r message=FALSE, warning=FALSE}
FinalDemographic <- read.csv("/Users/sofiapozsonyiova/Desktop/COVID-19Bayes/Demographic_Data_/FINALDemographic_Data.csv")
#save(FinalDemographic, file = 'FinalDemographic.RData')
```

Data:

Our dataset, `Demographic`, was created by merging three other datasets which all contained different demographic and election information. We obtained the main portion of our demographic data from the US Census Bureau’s American Community Survey (ACS) which is an ongoing survey administered by the U.S. Census Bureau. It  gathers information on characteristics like income, employment, and housing  annually for all the 50 U.S. States on the county and state level. To access the county-level dataset we used the R package called Choroplethr which provides API connections to data sources like the ACS. The ACS County-Level dataset was then merged with a county-level election outcome dataset that was created by Tony McGoven. Tony’s dataset contained presidential election results for 2008,2012, and 2016 but we chose to focus solely on the most recent election,2016. That said, the 2016 election results at the county-level were scraped from results published by Townhall.com. However, the State of Alaska reports results at the precinct or state level so there was no county-level data available. Therefore, another dataset had to be created that contained the election results for Alaska and this was done using the official election results provided by the Alaska Division of Elections and was later merged in. The final dataset that was used came from Alicia Johnson and it contained information on a state’s political leaning. Meaning it categorizes each county as belonging to a blue/red/purple state based on the state categorizations at 279towin.

Information on the data itself:

```{r message=FALSE, warning=FALSE}
#Dimensions:
dim(FinalDemographic)
#51 Observations and 19 variables

#Variable Names:
names(FinalDemographic)

#Head: 
head(FinalDemographic)

#Summary:
summary(FinalDemographic)
```

+------------------------+---------------------------------------------------+
| Variables:             | Meaning:                                          |
+========================+===================================================+
| `polyname`             | State Name                                        |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `StateColor`           | Political Leaning                                 |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_hispanic`      | Percent of the Population that is Hispanic        |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_white`        | Percent of the Population that is White           |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_asian`        | Percent of the Population that is Asian           |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_black`        | Percent of Population that is Black               |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`total_population`      | Total State Population                            | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`per_capita_income`     | Income per Capita                                 |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_democrat2016`  | Percent of votes won by Democrat (Clinton)        |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_republican2016`| Percent of votes won by Republican (Trump)        | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `Winner`               | Indicator for whether a Republican or Democrat Won| 
|                        |                                                   |  
+------------------------+---------------------------------------------------+
|`total_2016`            | Total Number of Votes                             | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+

```{r message=FALSE, warning=FALSE}
library(choroplethrMaps)
library(usmap)
library(ggplot2)

mapdata <- FinalDemographic %>% mutate(state = polyname)

# plot_usmap(data = dat_sub, values = 'total.receipts', color = "red") + 
#   scale_fill_continuous(low = "white", high = "blue", name = "Total Receipts", label = scales::comma) + theme(legend.position = "right") + facet_wrap(~party) 
```

Visualizations: 
```{r, warning=FALSE}
#Demographic: Identification 
plot_usmap(data = mapdata, values = "percent_white", color = "white") + 
  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") + 
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

plot_usmap(data = mapdata, values = "percent_asian", color = "white") + 
  scale_fill_continuous( name = "Percent Asian", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") + 
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

plot_usmap(data = mapdata, values = "percent_asian", color = "white") + 
  scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") +
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
) 
```
The above visualization is looking at the percent of residents that identify as Asian within the United States. This information is valuable to us since we are trying to understand ___. As you can see, there is a higher percent of residents that identify as Asian in places like California and Washington, but the most being in Hawaii. From this visualization we can also see that that Midwest and the South tend to have a small percentage of residents identifying as Asian.

Polling Visualizations: 
```{r, warning=FALSE}
#By Results 
plot_usmap(data = mapdata, values = "percent_asian", color = "white") + 
  scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent Asian by General Election Results")+
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
) + facet_wrap(~Winner)

#By income 
plot_usmap(data = mapdata, values = "per_capita_income", color = "white") + 
  scale_fill_continuous(low = "sky blue", high = "black", name = "$ Per Capita", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent Capita Income")+
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
) 
```

```{r}
ggplot(mapdata, aes(x = percent_republican2016, fill = StateColor)) + 
    geom_density(alpha = 0.5) + 
    scale_fill_manual(values = c("blue","purple","red")) +ggtitle("Trump Support by State Affiliation") + xlab("Trump Support")+ylab("Density")

ggplot(mapdata, aes(x = percent_asian, y = percent_republican2016, color = StateColor)) + 
    geom_point(alpha = 0.5) + 
    scale_color_manual(values = c("blue","purple","red")) + 
    facet_wrap( ~ Winner) + ggtitle("Percent of Asians and Trump Support by Election Outcome") + xlab("Percent Asian") + ylab("Trump Support")

ggplot(mapdata, aes(x = percent_asian, y = percent_republican2016, color = Winner)) + 
    scale_color_manual(values = c("blue","purple","red")) + 
    geom_point(alpha = 0.8) + geom_text(aes(label=ifelse(percent_asian>.2,as.character(state),"")),hjust=1.2,vjust=0)+ geom_text(aes(label=ifelse(percent_republican2016<.2,as.character(state),"")),hjust=-.1,vjust=0) + ggtitle("Percent of Asians and Trump Support by Election Outcome") + xlab("Percent Asian") + ylab("Trump Support")

ggplot(mapdata, aes(x = per_capita_income)) + 
    geom_density()+ ggtitle("Per Capita Income") + xlab("Per Capita Income") + ylab("Density") + facet_wrap(~Winner)
```
Univariate Plots
```{r}
ggplot(mapdata, aes(x = percent_republican2016)) + 
    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density")

ggplot(mapdata, aes(x = percent_republican2016)) + 
    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density")

ggplot(mapdata, aes(x = percent_republican2016)) + 
    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density") + facet_wrap(~StateColor)

ggplot(mapdata, aes(x = per_capita_income)) + 
    geom_density()+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")

ggplot(mapdata, aes(x = per_capita_income, fill = StateColor)) + 
    geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")
```

### 2020-04-22 merged data/merging_datasets.Rmd

@@
 library(dplyr)
+library(naniar)
 ```
@@
 ```{r}
-demographic<-read.csv("Demographic_Data.csv")
-covid<-read.csv("states_current.csv")
+demographic<-read.csv("FINALDemographic_Data.csv")
+covid<-read.csv("states_cases_data.csv")
 stayhome<-read.csv("quarantine.csv")
@@
 
-covid<-covid%>%
-  mutate(dateModified = as.Date(substr(dateModified,start = 0,stop = 10)),
-         dateChecked = as.Date(substr(dateChecked,start = 0,stop = 10)))%>%
-  select(-c(notes,hash))
-colnames(covid)[1] <- "State"
+colnames(covid)[2] <- "State"
 
@@
 write.csv(all,"FullDataSet.csv")
+names(all)
 ```

### 2020-04-22 Checkpoint3.Rmd
Update Checkpoint3.Rmd
f

--- 2020-04-22 Checkpoint3.Rmd
@@
 ```{r}
-load("FullDataSet.csv")
+Finaldata<- read.csv("FinalDataSet.csv")
 ```
@@
 ```{r}
-FullDataSet <- FullDataSet %>% select(-c(median_rent))
+Finaldata <- Finaldata %>% select(-c(X,X.1)) 
 ```
@@
 ```{r}
-dim(FullDataSet)
+dim(Finaldata)
 
-names(FullDataSet)
+names(Finaldata)
 
-head(FullDataSet)
+head(Finaldata)
 
-summary(FullDataSet)
+summary(Finaldata)
 
-colnames(FullDataSet)
+colnames(Finaldata)
 ```
 
+##Variables of Interest
+
++------------------------+---------------------------------------------------+
+| Variables:             | Meaning:                                          |
++========================+===================================================+
+| `polyname`             | State Name                                        |
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+| `StateColor`           | Political Leaning                                 |
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`percent_hispanic`      | Percent of the Population that is Hispanic        |
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+| `percent_white`        | Percent of the Population that is White           |
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+| `percent_asian`        | Percent of the Population that is Asian           |  
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+| `percent_black`        | Percent of Population that is Black               |  
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`total_population`      | Total State Population                            | 
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`per_capita_income`     | Income per Capita                                 |
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`percent_democrat2016`  | Percent of votes won by Democrat (Clinton)        |  
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`percent_republican2016`| Percent of votes won by Republican (Trump)        | 
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+| `Winner`               | Indicator for whether a Republican or Democrat Won| 
+|                        |                                                   |  
++------------------------+---------------------------------------------------+
+|`total_2016`            | Total Number of Votes                             | 
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+
 ##Visualizations
+
+###Demographic 
+```{r}
+#Demographic: Identification 
+Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
+plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
+  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
+  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") + 
+  theme(
+plot.title = element_text(color="Black", size=14, face="bold")
+)
+
+plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
+  scale_fill_continuous( name = "Percent Asian", label = scales::comma) + 
+  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") + 
+  theme(
+plot.title = element_text(color="Black", size=14, face="bold")
+)
+
+plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
+  scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
+  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") +
+  theme(
+plot.title = element_text(color="Black", size=14, face="bold")
+)
+
+#By Results 
+plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
+  scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
+  theme(legend.position = "right") + ggtitle("Percent Asian by General Election Results")+
+  theme(
+plot.title = element_text(color="Black", size=14, face="bold")
+) + facet_wrap(~Winner)
+
+#By income 
+plot_usmap(data = Finaldata, values = "per_capita_income", color = "white") + 
+  scale_fill_continuous(low = "sky blue", high = "black", name = "$ Per Capita", label = scales::comma) + 
+  theme(legend.position = "right") + ggtitle("Percent Capita Income")+
+  theme(
+plot.title = element_text(color="Black", size=14, face="bold")
+)
+
+ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + 
+    geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")
+
+ggplot(Finaldata, aes(x = per_capita_income)) + 
+    geom_density()+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")
+
+ggplot(Finaldata, aes(x = percent_republican2016)) + 
+    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density")
+
+ggplot(Finaldata, aes(x = percent_republican2016)) + 
+    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density") + facet_wrap(~StateColor)
+
+ggplot(Finaldata, aes(x = percent_asian, y = percent_republican2016, color = Winner)) + 
+    scale_color_manual(values = c("blue","purple","red")) + 
+    geom_point(alpha = 0.8) + geom_text(aes(label=ifelse(percent_asian>.2,as.character(state),"")),hjust=1.2,vjust=0)+ geom_text(aes(label=ifelse(percent_republican2016<.2,as.character(state),"")),hjust=-.1,vjust=0) + ggtitle("Percent of Asians and Trump Support by Election Outcome") + xlab("Percent Asian") + ylab("Trump Support")
+
+ggplot(Finaldata, aes(x = per_capita_income)) + 
+    geom_density()+ ggtitle("Per Capita Income") + xlab("Per Capita Income") + ylab("Density") + facet_wrap(~Winner)
+```
 

### 2020-04-22 Checkpoint3.Rmd
Update Checkpoint3.Rmd

@@
 plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
-  scale_fill_continuous( name = "Percent Asian", label = scales::comma) + 
-  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") + 
-  theme(
-plot.title = element_text(color="Black", size=14, face="bold")
-)
-
-plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
   scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
@@
 
+#Income by state affiliation 
 ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + 
@@
 
-ggplot(Finaldata, aes(x = per_capita_income)) + 
-    geom_density()+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")
-
+#Trump Support 
 ggplot(Finaldata, aes(x = percent_republican2016)) + 
     geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density")
-
-ggplot(Finaldata, aes(x = percent_republican2016)) + 
-    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density") + facet_wrap(~StateColor)
 

### 2020-04-22 Checkpoint3.Rmd
regions
regions

@@
 ```{r}
-Finaldata <- Finaldata %>% select(-c(X,X.1)) 
+Finaldata <- Finaldata %>% select(-c(X,X.1)) %>% 
+  mutate(Region = ifelse(State %in% c("AK","CA","OR","WA","HI"), "West", ifelse(State %in% c("CO","UT","ID","MT","WY", "NM", "AZ", "NV"), "Mountain", ifelse(State %in% c("SD","ND","MN","KS","IN", "MI", "NE", "IA", "WI","IL", "OH", "MO", "OK"), "Midwest",  ifelse(State %in% c("TX","AL","MS","FL","AR", "WV", "TN", "NC", "SC","GA", "VA", "KY", "LA"), "South", ifelse(State %in% c("MD","PA","DE","NJ","NY", "MA", "CT", "NH", "VT","ME", "RI", "DC"), "Northeast", 0))))))
 ```
@@
 
+$$
+
+$$
+
 \

### 2020-04-22 Checkpoint3.Rmd
analysis

@@
 title: "Checkpoint 3"
-author: "Quinn Rafferty, Ferderico Chung, Sofia Pozsonyiova, Will Madairy"
-date: '`r format(Sys.Date(), "%B %d, %Y")`'
+author: "Quinn Rafferty, Sofia Pozsonyiova, Will Madairy, Federico Chung"
+date: ""
 output: 
   html_document:
-    toc:true
-    toc_float:true
+    toc: true
+    toc_float: true
 ---
@@
 
-$$
+```{r}
+# Take a sub-sample of the data
+set.seed(84735)
+test1 <- Finaldata %>% 
+  select(mean_KungFluInterest, percent_republican2016, percent_asian, StateColor) %>%
+  na.omit() %>% 
+  sample_n(500)
 
-$$
+names(test1) <- tolower(names(test1))
+
+test1
+```
+
+```{r}
+set.seed(454)
+building_mod <- stan_glm(
+  mean_kungfluinterest ~ percent_republican2016 + percent_asian +statecolor, 
+  data = test1, 
+  family = gaussian, 
+  chains = 4, iter = 10000
+)
+```
+
+```{r}
+mcmc_trace(building_mod)
+mcmc_dens_overlay(building_mod)
+```
+
+```{r}
+pp_check(building_mod)
+```
+
+```{r}
+summary_building_mod <- summary(building_mod)
+
+head(as.data.frame(summary_building_mod),-2)
+```
+
+```{r}
+prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
+  # Calculate summary statistics of simulated 
+  # posterior predictive models for each case
+  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
+  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
+  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
+  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
+  df <- data.frame(yrep) %>% 
+    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
+    unlist() %>% 
+    matrix(., length(y), 8) %>% 
+    data.frame()
+  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
+  data.frame(cbind(y, df))
+}
+
+prediction_summary <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
+  # This function summarizes the predictions across all cases
+  pred_data <- prediction_summary_data(y, yrep, prob_inner = prob_inner, prob_outer = prob_outer) %>% 
+    mutate(error = y - post_median) %>% 
+    mutate(error_scaled = error / post_mad) %>% 
+    mutate(within_inner = (y >= l_inner) & (y <= u_inner)) %>% 
+    mutate(within_outer = (y >= l_outer) & (y <= u_outer))
+
+  pred_summary <- pred_data %>% 
+    summarize(mae = median(abs(error)), 
+      mae_scaled = median(abs(error_scaled)),
+      within_inner = mean(within_inner),
+      within_outer = mean(within_outer)
+    )
+  names(pred_summary)[3] <- paste0("within_", prob_inner*100)
+  names(pred_summary)[4] <- paste0("within_", prob_outer*100)
+
+  pred_summary
+}
+```
+
+```{r}
+preds <- posterior_predict(building_mod,newdata = test1) # Ask Alicia 
+prediction_summary(y = test1$mean_kungfluinterest, yprep = preds)
+
+```
 

### 2020-04-23 Checkpoint3.Rmd
update table

@@
 +------------------------+---------------------------------------------------+
-| Variables:             | Meaning:                                          |
+| Variables:             | Description:                                      |
 +========================+===================================================+
@@
 |                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`Positive`              | Number of reported positive COVID-19 cases        | 
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`Negative`              | Number of reported negative COVID-19 cases        | 
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`date`                  | Date of report                                    | 
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`death`                 | Total Number of reported deaths due to COVID-19   | 
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`hospitalized`          | Total Number of indivudals hopitalized due        |
+|                        | to COVID-19                                       |
++------------------------+---------------------------------------------------+
+|`totalTestResults`      | Total Number test results (Positive +Negative)    | 
+|                        |                                                   | 
++------------------------+---------------------------------------------------+
+|`FIPS`                  | A five-digit Federal Information Processing       |
+|                        | Standards code which uniquely identified counties |
+|                        | and county                                        | 
 +------------------------+---------------------------------------------------+

### 2020-04-23 Checkpoint3.Rmd
Adding visualizations

@@
 
-###Demographic 
+### Demographic 
 ```{r}
@@
 
+### COVID-19 Cases
+
+```{r}
+## Creating a df of just the cases the week before 3/17
+weekbefore <- data.frame(states_cases_data) %>% filter(date <= as.Date("2020-03-17"))
+
+plot1<- plot_usmap(data = weekbefore, values = "positive", color = "white") + 
+  scale_fill_continuous(name = "Cases", label = scales::comma) + 
+  theme(legend.position = "right")+ ggtitle("# of COVID Cases Before 3/17") + 
+  theme(
+plot.title = element_text(color="Black", size=8)
+)
+
+## Creating a df of just the cases the week after 3/17
+weekafter <- data.frame(states_cases_data) %>% filter(date >= as.Date("2020-03-17"))
+
+plot2<-plot_usmap(data = weekafter, values = "positive", color = "white") + 
+  scale_fill_continuous(name = "Cases", label = scales::comma) + 
+  theme(legend.position = "right")+ ggtitle("# of COVID Cases After 3/17") + 
+  theme(
+plot.title = element_text(color="Black", size=5)
+)
+
+# The number of Positive Covid Cases, comparison before and after the China Virus announcement 
+grid.arrange(plot1, plot2, ncol=2)
+```
+
+```{r}
+# 
+ggplot(Finaldata, aes(x = positive, fill = StateColor)) + 
+    geom_density(alpha = .8)+ ggtitle("Positive COVID-19 Cases by State Party") + xlab("Cases") + ylab("Density")+xlim(0,500)
+```
+
+```{r}
+library(statebins)
+plot3<-statebins(state_data = weekbefore, state_col = "state",
+                     text_color = "white", value_col = "positive",
+                     brewer_pal="Spectral", font_size = 2,breaks =7,
+                     legend_title="Week Before",
+                 labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))
+
+### Drastic scale change, needs work for comparison sake
+plot4<-statebins(state_data = weekafter, state_col = "state",
+                     text_color = "white", value_col = "positive",
+                     brewer_pal="Spectral", font_size = 3,breaks =6,
+                     legend_title="Week After",labels = c("1-100", "100-500", "500-5000", "5000-15000", "15000-25000", "25000-35000"))
+
+plot3
+plot4
+```
+
 \
@@
 
-#Analysis
+# Analysis
 
 ```{r}
-# Take a sub-sample of the data
 set.seed(84735)
@@
 
-```{r}
+```{r, include=FALSE}
 prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){

### 2020-04-23 Checkpoint3.Rmd
fed's graph
keep the range

@@
 \
+
+```{r}
+google_ts<-read.csv("Time_series_Google.csv")
+
+day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
+day2<-as.Date("03/24/2020",format = "%m/%d/%Y")
+
+google_ts_reg<-google_ts_reg%>%
+  mutate(Day = as.Date(as.character(Day)))
+
+a<-google_ts_reg %>% 
+  #filter(Day<=day2)%>%
+  #filter(Day>=day1)%>%
+  group_by(Region, Day) %>% 
+  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
+  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
+  geom_point()
+
+ggplotly(a)
+```

### 2020-04-23 Checkpoint3.Rmd
adding data description

--- 2020-04-23 Checkpoint3.Rmd
@@
 library(rgdal)
+library(gridExtra)
 
@@
 Meaning it categorizes each county as belonging to a blue/red/purple state based on the state categorizations at 279towin.
+
+`COVID-19 Cases`
+The COVID-19 data is provided by The COVID Tracking Project(CTP).
+All of the  data points come from state/district/territory public health authorities—or, occasionally, from trusted news reporting, official press conferences, or (very occasionally) tweets or Facebook updates from state public health authorities or governors.
+These numbers are updated daily at 4PM EST.
+The biggest weakness of this dataset is that there is no standardized methods for states to follow for data collection/report.
+For example, some states, like Oregon, provide the **full** set of numbers but others provide some or none of these numbers on an ongoing basis.
+Some crucial states in this outbreak, notably California, Washington, and New York, have not been regularly reporting their total number of people tested.
+The CTP aims to remedy this uncertainty in states by utilizing other reporting/measuring tools such as: "Directly asking state officials, watching news conferences, gleaning information from trusted news sources, and whatever else it takes to present reliable numbers."
 
@@
                      text_color = "white", value_col = "positive",
-                     brewer_pal="Spectral", font_size = 2,breaks =7,
+                     brewer_pal="Spectral", font_size = 3,breaks =7,
                      legend_title="Week Before",
@@
 pp_check(building_mod)
+
+# Could build like the sleep study, 50 frames one for each state and how Google Trends changed over time, each state has its own trajectory
+# Can we look at each state and how their interest changes over time and if that's related to how many cases are in the state
+
+#What's the trend in interest and how does it depend on cases? 
 ```

### 2020-04-23 Google/BayesCap-Will.Rmd

---
title: "BayesCap-Will"
author: "Will Madairy"
date: "4/21/2020"
output: html_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(ggplot2)
```

```{r}
googledata<-read.csv("/Users/willmadairy/Documents/BayesData/Alaska.csv")
```
```{r}
write.csv(googledata, "/Users/willmadairy/Documents/BayesData/googlesearch.csv")
```

```{r}
google_ts<-read.csv("/Users/willmadairy/Documents/GitHub/COVID-19Bayes/Google/Time_series_Google.csv")
```

```{r}
google_ts_reg<-google_ts %>% 
  mutate(Region = ifelse(State %in% c("AK","CA","OR","WA","HI"), "West", ifelse(State %in% c("CO","UT","ID","MT","WY", "NM", "AZ", "NV"), "Mountain", ifelse(State %in% c("SD","ND","MN","KS","IN", "MI", "NE", "IA", "WI","IL", "OH", "MO", "OK"), "Midwest",  ifelse(State %in% c("TX","AL","MS","FL","AR", "WV", "TN", "NC", "SC","GA", "VA", "KY", "LA"), "South", ifelse(State %in% c("MD","PA","DE","NJ","NY", "MA", "CT", "NH", "VT","ME", "RI", "DC"), "Northeast", 0))))))
```

This set of data looks at the interest in

```{r}
google_ts %>% 
  ggplot(aes(x=Day, y=ChinaVirusInterest, color=State)) + 
  geom_point()
```
```{r}
google<-google_ts_reg %>% 
  mutate(date = mdy(Day))
```

```{r}
google_ts_reg %>% 
  group_by(Region, Day) %>% 
  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
  geom_point()
```

### 2020-04-23 Checkpoint3.Rmd
push
Update Checkpoint3.Rmd
adding google descriptions

@@
 |                        | and county                                        | 
++------------------------+---------------------------------------------------+
+|`KungFluInterest`       | Interest index from google searches by state.     |
+|                        | Peak search day=100, all other days in set are    |
+|                        | based searches on relative to this peak day.      | 
++------------------------+---------------------------------------------------+
+|`ChinaVirusInterest`    | Interest index from google searches by state.     |
+|                        | Peak search day=100, all other days in set are    |
+|                        | based searches on relative to this peak day.      | 
 +------------------------+---------------------------------------------------+
@@
 ```{r}
+library(plotly)
 google_ts<-read.csv("Time_series_Google.csv")

### 2020-04-23 Checkpoint3.Rmd
add csv and visuals
Added regional csv and visuals to rmd

@@
 Finaldata<- read.csv("FinalDataSet.csv")
+```
+```{r}
+google<-read.csv("Google/googlefinal.csv")
 ```
@@
 ##Visualizations 
+```{r}
+google %>% 
+  group_by(Region, Day) %>% 
+  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
+  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
+  geom_point()
+```
 

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd

@@
 author: "Quinn Rafferty, Sofia Pozsonyiova, Will Madairy, Federico Chung"
-date: ""
+date: "4/24/2020"
 output: 
@@
 ##Dataset Description
-**Put in Data Descriptions Here**
 
@@
 ## Creating a df of just the cases the week before 3/17
-weekbefore <- data.frame(states_cases_data) %>% filter(date <= as.Date("2020-03-17"))
+weekbefore <- data.frame(Finaldata) %>% filter(date <= as.Date("2020-03-17"))
 
@@
 ## Creating a df of just the cases the week after 3/17
-weekafter <- data.frame(states_cases_data) %>% filter(date >= as.Date("2020-03-17"))
+weekafter <- data.frame(Finaldata) %>% filter(date >= as.Date("2020-03-17"))
 
@@
 ```{r}
-# 
+# Positive COVID cases aggregated by party 
 ggplot(Finaldata, aes(x = positive, fill = StateColor)) + 
@@
 ```{r}
+## Positive COVID cases map before and after week 
 library(statebins)

### 2020-04-23 Checkpoint3.Rmd
pull

@@
 ```{r}
-Finaldata<- read.csv("FinalDataSet.csv")
+Finaldata<- read.csv("time_series_final_Data.csv")
 ```
+
 ```{r}
@@
 ```{r}
-Finaldata <- Finaldata %>% select(-c(X,X.1)) %>% 
-  mutate(Region = ifelse(State %in% c("AK","CA","OR","WA","HI"), "West", ifelse(State %in% c("CO","UT","ID","MT","WY", "NM", "AZ", "NV"), "Mountain", ifelse(State %in% c("SD","ND","MN","KS","IN", "MI", "NE", "IA", "WI","IL", "OH", "MO", "OK"), "Midwest",  ifelse(State %in% c("TX","AL","MS","FL","AR", "WV", "TN", "NC", "SC","GA", "VA", "KY", "LA"), "South", ifelse(State %in% c("MD","PA","DE","NJ","NY", "MA", "CT", "NH", "VT","ME", "RI", "DC"), "Northeast", 0))))))
+Finaldata <- Finaldata %>% select(-c(X))
 ```

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd

@@
 Finaldata <- Finaldata %>% select(-c(X)) 
+Finaldata <- Finaldata %>% mutate(as.Date(Day))
 ```
@@
 ## Creating a df of just the cases the week before 3/17
-weekbefore <- data.frame(Finaldata) %>% filter(date <= as.Date("2020-03-17"))
+weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.character(as.Date("2020-03-17")))
 
@@
 ## Creating a df of just the cases the week after 3/17
-weekafter <- data.frame(Finaldata) %>% filter(date >= as.Date("2020-03-17"))
+weekafter <- data.frame(Finaldata) %>% filter(Day >= as.Date("2020-03-17"))
 

### 2020-04-23 Checkpoint3.Rmd
changes

@@
 Finaldata <- Finaldata %>% select(-c(X)) 
-Finaldata <- Finaldata %>% mutate(as.Date(Day))
+Finaldata <- Finaldata %>% mutate(Day = as.Date(as.character(Day)))
 ```
@@
 ## Creating a df of just the cases the week before 3/17
-weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.character(as.Date("2020-03-17")))
+day1<-as.Date("2020-03-17")
+weekbefore <- Finaldata %>% filter(Day <= day1)
+
+Finaldata %>% 
+  filter(Day <= day1)
 

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd

--- 2020-04-23 Checkpoint3.Rmd
@@
 ##Visualizations 
-```{r}
+```{r echo=FALSE}
 google %>% 

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd

--- 2020-04-23 Checkpoint3.Rmd
@@
 Finaldata <- Finaldata %>% select(-c(X)) 
-Finaldata <- Finaldata %>% mutate(Day = as.Date(as.character(Day)))
+Finaldata <- Finaldata %>% mutate(as.Date(Day))
 ```
@@
 ## Creating a df of just the cases the week before 3/17
-day1<-as.Date("2020-03-17")
-weekbefore <- Finaldata %>% filter(Day <= day1)
-
-Finaldata %>% 
-  filter(Day <= day1)
+weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.character(as.Date("2020-03-17")))
 
@@
 plot4
+```
+
+## Final Dataset
+```{r}
+ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
+  geom_density(alpha = 0.5)
 ```

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd
Googele descript

--- 2020-04-23 Checkpoint3.Rmd
@@
 The CTP aims to remedy this uncertainty in states by utilizing other reporting/measuring tools such as: "Directly asking state officials, watching news conferences, gleaning information from trusted news sources, and whatever else it takes to present reliable numbers."
+
+`Google Search Interest`
+This data set includes two search interest indexes over time, measuring how people in each of the state’s interest in searching either “Kung Flu” or “China Virus” based on the time frame selected in the search.
+This data is downloaded directly from Google Trends which uses the same technique to track the interest of all searches on the platform.
+The main downside to this data set is the method of the indexing which makes the comparison from state to state less meaningful since each state is guaranteed to have a 100-level interest on their peak day, and the actual unknown search values can vary greatly across different states.
 

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd

--- 2020-04-23 Checkpoint3.Rmd
@@
   geom_density(alpha = 0.5)
+
 ```
-
+```{r}
+ggplot(Finaldata, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
+    geom_point() + 
+    geom_smooth(method = "lm", se = FALSE) + 
+    facet_wrap(~ State) + 
+    theme(legend.position = "none")
+```
 \
@@
 \
-
-```{r}
-library(plotly)
-google_ts<-read.csv("Time_series_Google.csv")
-
-day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
-day2<-as.Date("03/24/2020",format = "%m/%d/%Y")
-
-google_ts_reg<-google_ts_reg%>%
-  mutate(Day = as.Date(as.character(Day)))
-
-a<-google_ts_reg %>% 
-  #filter(Day<=day2)%>%
-  #filter(Day>=day1)%>%
-  group_by(Region, Day) %>% 
-  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
-  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
-  geom_point()
-
-ggplotly(a)
-```

### 2020-04-23 Checkpoint3.Rmd

@@
 google<-read.csv("Google/googlefinal.csv")
+names(google)
 ```
@@
 ```{r} 
+google <- google %>%  select(-c(X.1))
 Finaldata <- Finaldata %>% select(-c(X)) 
@@
 ```{r}
-google %>% 
+library(plotly)
+#google_ts<-read.csv("Time_series_Google.csv")
+
+day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
+day2<-as.Date("03/24/2020",format = "%m/%d/%Y")
+
+google_ts<-google%>%
+  mutate(Day = as.Date(as.character(Day)))
+
+a<-google_ts %>% 
+  #filter(Day<=day2)%>%
+  #filter(Day>=day1)%>%
   group_by(Region, Day) %>% 
@@
   geom_point()
+
+ggplotly(a)
 ```
@@
 ## Positive COVID cases map before and after week 
-library(statebins)
-plot3<-statebins(state_data = weekbefore, state_col = "state",
+plot3<-statebins(state_data = weekbefore, state_col = "State",
                      text_color = "white", value_col = "positive",

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd

@@
 require(bayesplot)
+```
+
+\
+\
+
+#Functions
+
+```{r, include=FALSE}
+prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
+  # Calculate summary statistics of simulated 
+  # posterior predictive models for each case
+  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
+  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
+  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
+  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
+  df <- data.frame(yrep) %>% 
+    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
+    unlist() %>% 
+    matrix(., length(y), 8) %>% 
+    data.frame()
+  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
+  data.frame(cbind(y, df))
+}
+
+prediction_summary <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
+  # This function summarizes the predictions across all cases
+  pred_data <- prediction_summary_data(y, yrep, prob_inner = prob_inner, prob_outer = prob_outer) %>% 
+    mutate(error = y - post_median) %>% 
+    mutate(error_scaled = error / post_mad) %>% 
+    mutate(within_inner = (y >= l_inner) & (y <= u_inner)) %>% 
+    mutate(within_outer = (y >= l_outer) & (y <= u_outer))
+
+  pred_summary <- pred_data %>% 
+    summarize(mae = median(abs(error)), 
+      mae_scaled = median(abs(error_scaled)),
+      within_inner = mean(within_inner),
+      within_outer = mean(within_outer)
+    )
+  names(pred_summary)[3] <- paste0("within_", prob_inner*100)
+  names(pred_summary)[4] <- paste0("within_", prob_outer*100)
+
+  pred_summary
+}
 ```
@@
 Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
-plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
-  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
-  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") + 
-  theme(
-plot.title = element_text(color="Black", size=14, face="bold")
-)
 
@@
 
-#By Results 
-plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
-  scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
-  theme(legend.position = "right") + ggtitle("Percent Asian by General Election Results")+
-  theme(
-plot.title = element_text(color="Black", size=14, face="bold")
-) + facet_wrap(~Winner)
-
-#By income 
-plot_usmap(data = Finaldata, values = "per_capita_income", color = "white") + 
-  scale_fill_continuous(low = "sky blue", high = "black", name = "$ Per Capita", label = scales::comma) + 
-  theme(legend.position = "right") + ggtitle("Percent Capita Income")+
-  theme(
-plot.title = element_text(color="Black", size=14, face="bold")
-)
-
 #Income by state affiliation 
 ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + 
-    geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")
+    geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density") +scale_fill_manual(values=c("blue", "purple", "red"))
 
 #Trump Support
-ggplot(Finaldata, aes(x = percent_republican2016)) + 
-    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density")
+
+plot_usmap(data = Finaldata, values = "percent_republican2016", color = "white") + 
+  scale_fill_continuous(low = "sky blue", high = "black", name = "Trump Support", label = scales::comma) + 
+  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") +
+  theme(plot.title = element_text(color="Black", size=14, face="bold"))
 
@@
 
-ggplot(Finaldata, aes(x = per_capita_income)) + 
-    geom_density()+ ggtitle("Per Capita Income") + xlab("Per Capita Income") + ylab("Density") + facet_wrap(~Winner)
 ```
@@
 
-```{r}
+```{r echo=FALSE}
 ## Creating a df of just the cases the week before 3/17
+#Scale.fill color manual ??? so to go from green to red
 weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.character(as.Date("2020-03-17")))
@@
 ```
+
 ```{r}
@@
     geom_smooth(method = "lm", se = FALSE) + 
-    facet_wrap(~ State) + 
+    facet_wrap(~ Region) + 
     theme(legend.position = "none")
@@
 
-```{r, include=FALSE}
-prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
-  # Calculate summary statistics of simulated 
-  # posterior predictive models for each case
-  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
-  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
-  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
-  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
-  df <- data.frame(yrep) %>% 
-    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
-    unlist() %>% 
-    matrix(., length(y), 8) %>% 
-    data.frame()
-  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
-  data.frame(cbind(y, df))
-}
-
-prediction_summary <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
-  # This function summarizes the predictions across all cases
-  pred_data <- prediction_summary_data(y, yrep, prob_inner = prob_inner, prob_outer = prob_outer) %>% 
-    mutate(error = y - post_median) %>% 
-    mutate(error_scaled = error / post_mad) %>% 
-    mutate(within_inner = (y >= l_inner) & (y <= u_inner)) %>% 
-    mutate(within_outer = (y >= l_outer) & (y <= u_outer))
-
-  pred_summary <- pred_data %>% 
-    summarize(mae = median(abs(error)), 
-      mae_scaled = median(abs(error_scaled)),
-      within_inner = mean(within_inner),
-      within_outer = mean(within_outer)
-    )
-  names(pred_summary)[3] <- paste0("within_", prob_inner*100)
-  names(pred_summary)[4] <- paste0("within_", prob_outer*100)
-
-  pred_summary
-}
-```
+\
+\
 
@@
 ```
-
-\
-\

### 2020-04-23 Checkpoint3.Rmd
stuff

--- 2020-04-23 Checkpoint3.Rmd
@@
 Finaldata <- Finaldata %>% select(-c(X)) 
-Finaldata <- Finaldata %>% mutate(as.Date(Day))
+Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
 ```
@@
 ## Creating a df of just the cases the week before 3/17
-weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.character(as.Date("2020-03-17")))
+weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.Date("2020-03-17"))
 
@@
 ```{r}
-## Positive COVID cases map before and after week 
-plot3<-statebins(state_data = weekbefore, state_col = "State",
-                     text_color = "white", value_col = "positive",
-                     brewer_pal="Spectral", font_size = 3,breaks =7,
-                     legend_title="Week Before",
-                 labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))
-
-### Drastic scale change, needs work for comparison sake
-plot4<-statebins(state_data = weekafter, state_col = "state",
-                     text_color = "white", value_col = "positive",
-                     brewer_pal="Spectral", font_size = 3,breaks =6,
-                     legend_title="Week After",labels = c("1-100", "100-500", "500-5000", "5000-15000", "15000-25000", "25000-35000"))
-
-plot3
-plot4
+# ## Positive COVID cases map before and after week 
+# plot3<-statebins(state_data = weekbefore, state_col = "State",
+#                      text_color = "white", value_col = "positive",
+#                      brewer_pal="Spectral", font_size = 3,breaks =7,
+#                      legend_title="Week Before",
+#                  labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))
+# 
+# ### Drastic scale change, needs work for comparison sake
+# plot4<-statebins(state_data = weekafter, state_col = "state",
+#                      text_color = "white", value_col = "positive",
+#                      brewer_pal="Spectral", font_size = 3,breaks =6,
+#                      legend_title="Week After",labels = c("1-100", "100-500", "500-5000", "5000-15000", "15000-25000", "25000-35000"))
+# 
+# plot3
+# plot4
 ```
@@
 # Analysis
-
-```{r}
-set.seed(84735)
-test1 <- Finaldata %>% 
-  select(mean_KungFluInterest, percent_republican2016, percent_asian, StateColor) %>%
-  na.omit() %>% 
-  sample_n(500)
-
-names(test1) <- tolower(names(test1))
-
-test1
-```
-
-```{r}
-set.seed(454)
-building_mod <- stan_glm(
-  mean_kungfluinterest ~ percent_republican2016 + percent_asian +statecolor, 
-  data = test1, 
-  family = gaussian, 
-  chains = 4, iter = 10000
-)
-```
-
-```{r}
-mcmc_trace(building_mod)
-mcmc_dens_overlay(building_mod)
-```
-
-```{r}
-pp_check(building_mod)
-
-# Could build like the sleep study, 50 frames one for each state and how Google Trends changed over time, each state has its own trajectory
-# Can we look at each state and how their interest changes over time and if that's related to how many cases are in the state
-
-#What's the trend in interest and how does it depend on cases? 
-```
-
-```{r}
-summary_building_mod <- summary(building_mod)
-
-head(as.data.frame(summary_building_mod),-2)
-```
-
-```{r, include=FALSE}
-prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
-  # Calculate summary statistics of simulated 
-  # posterior predictive models for each case
-  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
-  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
-  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
-  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
-  df <- data.frame(yrep) %>% 
-    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
-    unlist() %>% 
-    matrix(., length(y), 8) %>% 
-    data.frame()
-  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
-  data.frame(cbind(y, df))
-}
-
-prediction_summary <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
-  # This function summarizes the predictions across all cases
-  pred_data <- prediction_summary_data(y, yrep, prob_inner = prob_inner, prob_outer = prob_outer) %>% 
-    mutate(error = y - post_median) %>% 
-    mutate(error_scaled = error / post_mad) %>% 
-    mutate(within_inner = (y >= l_inner) & (y <= u_inner)) %>% 
-    mutate(within_outer = (y >= l_outer) & (y <= u_outer))
-
-  pred_summary <- pred_data %>% 
-    summarize(mae = median(abs(error)), 
-      mae_scaled = median(abs(error_scaled)),
-      within_inner = mean(within_inner),
-      within_outer = mean(within_outer)
-    )
-  names(pred_summary)[3] <- paste0("within_", prob_inner*100)
-  names(pred_summary)[4] <- paste0("within_", prob_outer*100)
-
-  pred_summary
-}
-```
-
-```{r}
-preds <- posterior_predict(building_mod,newdata = test1) # Ask Alicia 
-prediction_summary(y = test1$mean_kungfluinterest, yprep = preds)
-
-```
-
-\
-\

### 2020-04-23 Checkpoint3.Rmd
model 2

@@
 # Analysis
+
+# ```{r}
+# model_1 <- stan_glmer(
+#   ChinaVirusInterest ~ Day + (Day | State),
+#   data = Finaldata, family = gaussian,
+#   chains = 4, iter = 5000*2, refresh = 0
+# )
+# ```
+
+```{r}
+model_2 <- stan_glmer(
+  ChinaVirusInterest ~ (1 | Region),
+  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+)
+```
+
+```{r}
+mcmc_trace(model_2)
+mcmc_dens_overlay(model_2)
+```
+
+```{r}
+# Store the chains
+model_2_df <- as.array(model_2) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_2_df <- model_2_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[Region:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_2_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+```
+
+```{r}
+head(data.frame(summary(model_2)),-2)
+```

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd

@@
 
-```{r}
-# ## Positive COVID cases map before and after week 
-# plot3<-statebins(state_data = weekbefore, state_col = "State",
-#                      text_color = "white", value_col = "positive",
-#                      brewer_pal="Spectral", font_size = 3,breaks =7,
-#                      legend_title="Week Before",
-#                  labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))
-# 
-# ### Drastic scale change, needs work for comparison sake
-# plot4<-statebins(state_data = weekafter, state_col = "state",
-#                      text_color = "white", value_col = "positive",
-#                      brewer_pal="Spectral", font_size = 3,breaks =6,
-#                      legend_title="Week After",labels = c("1-100", "100-500", "500-5000", "5000-15000", "15000-25000", "25000-35000"))
-# 
-# plot3
-# plot4
-```
-
 ## Final Dataset

### 2020-04-24 Checkpoint3.Rmd
Finished Demographics

@@
 
+```
+Our first visualization is looking at the percent of residents that identify as white within the United States.
+As you can see, there is a higher percent of white identifying residents in the midwest and northeast states.
+From this visualization we can also see that places like Texas, California, and New Mexico have much lower white identifying residents which could provide important information for us in our actual analysis.
+
+```{r}
 plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
@@
 ) 
+```
+The above visualization is looking at the percent of residents that identify as Asian within the United States.
+As you can see, there is a higher percent of residents that identify as Asian in places like California and Washington, but the most being in Hawaii.
+From this visualization we can also see that that Midwest and the South tend to have a small percentage of residents identifying as Asian.
+We are especially interested in the `percent_asian` variable as it plays a major role in our analysis.
 
-#By Results 
-plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
-  scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
-  theme(legend.position = "right") + ggtitle("Percent Asian by General Election Results")+
-  theme(
-plot.title = element_text(color="Black", size=14, face="bold")
-) + facet_wrap(~Winner)
-
+```{r}
 #By income 
@@
   scale_fill_continuous(low = "sky blue", high = "black", name = "$ Per Capita", label = scales::comma) + 
-  theme(legend.position = "right") + ggtitle("Percent Capita Income")+
+  theme(legend.position = "right") + ggtitle("Income per Capita")+
   theme(
@@
 ) 
+```
+We also wanted to take a look at the `per capita income` variable, as we believe it could be valuable within our analysis.
+Specifically, we are thinking that it could possibly be an indicator for the amount COVID Cases and or could really affect an individuals reaction to Trump's tweet.
+This visualization however, is just uni-variate as we wanted to understand the variable a bit more.
+As you can see, the Northeast and the West coast tend to have higher incomes per capita than places like the South for instance.
 
+```{r}
 #Income by state affiliation 
-ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + 
-    geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")
+g <- ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")
 
+g + scale_fill_manual(values=c("blue", "purple", "red"))
+```
+After learning more about the `per capita income` variable we wanted to see how the variable would change when we added `State Color` into the mix.
+Where `State Color` signifies a state's political leaning during the election.
+What is interesting is that the states that were red had much lower incomes per capita than states that were blue.
+We see that the blue states had a much wider and higher spread of income per capita ranging all the way to $45,000.
+Purple states on the other hand tended to be in the middle.
+
+```{r}
 #Trump Support 
 ggplot(Finaldata, aes(x = percent_republican2016)) + 
-    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density")
+    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density") + facet_wrap(~Region)
+```
+This visualization is looking at Trump Support during the 2016 elections across different U.S.
+regions.
+From these visualizations it seems as though each region had pretty varying support.
+The Northeast had this interesting peak at 0.4 but also has another slope at around 0.
+The Western and Mountain regions have a similar pattern happening where there are strong peaks but then those peaks start dipping down fairly drastically.
+The South and the Midwest tend to lean more towards higher Trump support and we don't see the "dipping" occur as much.
+This leads us to believe that during that election those regions had more states that favored Trump and the Republican party.
 
+```{r}
 ggplot(Finaldata, aes(x = percent_asian, y = percent_republican2016, color = Winner)) + 
@@
 
-ggplot(Finaldata, aes(x = per_capita_income)) + 
-    geom_density()+ ggtitle("Per Capita Income") + xlab("Per Capita Income") + ylab("Density") + facet_wrap(~Winner)
 ```
+This final demographic visualization is depicting Trump support across all states among those who identify as Asian, and is then classifying whether or not Trump won in that specific state.
+The two outliers are labeled as Hawaii and DC.
+These are interesting because we see that DC had a small percent of Asian residents and also had low Trump support this is kinda expected.
+However, we see that Hawaii had a much larger percentage of Asian identifying residents but also still had a decent amount of Trump support.
+All in all though, this visualization tells us that in a way the states that had lower Asian identifying residents tended to have higher Trump support.
 

### 2020-04-24 Checkpoint3.Rmd
Update Checkpoint3.Rmd
google Vis description

@@
 
+This plot shows the relationship of “China Virus” search interest over grouped by region.
+This plots shows that there are certainly key events that trigger an uptick in searches overall.
+In this plot it is not clear which region may search China Virus more or less often, but it does show a that the regions move together in search interest, which would imply federal level events like a Donald Trump tweet to trigger these interest spikes.
+
 ### Demographic 

### 2020-04-24 Checkpoint3.Rmd
Adding my descriptions

@@
 library(gridExtra)
-
+library(plotly)
 require(janitor)
@@
 
-Re-Cleaned 
+## Re-Cleaned 
 ```{r} 
@@
 
-##Dataset Description
+## Dataset Description
 
-`Demographic:`
+### `Demographic:`
 Our dataset, `Demographic`, was created by merging three other datasets which all contained different demographic and election information.
@@
 
-`COVID-19 Cases`
+### `COVID-19 Cases`
 The COVID-19 data is provided by The COVID Tracking Project(CTP).
@@
 
-`Google Search Interest`
+### `Google Search Interest`
 This data set includes two search interest indexes over time, measuring how people in each of the state’s interest in searching either “Kung Flu” or “China Virus” based on the time frame selected in the search.
@@
 
-##Dataset Details 
+## Dataset Details 
 ```{r}
@@
 summary(Finaldata)
-
-colnames(Finaldata)
 ```
 
-##Variables of Interest
+## Variables of Interest
 
@@
 
-##Visualizations 
+# Visualizations
+
+## Google Set
 ```{r}
-library(plotly)
-#google_ts<-read.csv("Time_series_Google.csv")
-
 day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
@@
 
-### Demographic 
+## Demographic 
 ```{r}
 #Demographic: Identification 
+## Might not use, how helpful is this? Possibly combine into a shiny app so people could adjust for which race to look at? 
 Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
@@
 
-### COVID-19 Cases
+## COVID-19 Cases
 
@@
 plot1<- plot_usmap(data = weekbefore, values = "positive", color = "white") + 
-  scale_fill_continuous(name = "Cases", label = scales::comma) + 
+  scale_fill_continuous(low = "sky blue", high ="blue", 
+                          name = "Cases(#)",label = scales::comma,
+                          limits = c(0,500)) + 
   theme(legend.position = "right")+ ggtitle("# of COVID Cases Before 3/17") + 
@@
 plot2<-plot_usmap(data = weekafter, values = "positive", color = "white") + 
-  scale_fill_continuous(name = "Cases", label = scales::comma) + 
+   scale_fill_continuous(low = "sky blue", high ="red", 
+                          name = "Cases(#)",label = scales::comma,
+                          limits = c(0,10000)) + 
   theme(legend.position = "right")+ ggtitle("# of COVID Cases After 3/17") + 
@@
 grid.arrange(plot1, plot2, ncol=2)
+
+## I would like help fixing this scale
 ```
-
-```{r}
-# Positive COVID cases aggregated by party 
-ggplot(Finaldata, aes(x = positive, fill = StateColor)) + 
-    geom_density(alpha = .8)+ ggtitle("Positive COVID-19 Cases by State Party") + xlab("Cases") + ylab("Density")+xlim(0,500)
-```
+This visualization allows us to compare the raw count of positive COVID-19 cases among the US before and after March 17th (Trump says "China Virus").
+The goal of this visualization is to show the number of positive COVID-19 cases as the time progresses.
+From the first plot we can see there are very few states that have positive cases above 0-100.
+However, we see states like Washington, Michigan, California and New York have higher numbers.
+The second plot shows that while there are very few states above ~2,000 there overall a higher number of positive cases among the US.
+This intuitively makes sense given this is an infectious disease and we would only expect there to be more positive cases over time.
 
@@
 ```{r}
-ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
+b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
   geom_density(alpha = 0.5)
 
+ggplotly(b)
 ```
+We can see that the variability in Google interest in the term China Virus is has quite a large range between states.
+There are very few states that have high densities among the upper echelons of the interest scale but there are some interesting peaks of densities among the lower values.
+For example, we can see that Alaska, Wyoming and Iowa have unusal peaksaround the 25-50 range.
+It is is also interesitng interesting to note that there isn't an *obvious* mean or median value of China Virus interest among the states.
+
 ```{r}
-ggplot(Finaldata, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
+c<- ggplot(Finaldata, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
     geom_point() + 
@@
     theme(legend.position = "none")
+
+ggplotly(c)
 ```
+With this visualization we wanted to observe the different slopes of each slope of interest in the term China Virus over time.
+Arguably, the slopes of interest among the states are not significantly different.
+There are some interesting downward slopes in states like Wyoming but we would need to dig a bit deeper into this to fully understand what it means.
+However, a really interesting facet of this viusalization is that we can see a pattern among all states ofpeaks and valleys.
+In other words, from observation, the majority of states demonstrate a pattern correlated to the day.
+This would be interesting to explore further and see how it interacts with other aspects like number of COVID cases by state.
+
 \
@@
 
-# Analysis
-
-# ```{r}
-# model_1 <- stan_glmer(
-#   ChinaVirusInterest ~ Day + (Day | State),
-#   data = Finaldata, family = gaussian,
-#   chains = 4, iter = 5000*2, refresh = 0
-# )
-# ```
+# Building Models
 
 ```{r}
-model_2 <- stan_glmer(
+model_1 <- stan_glmer(
   ChinaVirusInterest ~ (1 | Region),
@@
 ```{r}
-mcmc_trace(model_2)
-mcmc_dens_overlay(model_2)
+mcmc_trace(model_1)
+mcmc_dens_overlay(model_1)
 ```
@@
 # Store the chains
-model_2_df <- as.array(model_2) %>% 
+model_1_df <- as.array(model_1) %>% 
   melt %>% 
@@
 # Note the need for `...` around the sigma_sq_b
-model_2_df <- model_2_df %>% 
+model_1_df <- model_1_df %>% 
   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[Region:(Intercept),(Intercept)]`) %>% 
@@
 
-ggplot(model_2_df, aes(x = correlation)) + 
+ggplot(model_1_df, aes(x = correlation)) + 
   geom_density(alpha = 0.5)
@@
 ```{r}
-head(data.frame(summary(model_2)),-2)
+head(data.frame(summary(model_1)),-2)
 ```
+
+# Next Steps
+The obvious improvements we need to make is exploring more models.
+We can see from our visualizations that are there are a wide variety of relationships we can dig into with our dataset.
+However, as a group, we need to decide what path(s) to take.
+Once we decide on which relationship(s) we want to analyze further, then this project can be enhanced with possibly animiated visualizations or even a shiny app.

### 2020-04-24 Checkpoint3.Rmd
updates

@@
 +------------------------+---------------------------------------------------+
-
+|`Region`                | States divided into five different regions:       |
+|                        | West, South, Mountain, Northeast, Midwest         |
++------------------------+---------------------------------------------------+
+|`StayAtHome_date`       | The date states have enforced quarantine          |
++------------------------+---------------------------------------------------+
+|`Quarantine_Yes`        | An 0,1 indicator of whether states have enforced  |
+|                        | quarantine                                        |
++------------------------+---------------------------------------------------+
 # Visualizations
@@
 ```{r}
+Trump<- as.Date("03/16/2020", format = "%m/%d/%Y")
 day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
@@
 plot1<- plot_usmap(data = weekbefore, values = "positive", color = "white") + 
-  scale_fill_continuous(low = "sky blue", high ="blue", 
-                          name = "Cases(#)",label = scales::comma,
+  scale_fill_gradient2(low = "white", high ="blue", mid = "skyblue",midpoint = 30,
+                          name = "Cases (#)",label = scales::comma,
                           limits = c(0,500)) + 
@@
 plot2<-plot_usmap(data = weekafter, values = "positive", color = "white") + 
-   scale_fill_continuous(low = "sky blue", high ="red", 
-                          name = "Cases(#)",label = scales::comma,
+   scale_fill_gradient2(low = "white", high ="red", mid = "blue",midpoint = 500,
+                          name = "Cases (#)",label = scales::comma,
                           limits = c(0,10000)) + 
@@
 grid.arrange(plot1, plot2, ncol=2)
-
-## I would like help fixing this scale
 ```
@@
 
-```{r}
+$$\begin{aligned}
+i = \text{state, } j = \text{date, } Y = \text{China Virus Interest}\\
+Y_{ij}|b_0,b_1 \sim N(b_{0i} + b_{1i}Day_{i},\sigma^2)\\
+b_{0i} \sim N(...)\\
+b_{1i} \sim N(...)\\
+\end{aligned}$$
+
+```{r cache=TRUE}
+set.seed(454)
 model_1 <- stan_glmer(

### 2020-04-24 Checkpoint3.Rmd
asdf
changes

@@
 $$\begin{aligned}
-i = \text{state, } j = \text{date, } Y = \text{China Virus Interest}\\
+i = \text{region, } j = \text{date, } Y = \text{China Virus Interest}\\
 Y_{ij}|b_0,b_1 \sim N(b_{0i} + b_{1i}Day_{i},\sigma^2)\\
@@
 set.seed(454)
+Finaldata<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day))
+
 model_1 <- stan_glmer(
@@
 ```
+
+From what we can see from the trace plot the intercepts for each region are not very different from each other.
+We could see that it is possible that the midwest and the north east have a higher intercept compared to the west, but the mean is centered around 0 for almost all of them.
+We would rather use states to see if we see differing intercepts through states but unfortunatelly our code did not run.
+
+Our model shows that the chains are stable maybe telling us that the model might work with lower chain iterations.
 
@@
 
+In our correlation density plot we can see that the values are not very correlated accross regions meaning that regions is probably a bad way to segment them.
+
 ```{r}

### 2020-04-24 merged data/Old Datasets/merging_datasets.Rmd
n
asdf
changes

--- 2020-04-22 merged data/merging_datasets.Rmd
@@
 stayhome<-read.csv("quarantine.csv")
-google<-read.csv("Google_final.csv")
+google<-read.csv("time_series_google.csv")
+
+google<-
+  google%>%
+  mutate(Day=as.Date(Day))
+
+day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
+day2<-as.Date("03/24/2020",format = "%m/%d/%Y")
+
+google_timeseries<-
+  google%>%
+  filter(Day<=day2)%>%
+  filter(Day>=day1)
+
 ```
@@
 
-all<-demographic%>%
+covid<-covid%>%
+  mutate(Day = as.Date(date, format = "%m/%d/%Y"))
+
+colnames(covid)[2] <- "State"
+
+covid%>%
+  group_by(State)
+
+google_timeseries<-google_timeseries%>%
+  select(-c(X))
+
+write.csv(all,"FinalDataSet.csv")
+names(all)
+
+time_series_final_Data<-google_timeseries%>%
   left_join(covid)%>%
-  left_join(stayhomefinal)%>%
-  left_join(google)
+  select(-c(date))%>%
+  left_join(stayhome)%>%
+  left_join(demographic)%>% 
+  mutate(Region = ifelse(State %in% c("AK","CA","OR","WA","HI"), "West", ifelse(State %in% c("CO","UT","ID","MT","WY", "NM", "AZ", "NV"), "Mountain", ifelse(State %in% c("SD","ND","MN","KS","IN", "MI", "NE", "IA", "WI","IL", "OH", "MO", "OK"), "Midwest",  ifelse(State %in% c("TX","AL","MS","FL","AR", "WV", "TN", "NC", "SC","GA", "VA", "KY", "LA"), "South", ifelse(State %in% c("MD","PA","DE","NJ","NY", "MA", "CT", "NH", "VT","ME", "RI", "DC"), "Northeast", 0))))))
 
-all
+write.csv(time_series_final_Data,"time_series_final_Data.csv")
+```
 
-write.csv(all,"FullDataSet.csv")
-names(all)
+```{r}
+Trump<- as.Date("03/16/2020", format = "%m/%d/%Y")
+
+glimpse(time_series_final_Data)
+time_series_final_Data%>%
+  group_by(StateColor, Day)%>%
+  mutate(mean_ChinaVirusInterest = mean(ChinaVirusInterest))%>%
+  ggplot(aes(x = Day, y = mean_ChinaVirusInterest, color = StateColor))+
+  geom_smooth(fill=NA)+
+  geom_vline(xintercept = Trump)+
+  geom_text(aes(Trump , 30, label = "Trump Tweets China Virus", vjust = -1), size = 3, color = "black")+
+  scale_color_manual(values = c("#0000FF", "#800080", "#FF0000"))
+
+time_series_final_Data%>%
+
 ```

### 2020-04-27 Checkpoint 4.Rmd
Creation of CP 4

---
title: "Checkpoint 4"
author: "Will Madairy, Sofia Pozsonyiova, Quinn Rafferty, Federico Chung"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
header-includes:
  - \usepackage{tabularx}
output:
  pdf_document: default
  html_document: default
abstract: ""
---

### 2020-04-28 Checkpoint 4.Rmd
I plot stuff

@@
 ---
+
+# Quinn plots stuff
+```{r}
+a<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
+  geom_density(alpha = 0.5)
+
+b<- ggplot(Finaldata, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
+    geom_point() + 
+    geom_smooth(method = "lm", se = FALSE) + 
+    facet_wrap(~ State) + 
+    theme(legend.position = "right")
+
+c<- ggplot(Finaldata, aes(x = ChinaVirusInterest, color = factor(StateColor))) + 
+    geom_histogram() + 
+    facet_wrap(~ Region) +
+    theme(legend.position = "right") + 
+    scale_colour_manual( values=c("red"= "red3", "blue"= "royalblue", "purple"="darkorchid3"))
+
+d <-  ggplot(Finaldata, aes(y=percent_asian, color = factor(Region))) + 
+      geom_boxplot() +
+      theme(legend.position = "right")
+
+ggplotly(a)
+ggplotly(b)
+ggplotly(c)
+ggplotly(d)
+```

### 2020-04-28 Checkpoint 4.Rmd
quinn plots more stuff

--- 2020-04-27 Checkpoint 4.Rmd
@@
   html_document: default
-abstract: ""
 ---
+
+```{r, warning=FALSE}
+library(dplyr)
+library(usmap)
+library(maps)
+library(ggplot2)
+library(tidyverse)
+library(ggmap)
+library(viridis)
+library(rgdal)
+library(gridExtra)
+library(plotly)
+require(janitor)
+require(reshape2)
+require(tidyr)
+require(rstan)
+require(rstanarm)
+require(bayesplot)
+```
+
+# Quinn plots stuff
+```{r}
+a<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
+  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State")
+
+b<- ggplot(Finaldata, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
+    geom_point() + 
+    geom_smooth(method = "lm", se = FALSE) + 
+    facet_wrap(~ State) + 
+    theme(legend.position = "right")+
+    ggtitle("China Virus Interest by Day by State")
+
+c<- ggplot(Finaldata, aes(x = ChinaVirusInterest, color = factor(StateColor))) + 
+    geom_histogram() + 
+    facet_wrap(~ Winner) +
+    theme(legend.position = "right") + 
+    scale_colour_manual( values=c("red"= "red3", "blue"= "royalblue", "purple"="darkorchid3")) +
+    ggtitle("China Virus Google by State Poltical Party Winner")
+
+d <-  ggplot(Finaldata, aes(y=positive, x=Winner, fill=(Winner)))+
+      geom_boxplot() +
+      facet_wrap(~Region)+
+      theme(legend.position = "none") +
+      scale_fill_manual(values = c("Democrat"="blue3", "Republican"= "red3"))+
+      lims(y= c(0,1000))+
+      ggtitle("Positive COVID-19 Cases by State Political Party Winner & Region")
+
+ggplotly(a)
+ggplotly(b)
+ggplotly(c) #Shows that Democrat states tend to have a higher interest in Googling China Virus 
+ggplotly(d)
+```

### 2020-04-28 Checkpoint3.Rmd

@@
 +------------------------+---------------------------------------------------+
+
+\
+\
+
 # Visualizations
@@
 ```
+
 Our first visualization is looking at the percent of residents that identify as white within the United States.
@@
 ```
+
 The above visualization is looking at the percent of residents that identify as Asian within the United States.
@@
 ```
+
 We also wanted to take a look at the `per capita income` variable, as we believe it could be valuable within our analysis.
@@
 ```
+
 After learning more about the `per capita income` variable we wanted to see how the variable would change when we added `State Color` into the mix.
@@
 ```
+
 This visualization is looking at Trump Support during the 2016 elections across different U.S.
@@
 ```
+
 This final demographic visualization is depicting Trump support across all states among those who identify as Asian, and is then classifying whether or not Trump won in that specific state.
@@
 ```
+
 This visualization allows us to compare the raw count of positive COVID-19 cases among the US before and after March 17th (Trump says "China Virus").
@@
 ```
+
 We can see that the variability in Google interest in the term China Virus is has quite a large range between states.
@@
 ```
+
 With this visualization we wanted to observe the different slopes of each slope of interest in the term China Virus over time.
@@
 
-# Building Models
+# Building Model
 
@@
 Once we decide on which relationship(s) we want to analyze further, then this project can be enhanced with possibly animiated visualizations or even a shiny app.
+
+# Project Contributions
+- Quinn: Cleaned the COVID-19 data set, provided all visualizations and descriptions of COVID-19, provided the data description, ran analysis of the model, cleaned/formated checkpoint 3 document and knitted/turned in final checkpoint 3 product.
+- Sofia: Cleaned the demographic data set, provided all visualizations and descriptions of demographic aspects, provided the data descriptions for the dataset and created variables of interest table.
+- Will:  Cleaned the Google Trend data set, provided all visualizations and descriptions of the CHina Virus and Kung Flu virus relationships and provided the data descriptions for the dataset.
+- Federico: Merged the datasets and provided brief descriptions of our building model section.

### 2020-04-28 Checkpoint 4.Rmd
graphs

@@
 # Quinn plots stuff
+
+```{r}
+Finaldata<-read.csv("time_series_final_Data.csv")
+
+```
+```{r} 
+Finaldata <- Finaldata %>% select(-c(X)) 
+Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
+```
+
+```{r}
+Finaldata%>%
+  mutate(perc_population_positive = positive/total_population)%>%
+  group_by(State)%>%
+  mutate(mean_corona_interest = mean(ChinaVirusInterest),
+         max = max(ChinaVirusInterest),
+         median = median(ChinaVirusInterest))%>%
+  ggplot(aes(x = mean_corona_interest, y = perc_population_positive, color = percent_asian))+
+  geom_point()+
+  scale_colour_gradient2(low = "blue", mid = "lightblue", high = "red")
+```
+
 ```{r}

### 2020-04-28 Checkpoint 4.Rmd
trying some models

--- 2020-04-28 Checkpoint 4.Rmd
@@
 
-```{r, warning=FALSE}
+```{r, warning=FALSE, include=FALSE}
 library(dplyr)
@@
 require(bayesplot)
+```
+
+```{r}
+Finaldata<-read.csv("time_series_final_Data.csv")
+```
+
+```{r} 
+Finaldata <- Finaldata %>% select(-c(X)) 
+Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
+names(Finaldata)
+```
+
+```{r}
+Finaldata%>%
+  mutate(perc_population_positive = positive/total_population)%>%
+  group_by(State)%>%
+  mutate(mean_corona_interest = mean(ChinaVirusInterest),
+         max = max(ChinaVirusInterest),
+         median = median(ChinaVirusInterest))%>%
+  ggplot(aes(x = mean_corona_interest, y = perc_population_positive, color = percent_asian))+
+  geom_point()+
+  scale_colour_gradient2(low = "blue", mid = "lightblue", high = "red")
 ```
@@
 ggplotly(d)
+
+# What affects the China Interest search, is it demographic, policitical or COVID based? 
+## From Alicia:: Start by thinking, take the four models from the sleep study and just think how we can go thorugh those four models in the context of our work. It's
 ```
+
+```{r}
+set.seed(454)
+Finaldata<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day))
+
+model_1 <- stan_glmer(
+  ChinaVirusInterest ~ (1 | State), #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+)
+```
+
+```{r}
+model_2 <- stan_glmer(
+  ChinaVirusInterest ~ Day + (Day | State),
+  data = Finaldata, family = gaussian,
+  chains = 4, iter = 5000*2, refresh = 0
+)
+
+```
+
+```{r}
+# model_3 <- stan_glmer(
+#   ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
+#   data = Finaldata, family = gaussian,
+#   chains = 4, iter = 100, refresh = 0
+# )
+```
+
+```{r}
+# model_4 <- stan_glm(
+#   Reaction ~ 1,
+#   data = sleep, family = gaussian,
+#   chains = 4, iter = 5000*2
+# )
+# 
+```
+
+```{r}
+head(data.frame(summary(model_1)),-2)
+```

### 2020-04-28 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd
more model building

@@
 
+#################################### Notes!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+
 # What affects the China Interest search, is it demographic, policitical or COVID based? 
-## From Alicia:: Start by thinking, take the four models from the sleep study and just think how we can go thorugh those four models in the context of our work. It's
+## From Alicia:: Start by thinking, take the four models from the sleep study and just think how we can go thorugh those four models in the context of our work.
+
+## Chosen variables: Number of COVID-19 cases, State color, percent black, percent white, income
 ```
 
-```{r}
+#Quinn making models
+```{r, cahce=TRUE}
 set.seed(454)
@@
 ```{r}
+head(data.frame(summary(model_1)),-2)
+```
+
+#Quinn making models
+```{r}
 model_2 <- stan_glmer(
@@
 
+#Quinn makes models
 ```{r}
@@
 ```
-
-```{r}
-head(data.frame(summary(model_1)),-2)
-```

### 2020-04-28 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd

@@
 Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
-names(Finaldata)
 ```
@@
 #Quinn making models
-```{r}
+```{r, warning=FALSE, cache=TRUE}
 model_2 <- stan_glmer(
@@
   data = Finaldata, family = gaussian,
-  chains = 4, iter = 5000*2, refresh = 0
+  chains = 4, iter = 100, refresh = 0
 )
@@
 
-#Quinn makes models
 ```{r}
-# model_3 <- stan_glmer(
-#   ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
-#   data = Finaldata, family = gaussian,
-#   chains = 4, iter = 100, refresh = 0
-# )
+head(data.frame(summary(model_2)),-2)
 ```
@@
 #Quinn makes models
+```{r, warning = FALSE, cache=TRUE}
+model_3 <- stan_glmer(
+  ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
+  data = Finaldata, family = gaussian,
+  chains = 4, iter = 100, refresh = 0
+)
+```
+
 ```{r}
-# model_4 <- stan_glm(
-#   Reaction ~ 1,
-#   data = sleep, family = gaussian,
-#   chains = 4, iter = 5000*2
-# )
-# 
+head(data.frame(summary(model_3)),-2)
 ```
+
+#Quinn makes models
+```{r, warning = FALSE, cache=TRUE}
+model_4 <- stan_glmer(
+  ChinaVirusInterest ~ Day + totalTestResults + (Day | State),#Random intercepts and slopes when we put Day in
+  data = Finaldata, family = gaussian,
+  chains = 4, iter = 100, refresh = 0
+)
+```
+
+```{r}
+head(data.frame(summary(model_4)),-2)
+```

### 2020-04-28 Checkpoint 4.Rmd
Models updated

@@
 ```
+
+\
+\
+
+#Sofia's Models:
+
+Variables of Interest: 
+\
+• per_capita_income
+\
+•totalTestResults
+\
+• StateColor
+\
+• percent_asian
+\
+•percent_black
+
+##Model 5:
+
+```{r, warning = FALSE, cache=TRUE}
+set.seed(454)
+Finaldata<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day))
+
+model_1 <- stan_glmer(
+  ChinaVirusInterest ~ StateColor + (StateColor | State), #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+)
+```
+
+```{r}
+head(data.frame(summary(model_1)),-2)
+```
+
+##Model 6: 
+StateColor + per_capita_income + (StateColor | State)
+```{r, warning = FALSE, cache=TRUE}
+set.seed(454)
+Finaldata<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day))
+
+model_6 <- stan_glmer(
+  ChinaVirusInterest ~ StateColor + per_capita_income + (StateColor | State), #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 3, iter = 3000*2
+)
+```
+
+```{r}
+head(data.frame(summary(model_6)),-2)
+```
+
+##Model 7: 
+StateColor + percent_asian + (StateColor | State)
+
+```{r, warning = FALSE, cache=TRUE}
+set.seed(454)
+Finaldata<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day))
+
+model_7 <- stan_glmer(
+  ChinaVirusInterest ~ StateColor + percent_asian + (StateColor | State), #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
+)
+```
+
+```{r}
+head(data.frame(summary(model_7)),-2)
+```
+
+##Model 8:
+
+StateColor + totalTestResults + (StateColor | State)
+
+```{r, warning = FALSE, cache=TRUE}
+set.seed(454)
+Finaldata<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day))
+
+model_8 <- stan_glmer(
+  ChinaVirusInterest ~ StateColor + totalTestResults + (StateColor | State), #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
+)
+```
+```{r}
+head(data.frame(summary(model_8)),-2)
+```
+
+##Model 9:
+
+StateColor +percent_asian + totalTestResults + (StateColor | State)
+
+```{r, warning = FALSE, cache=TRUE}
+set.seed(454)
+Finaldata<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day))
+
+model_9 <- stan_glmer(
+  ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State), #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
+)
+```
+
+```{r}
+head(data.frame(summary(model_9)),-2)
+```

### 2020-04-29 Checkpoint 4.Rmd
4 models

@@
 ```{r}
-Finaldata<-read.csv("time_series_final_Data.csv")
+Finaldata<-read_csv("time_series_final_Data.csv")
 ```
@@
 Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
-```
-
-```{r}
-Finaldata%>%
-  mutate(perc_population_positive = positive/total_population)%>%
-  group_by(State)%>%
-  mutate(mean_corona_interest = mean(ChinaVirusInterest),
-         max = max(ChinaVirusInterest),
-         median = median(ChinaVirusInterest))%>%
-  ggplot(aes(x = mean_corona_interest, y = perc_population_positive, color = percent_asian))+
-  geom_point()+
-  scale_colour_gradient2(low = "blue", mid = "lightblue", high = "red")
 ```
@@
 ```
+
+#Fed's visualizations:
+```{r}
+#for visuals
+install.packages("ggforce")
+library(ggforce)
+ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
+    geom_point() + 
+    geom_smooth(method = "lm", se = FALSE) + 
+    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 1) + 
+    theme(legend.position = "none")
+```
+
+```{r}
+ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
+    geom_point() + 
+    geom_smooth(method = "lm", se = FALSE) + 
+    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 2) + 
+    theme(legend.position = "none")
+```
+
+```{r}
+ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
+    geom_point() + 
+    geom_smooth(method = "lm", se = FALSE) + 
+    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 3) + 
+    theme(legend.position = "none")
+```
+
+```{r}
+ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
+    geom_point() + 
+    geom_smooth(method = "lm", se = FALSE) + 
+    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 4) + 
+    theme(legend.position = "none")
+```
+
+```{r}
+ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
+    geom_point() + 
+    geom_smooth(method = "lm", se = FALSE) + 
+    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 5) + 
+    theme(legend.position = "none")
+```
+
+```{r}
+ggplot(Finaldata, aes(x = as.numeric(Day), y = ChinaVirusInterest, color = factor(State))) + 
+    geom_point() + 
+    geom_smooth(method = "lm", se = FALSE) + 
+    facet_wrap_paginate(~ State, ncol = 3, nrow = 3, page = 6) + 
+    theme(legend.position = "none")
+```
+
+```{r}
+Finaldata%>%
+  mutate(perc_population_positive = positive/total_population)%>%
+  group_by(State)%>%
+  mutate(mean_corona_interest = mean(ChinaVirusInterest),
+         max = max(ChinaVirusInterest),
+         median = median(ChinaVirusInterest))%>%
+  ggplot(aes(x = mean_corona_interest, y = perc_population_positive, color = percent_asian))+
+  geom_point()+
+  scale_colour_gradient2(low = "blue", mid = "lightblue", high = "red")
+```
+
+#Fed's Models:
+
+Variables of interest:
+- % white
+- postive rate (out of the tested)
+
+```{r}
+set.seed(454)
+glimpse(Finaldata)
+model_data<-Finaldata%>%
+  mutate(Date = as.numeric(Day))%>%
+  mutate(positive_rate = positive/ totalTestResults)%>%
+  select(State, ChinaVirusInterest, Day, percent_white,positive_rate)
+model_data<- na.omit(model_data)
+
+colSums(is.na(model_data))
+
+model_10 <- stan_glmer(
+  ChinaVirusInterest ~ Day + (1 | State) + percent_white,
+  data = model_data, family = gaussian, chains = 4, iter = 1000
+)
+```
+```{r}
+head(data.frame(summary(model_10)),-2)
+```
+
+```{r}
+# Store the chains
+model_10_df <- as.array(model_10) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_10_df <- model_10_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_10_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+```
+```{r}
+set.seed(454)
+#random intercept and random slope, percent white
+model_11 <- stan_glmer(
+  ChinaVirusInterest ~ (Day | State) + percent_white,
+  data = model_data, family = gaussian, chains = 4, iter = 3000
+)
+```
+```{r}
+head(data.frame(summary(model_11)),-2)
+```
+
+```{r}
+# Store the chains
+model_11_df <- as.array(model_11) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_11_df <- model_11_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_10_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+```
+
+```{r}
+set.seed(454)
+
+model_12<- stan_glmer(
+  ChinaVirusInterest ~ Day + (1 | State) + percent_white +positive_rate,
+  data = model_data, family = gaussian, chains = 4, iter = 3000
+)
+```
+```{r}
+head(data.frame(summary(model_12)),-2)
+```
+
+```{r}
+# Store the chains
+model_12_df <- as.array(model_12) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_12_df <- model_12_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_12_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+```
+
+```{r}
+set.seed(454)
+#random intercept and random slope, percent white and positive rate = positive/ total tests
+#iterations might be low need to sample up if we want to make the models better
+model_13 <- stan_glmer(
+  ChinaVirusInterest ~ (Day | State) + percent_white +positive_rate,
+  data = model_data, family = gaussian, chains = 4, iter = 3000
+)
+```
+```{r}
+head(data.frame(summary(model_13)),-2)
+```
+
+```{r}
+# Store the chains
+model_13_df <- as.array(model_13) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_13_df <- model_13_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_13_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+```

### 2020-04-29 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd
Added Models: Black, Pct Neg

@@
 ```
+
+# Will's Models
+
+-Variables of Interest:
+*Pct Black
+*Pct Positive
+*Pct Negative
+
+```{r}
+mod_data<-Finaldata%>%
+  mutate(Date = as.numeric(Day))%>%
+  mutate(positive_rate = positive/ totalTestResults)%>%
+  mutate(negative_rate = 1-positive_rate) %>% 
+  select(State, ChinaVirusInterest, Day, percent_white, percent_black, positive_rate, negative_rate, KungFluInterest, Region, StateColor)
+model_data<- na.omit(model_data)
+```
+
+```{r}
+set.seed(454)
+#Neg Rate
+model_14 <- stan_glmer(
+  ChinaVirusInterest ~ Day + (1 | State) + negative_rate,
+  data = mod_data, family = gaussian, chains = 4, iter = 1000
+)
+```
+
+```{r}
+head(data.frame(summary(model_14)),-2)
+```
+
+```{r}
+# Store the chains
+model_14_df <- as.array(model_14) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_14_df <- model_14_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_14_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+```
+
+```{r}
+model_15<-stan_glmer(
+  ChinaVirusInterest ~ (Day|State) + negative_rate, 
+  data=mod_data, family=gaussian, chains =4, iter = 5000
+)
+```
+
+```{r}
+head(data.frame(summary(model_15)),-2)
+```
+
+```{r}
+# Store the chains
+model_15_df <- as.array(model_15) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_15_df <- model_15_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_15_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+```
+
+```{r}
+model_16<-stan_glmer(
+  ChinaVirusInterest~ (1|State) + percent_black + negative_rate, 
+  data = mod_data, family = gaussian, chains = 4, iter = 5000
+)
+```
+
+```{r}
+head(data.frame(summary(model_16)),-2)
+```
+
+```{r}
+# Store the chains
+model_16_df <- as.array(model_16) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_16_df <- model_16_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_16_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+```
+
+```{r}
+# Pct black, Neg Rate: Random effects
+model_17<-stan_glmer(
+  ChinaVirusInterest~ (Day|State) + percent_black + negative_rate, 
+  data = mod_data, family = gaussian, chains = 4, iter = 2*5000
+)
+```
+
+```{r}
+head(data.frame(summary(model_17)),-2)
+```
+
+```{r}
+model_17_df <- as.array(model_17) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_17_df <- model_17_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_17_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+```

### 2020-04-29 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd

--- 2020-04-28 Checkpoint 4.Rmd
@@
 
-\
-\
-
-#Sofia's Models:
-
-Variables of Interest: 
-\
-• per_capita_income
-\
-•totalTestResults
-\
-• StateColor
-\
-• percent_asian
-\
-•percent_black
-
-##Model 5:
-
 ```{r, warning = FALSE, cache=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
-
-model_1 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+model_5 <- stan_glmer(
+  ChinaVirusInterest ~ Day + totalTestResults + positive + percent_white +  (Day | State),#Random intercepts and slopes when we put Day in
+  data = Finaldata, family = gaussian,
+  chains = 4, iter = 100, refresh = 0
 )
@@
 ```{r}
-head(data.frame(summary(model_1)),-2)
+head(data.frame(summary(model_5),-2))
 ```
-
-##Model 6: 
-StateColor + per_capita_income + (StateColor | State)
-```{r, warning = FALSE, cache=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
-
-model_6 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor + per_capita_income + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 3, iter = 3000*2
-)
-```
-
-```{r}
-head(data.frame(summary(model_6)),-2)
-```
-
-##Model 7: 
-StateColor + percent_asian + (StateColor | State)
-
-```{r, warning = FALSE, cache=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
-
-model_7 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor + percent_asian + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
-)
-```
-
-```{r}
-head(data.frame(summary(model_7)),-2)
-```
-
-##Model 8:
-
-StateColor + totalTestResults + (StateColor | State)
-
-```{r, warning = FALSE, cache=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
-
-model_8 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor + totalTestResults + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
-)
-```
-```{r}
-head(data.frame(summary(model_8)),-2)
-```
-
-##Model 9:
-
-StateColor +percent_asian + totalTestResults + (StateColor | State)
-
-```{r, warning = FALSE, cache=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
-
-model_9 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
-)
-```
-
-```{r}
-head(data.frame(summary(model_9)),-2)
-```

### 2020-04-29 Checkpoint 4.Rmd
to do now

--- 2020-04-29 Checkpoint 4.Rmd
@@
 require(bayesplot)
+```
+
+```{r}
+################################## To do before Alicia with your fave model ##########################################
+# mcmc_trace()
+# mcmc_dens_overlay()
+# pp_check()
+
+### For predicting one case 
+          # new_308 <- data.frame(Days = 9, Subject =308)
+          # 
+          # set.seed(454)
+          # pred_308 <- posterior_predict(
+          #   model_4, 
+          #   newdata = new_308)
+          # 
+          # pred_308 <- data.frame(y_new = pred_308[-1])
+          # 
+          # ggplot(pred_308, aes(x=y_new))+geom_density()
+          # 
+          # summary(pred_308)
+
+## For correlation check (type like model 2 from activity 19)
+          # Store the chains
+          # model_1_df <- as.array(model_1) %>% 
+          #   melt %>% 
+          #   pivot_wider(names_from = parameters, values_from = value)
+          # 
+          # # Wrangle the chains
+          # # Note the need for `...` around the sigma_sq_b
+          # model_1_df <- model_1_df %>% 
+          #   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[Region:(Intercept),(Intercept)]`) %>% 
+          #   mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+          # 
+          # ggplot(model_1_df, aes(x = correlation)) + 
+          #   geom_density(alpha = 0.5)
+```
+
+```{r, include=FALSE}
+prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
+  # Calculate summary statistics of simulated 
+  # posterior predictive models for each case
+  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
+  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
+  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
+  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
+  df <- data.frame(yrep) %>% 
+    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
+    unlist() %>% 
+    matrix(., length(y), 8) %>% 
+    data.frame()
+  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
+  data.frame(cbind(y, df))
+}
+
+prediction_summary <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
+  # This function summarizes the predictions across all cases
+  pred_data <- prediction_summary_data(y, yrep, prob_inner = prob_inner, prob_outer = prob_outer) %>% 
+    mutate(error = y - post_median) %>% 
+    mutate(error_scaled = error / post_mad) %>% 
+    mutate(within_inner = (y >= l_inner) & (y <= u_inner)) %>% 
+    mutate(within_outer = (y >= l_outer) & (y <= u_outer))
+
+  pred_summary <- pred_data %>% 
+    summarize(mae = median(abs(error)), 
+      mae_scaled = median(abs(error_scaled)),
+      within_inner = mean(within_inner),
+      within_outer = mean(within_outer)
+    )
+  names(pred_summary)[3] <- paste0("within_", prob_inner*100)
+  names(pred_summary)[4] <- paste0("within_", prob_outer*100)
+
+  pred_summary
+}
 ```
@@
 
-\
-\
+```{r, warning = FALSE, cache=TRUE}
+model_5 <- stan_glmer(
+  ChinaVirusInterest ~ Day + totalTestResults + positive + percent_white +  (Day | State),#Random intercepts and slopes when we put Day in
+  data = Finaldata, family = gaussian,
+  chains = 4, iter = 100, refresh = 0
+)
+
+```
 
@@
   data = mod_data, family = gaussian, chains = 4, iter = 2*5000
+
 )
@@
 ```{r}
+
+head(data.frame(summary(model_5),-2))
+
 head(data.frame(summary(model_17)),-2)
@@
   geom_density(alpha = 0.5)
+
 ```

### 2020-04-29 Checkpoint 4.Rmd
data

@@
 ```{r} 
-Finaldata <- Finaldata %>% select(-c(X)) 
 Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
+day_initial<- as.Date("2020-03-14")
+day_final<- as.Date("2020-03-21")
+Finaldata<- Finaldata%>%
+  filter(Day>=day_initial)%>%
+  filter(Day<=day_final)
 ```

### 2020-04-30 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd

--- 2020-04-29 Checkpoint 4.Rmd
@@
 
-model_1 <- stan_glmer(
+model_5 <- stan_glmer(
   ChinaVirusInterest ~ StateColor + (StateColor | State), #Gives us random intercepts
@@
 ```{r}
-head(data.frame(summary(model_1)),-2)
+head(data.frame(summary(model_5)),-2)
 ```
 
-##Model 6: 
-StateColor + per_capita_income + (StateColor | State)
-```{r, warning = FALSE, cache=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
+Checks:
 
-model_6 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor + per_capita_income + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 3, iter = 3000*2
-)
+```{r}
+# Trace plots
+#mcmc_trace(model_5)
+
+# Density plots
+#mcmc_dens_overlay(model_5)
 ```
@@
 ```{r}
-head(data.frame(summary(model_6)),-2)
+# y = original sample, yrep = MCMC simulation
+set.seed(454)
+pp_check(model_5, nreps = 50)
+```
+
+```{r}
+# Store the chains
+model_5_df <- as.array(model_5) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_5_df <- model_5_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))
+
+ggplot(model_5_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+
+```
+
+```{r}
+#set.seed(454)
+#my_data <- data.frame(StateColor = "red", State = "FL")
+
+# Simulate a set of predictions for each case in newdata
+#my_prediction <- posterior_predict(
+ # model_5, 
+  #newdata = my_data)
+
+#my_prediction <- data.frame(y_new = my_prediction[,1])
+
+#ggplot(my_prediction, aes(x = y_new)) + 
+ # geom_density()
+
+#summary(my_prediction)
 ```
@@
 
-##Model 8:
+```{r}
+# y = original sample, yrep = MCMC simulation
+set.seed(454)
+pp_check(model_7, nreps = 50)
+```
 
-StateColor + totalTestResults + (StateColor | State)
+```{r}
+# Store the chains
+model_7_df <- as.array(model_7) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
 
-```{r, warning = FALSE, cache=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_7_df <- model_7_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))
 
-model_8 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor + totalTestResults + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
-)
+ggplot(model_7_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+
 ```
+
 ```{r}
-head(data.frame(summary(model_8)),-2)
+# set.seed(454)
+# my_data <- data.frame(StateColor = "blue", State = "IL", percent_asian = .12)
+# 
+# # Simulate a set of predictions for each case in newdata
+# my_prediction <- posterior_predict(
+#   model_7,
+#   newdata = my_data)
+
+#my_prediction <- data.frame(y_new = my_prediction[,1])
+
+#ggplot(my_prediction, aes(x = y_new)) +
+ # geom_density()
+
+#summary(my_prediction)
 ```
@@
   ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
+  data = Finaldata, family = gaussian, chains = 4, iter = 1000*2
 )
@@
 head(data.frame(summary(model_9)),-2)
+```
+
+```{r}
+# y = original sample, yrep = MCMC simulation
+set.seed(454)
+pp_check(model_9, nreps = 50)
+```
+
+```{r}
+# Store the chains
+model_9_df <- as.array(model_9) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_9_df <- model_9_df %>% 
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))
+
+ggplot(model_9_df, aes(x = correlation)) + 
+  geom_density(alpha = 0.5)
+
+```
+
+```{r}
+#set.seed(454)
+#my_data <- data.frame(StateColor = "red", State = "FL")
+
+# Simulate a set of predictions for each case in newdata
+#my_prediction <- posterior_predict(
+ # model_5, 
+  #newdata = my_data)
+
+#my_prediction <- data.frame(y_new = my_prediction[,1])
+
+#ggplot(my_prediction, aes(x = y_new)) + 
+ # geom_density()
+
+#summary(my_prediction)
 ```

### 2020-04-30 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd
pp-check

@@
 colSums(is.na(model_data))
-
+```
+```{r}
 model_10 <- stan_glmer(
@@
 
+Model 14
 ```{r}
@@
 model_14 <- stan_glmer(
-  ChinaVirusInterest ~ Day + (1 | State) + negative_rate,
+  ChinaVirusInterest ~ (1 | State) + negative_rate,
   data = mod_data, family = gaussian, chains = 4, iter = 1000
@@
 head(data.frame(summary(model_14)),-2)
+```
+
+Checking Model 14
+```{r}
+mcmc_trace(model_14)
+mcmc_dens(model_14)
+```
+```{r}
+pp_check(model_14, nreps=50)
 ```
@@
 ```{r}
-model_15<-stan_glmer(
-  ChinaVirusInterest ~ (Day|State) + negative_rate, 
-  data=mod_data, family=gaussian, chains =4, iter = 5000
-)
+set.seed(454)
+my_data <- data.frame(negative_rate = .9, State = "IL", percent_black = .12)
+
+ # Simulate a set of predictions for each case in newdata
+my_prediction <- posterior_predict(
+   model_14,
+   newdata = my_data)
+
+my_prediction <- data.frame(y_new = my_prediction[,1])
+
+ggplot(my_prediction, aes(x = y_new)) +
+  geom_density()
+
+summary(my_prediction)
 ```
@@
 ```{r}
-head(data.frame(summary(model_15)),-2)
+# model_15<-stan_glmer(
+#   ChinaVirusInterest ~ (Day|State) + negative_rate, 
+#   data=mod_data, family=gaussian, chains =4, iter = 5000
+# )
 ```
@@
 ```{r}
-# Store the chains
-model_15_df <- as.array(model_15) %>% 
-  melt %>% 
-  pivot_wider(names_from = parameters, values_from = value)
+# head(data.frame(summary(model_15)),-2)
+```
 
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_15_df <- model_15_df %>% 
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
-  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-
-ggplot(model_15_df, aes(x = correlation)) + 
-  geom_density(alpha = 0.5)
+```{r}
+# # Store the chains
+# model_15_df <- as.array(model_15) %>% 
+#   melt %>% 
+#   pivot_wider(names_from = parameters, values_from = value)
+# 
+# # Wrangle the chains
+# # Note the need for `...` around the sigma_sq_b
+# model_15_df <- model_15_df %>% 
+#   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+#   mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+# 
+# ggplot(model_15_df, aes(x = correlation)) + 
+#   geom_density(alpha = 0.5)
 ```
@@
 head(data.frame(summary(model_16)),-2)
+```
+
+```{r}
+mcmc_trace(model_16)
+mcmc_dens(model_16)
+```
+
+```{r}
+pp_check(model_16, iter=50)
 ```
@@
 ```{r}
-# Pct black, Neg Rate: Random effects
-model_17<-stan_glmer(
-  ChinaVirusInterest~ (Day|State) + percent_black + negative_rate, 
-  data = mod_data, family = gaussian, chains = 4, iter = 2*5000
+set.seed(454)
+my_data <- data.frame(negative_rate = .9, State = "IL", percent_black = .12)
 
-)
+ # Simulate a set of predictions for each case in newdata
+my_prediction <- posterior_predict(
+   model_16,
+   newdata = my_data)
+
+my_prediction <- data.frame(y_new = my_prediction[,1])
+
+ggplot(my_prediction, aes(x = y_new)) +
+  geom_density()
+
+summary(my_prediction)
 ```
@@
 ```{r}
-
-head(data.frame(summary(model_5),-2))
-
-head(data.frame(summary(model_17)),-2)
+# # Pct black, Neg Rate: Random effects
+# model_17<-stan_glmer(
+#   ChinaVirusInterest~ (Day|State) + percent_black + negative_rate, 
+#   data = mod_data, family = gaussian, chains = 4, iter = 2*5000
+# 
+# )
 ```
@@
 ```{r}
-model_17_df <- as.array(model_17) %>% 
-  melt %>% 
-  pivot_wider(names_from = parameters, values_from = value)
+# head(data.frame(summary(model_17)),-2)
+```
 
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_17_df <- model_17_df %>% 
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
-  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-
-ggplot(model_17_df, aes(x = correlation)) + 
-  geom_density(alpha = 0.5)
-
+```{r}
+# model_17_df <- as.array(model_17) %>% 
+#   melt %>% 
+#   pivot_wider(names_from = parameters, values_from = value)
+# 
+# # Wrangle the chains
+# # Note the need for `...` around the sigma_sq_b
+# model_17_df <- model_17_df %>% 
+#   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+#   mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+# 
+# ggplot(model_17_df, aes(x = correlation)) + 
+#   geom_density(alpha = 0.5)
 ```

### 2020-04-30 Checkpoint 4.Rmd
quinn does model eval

@@
 
-```{r}
+```{r, warning=FALSE}
 Finaldata<-read_csv("time_series_final_Data.csv")
@@
 ```{r, cahce=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
-
-model_1 <- stan_glmer(
-  ChinaVirusInterest ~ (1 | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
-)
+# 
+# model_1 <- stan_glmer(
+#   ChinaVirusInterest ~ (1 | State), #Gives us random intercepts
+#   data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+# )
 ```
@@
 ```{r}
-head(data.frame(summary(model_1)),-2)
+# head(data.frame(summary(model_1)),-2)
 ```
@@
 ```{r, warning=FALSE, cache=TRUE}
-model_2 <- stan_glmer(
-  ChinaVirusInterest ~ Day + (Day | State),
+# model_2 <- stan_glmer(
+#   ChinaVirusInterest ~ Day + (Day | State),
+#   data = Finaldata, family = gaussian,
+#   chains = 4, iter = 100, refresh = 0
+# )
+
+```
+
+```{r}
+# head(data.frame(summary(model_2)),-2)
+```
+
+#Quinn makes models
+```{r, warning = FALSE, cache=TRUE}
+# model_3 <- stan_glmer(
+#   ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
+#   data = Finaldata, family = gaussian,
+#   chains = 4, iter = 100, refresh = 0
+# )
+```
+
+```{r}
+# head(data.frame(summary(model_3)),-2)
+```
+
+#Quinn makes models
+```{r, warning = FALSE, cache=TRUE}
+# model_4 <- stan_glmer(
+#   ChinaVirusInterest ~ Day + totalTestResults + (Day | State),#Random intercepts and slopes when we put Day in
+#   data = Finaldata, family = gaussian,
+#   chains = 4, iter = 100, refresh = 0
+# )
+```
+
+```{r}
+# head(data.frame(summary(model_4)),-2)
+```
+
+```{r, warning = FALSE, cache=TRUE}
+model_100 <- stan_glmer(
+  ChinaVirusInterest ~ Day + totalTestResults + positive + percent_white +  (Day | State),#Random intercepts and slopes when we put Day in
   data = Finaldata, family = gaussian,
-  chains = 4, iter = 100, refresh = 0
+  chains = 4, iter = 5000*2, refresh = 0
 )
@@
 ```{r}
-head(data.frame(summary(model_2)),-2)
+head(data.frame(summary(model_100)),-2)
 ```
-
-#Quinn makes models
-```{r, warning = FALSE, cache=TRUE}
-model_3 <- stan_glmer(
-  ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
-  data = Finaldata, family = gaussian,
-  chains = 4, iter = 100, refresh = 0
-)
+```{r}
+mcmc_trace(model_100)
+mcmc_dens_overlay(model_100) #How can we just get a snapshot of our model evals?
 ```
@@
 ```{r}
-head(data.frame(summary(model_3)),-2)
-```
-
-#Quinn makes models
-```{r, warning = FALSE, cache=TRUE}
-model_4 <- stan_glmer(
-  ChinaVirusInterest ~ Day + totalTestResults + (Day | State),#Random intercepts and slopes when we put Day in
-  data = Finaldata, family = gaussian,
-  chains = 4, iter = 100, refresh = 0
-)
+pp_check(model_100)
 ```
@@
 ```{r}
-head(data.frame(summary(model_4)),-2)
+set.seed(454)
+pred_1 <- posterior_predict(
+  model_100,
+  newdata = Finaldata, transform = TRUE)
+
+prediction_summary(y = Finaldata$ChinaVirusInterest,
+  yrep = pred_1)
 ```
 
-```{r, warning = FALSE, cache=TRUE}
-model_5 <- stan_glmer(
-  ChinaVirusInterest ~ Day + totalTestResults + positive + percent_white +  (Day | State),#Random intercepts and slopes when we put Day in
-  data = Finaldata, family = gaussian,
-  chains = 4, iter = 100, refresh = 0
-)
+```{r}
+### For predicting one case 
+new_FL <- data.frame(Day = 7 , State = FL) #Doesn't recognize state
 
+set.seed(454)
+pred_FL <- posterior_predict(
+  model_100,
+  newdata = new_FL)
+
+pred_100 <- data.frame(y_new = pred_100[-1])
+
+ggplot(pred_100, aes(x=y_new))+geom_density()
+
+summary(pred_100)
+
+```
+
+```{r}
+# For correlation check (type like model 2 from activity 19)
+# Store the chains
+model_100_df <- as.array(model_100) %>%
+  melt %>%
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_100_df <- model_100_df %>%
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_100_df, aes(x = correlation)) +
+  geom_density(alpha = 0.5)
 ```

### 2020-04-30 Checkpoint 4.Rmd
Fed's models

@@
 ### For predicting one case 
-new_FL <- data.frame(Day = 7 , State = FL) #Doesn't recognize state
+new_FL <- data.frame(Day = 7 , State = "FL") #Doesn't recognize state
 
@@
 ```{r}
-set.seed(454)
 glimpse(Finaldata)
@@
   mutate(Date = as.numeric(Day))%>%
-  mutate(positive_rate = positive/ totalTestResults)%>%
-  select(State, ChinaVirusInterest, Day, percent_white,positive_rate)
+  mutate(positive_rate = positive/ totalTestResults,
+         ChinaVirusInterest_dec = ChinaVirusInterest/100)%>%
+  select(State, ChinaVirusInterest, Day, percent_white,positive_rate,ChinaVirusInterest_dec)
 model_data<- na.omit(model_data)
@@
 ```{r}
+model_data<-model_data%>%
+  select(-c(ChinaVirusInterest))
 set.seed(454)
@@
 model_13 <- stan_glmer(
-  ChinaVirusInterest ~ (Day | State) + percent_white +positive_rate,
+  ChinaVirusInterest_dec ~ (Day | State) + percent_white + positive_rate,
   data = model_data, family = gaussian, chains = 4, iter = 3000
@@
 head(data.frame(summary(model_13)),-2)
+```
+
+```{r}
+pp_check(model_13)
 ```
@@
   geom_density(alpha = 0.5)
+```
+```{r}
+set.seed(454)
+pred_13 <- posterior_predict(
+  model_13,
+  newdata = model_data, transform = TRUE)
+
+prediction_summary(y = model_data$ChinaVirusInterest,
+  yrep = pred_13)
+```
+#Final model Fed
+```{r}
+### For predicting one case
+
+new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) #Doesn't recognize state
+set.seed(454)
+pred_FL <- posterior_predict(
+  model_13,
+  newdata = new_FL)
+
+pred_FL <- data.frame(y_new = pred_FL[-1])
+
+ggplot(pred_FL, aes(x=y_new))+geom_density()
+
+summary(pred_FL)
 ```

### 2020-04-30 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd

@@
 model_5 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+  ChinaVirusInterest ~ StateColor + (1 | State), #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 3, iter = 100*2
 )
@@
 #set.seed(454)
-#my_data <- data.frame(StateColor = "red", State = "FL")
+my_data <- data.frame(StateColor = "red", State = "FL")
 
 # Simulate a set of predictions for each case in newdata
-#my_prediction <- posterior_predict(
- # model_5, 
-  #newdata = my_data)
+my_prediction <- posterior_predict(
+ model_5,
+  newdata = my_data)
 
-#my_prediction <- data.frame(y_new = my_prediction[,1])
+my_prediction <- data.frame(y_new = my_prediction[,1])
 
-#ggplot(my_prediction, aes(x = y_new)) + 
- # geom_density()
+ggplot(my_prediction, aes(x = y_new)) +
+ geom_density()
 
-#summary(my_prediction)
+summary(my_prediction)
 ```

### 2020-04-30 Checkpoint 4.Rmd
fixing predictions

--- 2020-04-30 Checkpoint 4.Rmd
@@
 mcmc_trace(model_100)
-mcmc_dens_overlay(model_100) #How can we just get a snapshot of our model evals?
+mcmc_dens_overlay(model_100) 
 ```
@@
 
+# pred_5 <- posterior_predict(
+#   model_5,
+#   newdata = Finaldata, transform = TRUE)
+
 prediction_summary(y = Finaldata$ChinaVirusInterest,
   yrep = pred_1)
+
+# prediction_summary(y = Finaldata$ChinaVirusInterest,
+#   yrep = pred_5)
 ```
@@
 ### For predicting one case 
-new_FL <- data.frame(Day = 7 , State = "FL") #Doesn't recognize state
+new_FL <- Finaldata%>% 
+          filter(State=="FL") #filter the row of interest
 
@@
 
-pred_100 <- data.frame(y_new = pred_100[-1])
+pred_2 <- data.frame(y_new = pred_FL[-1])
 
-ggplot(pred_100, aes(x=y_new))+geom_density()
+ggplot(pred_2, aes(x=y_new))+geom_density()
 
-summary(pred_100)
+summary(pred_2)
 
@@
 # Store the chains
-model_100_df <- as.array(model_100) %>%
+model_2_df <- as.array(model_2) %>%
   melt %>%
@@
 # Note the need for `...` around the sigma_sq_b
-model_100_df <- model_100_df %>%
+model_2_df <- model_2_df %>%
   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
@@
 
-ggplot(model_100_df, aes(x = correlation)) +
+ggplot(model_2_df, aes(x = correlation)) +
   geom_density(alpha = 0.5)

### 2020-04-30 Checkpoint 4.Rmd
stuff

@@
 ### For predicting one case 
-new_FL <- Finaldata%>% 
-          filter(State=="FL") #filter the row of interest
+new_CA <- Finaldata%>% 
+          filter(State=="CA") #filter the row of interest
 
 set.seed(454)
-pred_FL <- posterior_predict(
+pred_CA <- posterior_predict(
   model_100,
-  newdata = new_FL)
+  newdata = new_CA)
 
-pred_2 <- data.frame(y_new = pred_FL[-1])
+pred_2 <- data.frame(y_new = pred_CA[-1])
 

### 2020-04-30 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd

--- 2020-04-30 Checkpoint 4.Rmd
@@
 
-Variables of Interest: 
-\
-• per_capita_income
-\
-•totalTestResults
-\
-• StateColor
-\
-• percent_asian
-\
-•percent_black
-
 ##Model 5:
@@
 model_5 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor + (1 | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 3, iter = 100*2
+  ChinaVirusInterest ~ Day + StateColor + (Day | State), #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
 )
@@
   geom_density(alpha = 0.5)
-
 ```
@@
 #set.seed(454)
-my_data <- data.frame(StateColor = "red", State = "FL")
+my_data <- data.frame(StateColor = "blue", State = "FL", Day = 18336)
 
@@
 summary(my_prediction)
-```
-
-##Model 7: 
-StateColor + percent_asian + (StateColor | State)
-
-```{r, warning = FALSE, cache=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
-
-model_7 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor + percent_asian + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
-)
-```
-
-```{r}
-head(data.frame(summary(model_7)),-2)
-```
-
-```{r}
-# y = original sample, yrep = MCMC simulation
-set.seed(454)
-pp_check(model_7, nreps = 50)
-```
-
-```{r}
-# Store the chains
-model_7_df <- as.array(model_7) %>% 
-  melt %>% 
-  pivot_wider(names_from = parameters, values_from = value)
-
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_7_df <- model_7_df %>% 
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
-  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))
-
-ggplot(model_7_df, aes(x = correlation)) + 
-  geom_density(alpha = 0.5)
-
-```
-
-```{r}
-# set.seed(454)
-# my_data <- data.frame(StateColor = "blue", State = "IL", percent_asian = .12)
-# 
-# # Simulate a set of predictions for each case in newdata
-# my_prediction <- posterior_predict(
-#   model_7,
-#   newdata = my_data)
-
-#my_prediction <- data.frame(y_new = my_prediction[,1])
-
-#ggplot(my_prediction, aes(x = y_new)) +
- # geom_density()
-
-#summary(my_prediction)
 ```
@@
 #set.seed(454)
-#my_data <- data.frame(StateColor = "red", State = "FL")
+my_data <- data.frame(StateColor = "red", State = "FL")
 
 # Simulate a set of predictions for each case in newdata
-#my_prediction <- posterior_predict(
- # model_5, 
-  #newdata = my_data)
+my_prediction <- posterior_predict(
+  model_9,
+   newdata = my_data)
 
-#my_prediction <- data.frame(y_new = my_prediction[,1])
+my_prediction <- data.frame(y_new = my_prediction[,1])
 
-#ggplot(my_prediction, aes(x = y_new)) + 
- # geom_density()
+ggplot(my_prediction, aes(x = y_new)) +
+ geom_density()
 
-#summary(my_prediction)
+summary(my_prediction)
 ```
+
+ChinaVirusInterest ~ Day + StateColor + (Day | State)	mean	mcse	sd	X10.	X50.	X90.	n_eff	Rhat
+	(Intercept)	-1.94E+04	4.20E+01	6.48E+03	-2.77E+04	-1.94E+04	-1.11E+04	23821
+	Day	1.06E+00	2.29E-03	3.54E-01	6.06E-01	1.06E+00	1.51E+00	23821
+	StateColorpurple	-4.47E-01	3.93E-02	3.96E+00	-5.46E+00	-4.45E-01	4.57E+00	10177
+	StateColorred	-4.09E+00	3.24E-02	3.35E+00	-8.39E+00	-4.09E+00	1.79E-01	10690
+
+ChinaVirusInterest ~ StateColor + percent_asian + (Day | State)								
+	(Intercept)	4.36E+01	3.80E-02	3.16E+00	3.96E+01	4.35E+01	4.76E+01	6895
+	StateColorpurple	-8.65E-01	5.00E-02	4.23E+00	-6.28E+00	-8.61E-01	4.40E+00	7182
+	StateColorred	-4.48E+00	4.29E-02	3.68E+00	-9.18E+00	-4.50E+00	2.35E-01	7384
+	percent_asian	-8.57E+00	3.33E-01	3.10E+01	-4.82E+01	-8.11E+00	3.03E+01	8710
+
+ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State)								
+	(Intercept)	4.27E+01	7.19E-02	3.00E+00	3.90E+01	4.27E+01	4.65E+01	1741
+	StateColorpurple	-2.52E-01	9.18E-02	4.05E+00	-5.38E+00	-2.01E-01	4.85E+00	1949
+	StateColorred	-3.82E+00	9.17E-02	3.77E+00	-8.63E+00	-3.87E+00	8.40E-01	1685
+	percent_asian	-1.07E+01	5.48E-01	2.86E+01	-4.61E+01	-1.05E+01	2.60E+01	2720
+	totalTestResults	3.17E-04	4.75E-06	2.78E-04	-4.82E-05	3.19E-04	6.61E-04	3409
 

### 2020-04-30 Checkpoint 4.Rmd

@@
 ### For predicting one case 
-new_FL <- data.frame(Day = 7 , State = "FL") #Doesn't recognize state
+new_CA <- Finaldata%>% 
+          filter(State=="CA") #filter the row of interest
 
 set.seed(454)
-pred_FL <- posterior_predict(
+pred_CA <- posterior_predict(
   model_100,
-  newdata = new_FL)
+  newdata = new_CA)
 
-pred_100 <- data.frame(y_new = pred_100[-1])
+pred_2 <- data.frame(y_new = pred_CA[-1])
 
-ggplot(pred_100, aes(x=y_new))+geom_density()
+ggplot(pred_2, aes(x=y_new))+geom_density()
 
-summary(pred_100)
+summary(pred_2)
 
@@
 my_data <- data.frame(StateColor = "blue", State = "FL", Day = 18336)
+# Simulate a set of predictions for each case in newdata
+#my_prediction <- posterior_predict(
+ # model_5, 
+  #newdata = my_data)
 
-# Simulate a set of predictions for each case in newdata
-my_prediction <- posterior_predict(
- model_5,
-  newdata = my_data)
+#my_prediction <- data.frame(y_new = my_prediction[,1])
 
-my_prediction <- data.frame(y_new = my_prediction[,1])
+#ggplot(my_prediction, aes(x = y_new)) + 
+ # geom_density()
 
-ggplot(my_prediction, aes(x = y_new)) +
- geom_density()
-
-summary(my_prediction)
+#summary(my_prediction)
 ```

### 2020-04-30 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd
tables

@@
 ```{r}
-# model_15<-stan_glmer(
-#   ChinaVirusInterest ~ (Day|State) + negative_rate, 
-#   data=mod_data, family=gaussian, chains =4, iter = 5000
-# )
+model_15<-stan_glmer(
+  ChinaVirusInterest ~ (Day|State) + negative_rate,
+  data=mod_data, family=gaussian, chains =4, iter = 5000
+)
 ```
@@
 ```{r}
-# head(data.frame(summary(model_15)),-2)
+head(data.frame(summary(model_15)),-2)
 ```
@@
 ```{r}
-# # Store the chains
-# model_15_df <- as.array(model_15) %>% 
-#   melt %>% 
-#   pivot_wider(names_from = parameters, values_from = value)
-# 
-# # Wrangle the chains
-# # Note the need for `...` around the sigma_sq_b
-# model_15_df <- model_15_df %>% 
-#   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
-#   mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-# 
-# ggplot(model_15_df, aes(x = correlation)) + 
-#   geom_density(alpha = 0.5)
+# Store the chains
+model_15_df <- as.array(model_15) %>%
+  melt %>%
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+# Note the need for `...` around the sigma_sq_b
+model_15_df <- model_15_df %>%
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
+  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
+
+ggplot(model_15_df, aes(x = correlation)) +
+  geom_density(alpha = 0.5)
 ```
@@
 ```
+
+Model Outputs:
+
+Model 14: 
+ChinaVirusInterest~ (1|State) + negative_rate
+
+mean	mcse	sd	X10.	X50.	X90.	n_eff	Rhat
+
+44.38040197	0.11616343	4.2066034	39.0747590	44.36959567	49.6577069	1311	1.0010474
+-4.03732266	0.13077873	4.8298203	-10.2151294	-4.12905314	2.2624868	1364	1.0007950
+
+Model 16: 
+ChinaVirusInterest~ (1|State) + percent_black + negative_rate
+
+mean	mcse	sd	X10.	X50.	X90.	n_eff	Rhat
+
+(intercept) 45.38818892	0.059114913	4.851982	39.1598750	45.42176405	51.6208513	6737	1.0001366
+percent black -4.81756453	0.218542483	14.099591	-22.6838613	-5.02290077	13.1161595	4162	1.0008973
+negative_rate -4.48821663	0.053252003	4.937795	-10.7851047	-4.47175240	1.7764630	8598	1.0002747

### 2020-04-30 Checkpoint 4.Rmd
cleaning house

@@
 require(bayesplot)
-```
-
-```{r}
-################################## To do before Alicia with your fave model ##########################################
-# mcmc_trace()
-# mcmc_dens_overlay()
-# pp_check()
-
-### For predicting one case 
-          # new_308 <- data.frame(Days = 9, Subject =308)
-          # 
-          # set.seed(454)
-          # pred_308 <- posterior_predict(
-          #   model_4, 
-          #   newdata = new_308)
-          # 
-          # pred_308 <- data.frame(y_new = pred_308[-1])
-          # 
-          # ggplot(pred_308, aes(x=y_new))+geom_density()
-          # 
-          # summary(pred_308)
-
-## For correlation check (type like model 2 from activity 19)
-          # Store the chains
-          # model_1_df <- as.array(model_1) %>% 
-          #   melt %>% 
-          #   pivot_wider(names_from = parameters, values_from = value)
-          # 
-          # # Wrangle the chains
-          # # Note the need for `...` around the sigma_sq_b
-          # model_1_df <- model_1_df %>% 
-          #   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[Region:(Intercept),(Intercept)]`) %>% 
-          #   mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-          # 
-          # ggplot(model_1_df, aes(x = correlation)) + 
-          #   geom_density(alpha = 0.5)
 ```
@@
 #Quinn making models
-```{r, cahce=TRUE}
-# 
-# model_1 <- stan_glmer(
-#   ChinaVirusInterest ~ (1 | State), #Gives us random intercepts
-#   data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
-# )
-```
-
-```{r}
-# head(data.frame(summary(model_1)),-2)
-```
-
-#Quinn making models
-```{r, warning=FALSE, cache=TRUE}
-# model_2 <- stan_glmer(
-#   ChinaVirusInterest ~ Day + (Day | State),
-#   data = Finaldata, family = gaussian,
-#   chains = 4, iter = 100, refresh = 0
-# )
-
-```
-
-```{r}
-# head(data.frame(summary(model_2)),-2)
-```
-
-#Quinn makes models
-```{r, warning = FALSE, cache=TRUE}
-# model_3 <- stan_glmer(
-#   ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
-#   data = Finaldata, family = gaussian,
-#   chains = 4, iter = 100, refresh = 0
-# )
-```
-
-```{r}
-# head(data.frame(summary(model_3)),-2)
-```
-
-#Quinn makes models
-```{r, warning = FALSE, cache=TRUE}
-# model_4 <- stan_glmer(
-#   ChinaVirusInterest ~ Day + totalTestResults + (Day | State),#Random intercepts and slopes when we put Day in
-#   data = Finaldata, family = gaussian,
-#   chains = 4, iter = 100, refresh = 0
-# )
-```
-
-```{r}
-# head(data.frame(summary(model_4)),-2)
-```
 
@@
 
-# pred_5 <- posterior_predict(
-#   model_5,
-#   newdata = Finaldata, transform = TRUE)
-
 prediction_summary(y = Finaldata$ChinaVirusInterest,
   yrep = pred_1)
-
-# prediction_summary(y = Finaldata$ChinaVirusInterest,
-#   yrep = pred_5)
 ```
@@
 ### For predicting one case 
-new_CA <- Finaldata%>% 
-          filter(State=="CA") #filter the row of interest
+new_IL <- Finaldata%>% 
+          filter(State=="IL") #filter the row of interest
 
 set.seed(454)
-pred_CA <- posterior_predict(
+pred_IL <- posterior_predict(
   model_100,
-  newdata = new_CA)
+  newdata = new_IL)
 
-pred_2 <- data.frame(y_new = pred_CA[-1])
+pred_2 <- data.frame(y_new = pred_IL[-1])
 
@@
 
-```
-
-```{r}
-# For correlation check (type like model 2 from activity 19)
-# Store the chains
-model_2_df <- as.array(model_2) %>%
-  melt %>%
-  pivot_wider(names_from = parameters, values_from = value)
-
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_2_df <- model_2_df %>%
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
-  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-
-ggplot(model_2_df, aes(x = correlation)) +
-  geom_density(alpha = 0.5)
 ```
@@
 #set.seed(454)
-my_data <- data.frame(StateColor = "blue", State = "FL", Day = 18336)
-# Simulate a set of predictions for each case in newdata
-#my_prediction <- posterior_predict(
- # model_5, 
-  #newdata = my_data)
 
-#my_prediction <- data.frame(y_new = my_prediction[,1])
-
-#ggplot(my_prediction, aes(x = y_new)) + 
- # geom_density()
-
-#summary(my_prediction)
-```
-
-##Model 9:
-
-StateColor +percent_asian + totalTestResults + (StateColor | State)
-
-```{r, warning = FALSE, cache=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
-
-model_9 <- stan_glmer(
-  ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State), #Gives us random intercepts
-  data = Finaldata, family = gaussian, chains = 4, iter = 1000*2
-)
-```
-
-```{r}
-head(data.frame(summary(model_9)),-2)
-```
-
-```{r}
-# y = original sample, yrep = MCMC simulation
-set.seed(454)
-pp_check(model_9, nreps = 50)
-```
-
-```{r}
-# Store the chains
-model_9_df <- as.array(model_9) %>% 
-  melt %>% 
-  pivot_wider(names_from = parameters, values_from = value)
-
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_9_df <- model_9_df %>% 
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
-  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))
-
-ggplot(model_9_df, aes(x = correlation)) + 
-  geom_density(alpha = 0.5)
-
-```
-
-```{r}
-#set.seed(454)
-my_data <- data.frame(StateColor = "red", State = "FL")
-
-# Simulate a set of predictions for each case in newdata
 my_prediction <- posterior_predict(
-  model_9,
-   newdata = my_data)
+  model_5,
+  newdata = new_IL)
 
@@
 ```
-```{r}
-model_10 <- stan_glmer(
-  ChinaVirusInterest ~ Day + (1 | State) + percent_white,
-  data = model_data, family = gaussian, chains = 4, iter = 1000
-)
-```
-```{r}
-head(data.frame(summary(model_10)),-2)
-```
-
-```{r}
-# Store the chains
-model_10_df <- as.array(model_10) %>% 
-  melt %>% 
-  pivot_wider(names_from = parameters, values_from = value)
-
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_10_df <- model_10_df %>% 
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
-  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-
-ggplot(model_10_df, aes(x = correlation)) + 
-  geom_density(alpha = 0.5)
-```
-```{r}
-set.seed(454)
-#random intercept and random slope, percent white
-model_11 <- stan_glmer(
-  ChinaVirusInterest ~ (Day | State) + percent_white,
-  data = model_data, family = gaussian, chains = 4, iter = 3000
-)
-```
-```{r}
-head(data.frame(summary(model_11)),-2)
-```
-
-```{r}
-# Store the chains
-model_11_df <- as.array(model_11) %>% 
-  melt %>% 
-  pivot_wider(names_from = parameters, values_from = value)
-
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_11_df <- model_11_df %>% 
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
-  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-
-ggplot(model_10_df, aes(x = correlation)) + 
-  geom_density(alpha = 0.5)
-```
-
-```{r}
-set.seed(454)
-
-model_12<- stan_glmer(
-  ChinaVirusInterest ~ Day + (1 | State) + percent_white +positive_rate,
-  data = model_data, family = gaussian, chains = 4, iter = 3000
-)
-```
-```{r}
-head(data.frame(summary(model_12)),-2)
-```
-
-```{r}
-# Store the chains
-model_12_df <- as.array(model_12) %>% 
-  melt %>% 
-  pivot_wider(names_from = parameters, values_from = value)
-
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_12_df <- model_12_df %>% 
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
-  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-
-ggplot(model_12_df, aes(x = correlation)) + 
-  geom_density(alpha = 0.5)
-```
 
@@
 
-Model 14
-```{r}
-set.seed(454)
-#Neg Rate
-model_14 <- stan_glmer(
-  ChinaVirusInterest ~ (1 | State) + negative_rate,
-  data = mod_data, family = gaussian, chains = 4, iter = 1000
-)
-```
-
-```{r}
-head(data.frame(summary(model_14)),-2)
-```
-
-Checking Model 14
-```{r}
-mcmc_trace(model_14)
-mcmc_dens(model_14)
-```
-```{r}
-pp_check(model_14, nreps=50)
-```
-
-```{r}
-# Store the chains
-model_14_df <- as.array(model_14) %>% 
-  melt %>% 
-  pivot_wider(names_from = parameters, values_from = value)
-
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_14_df <- model_14_df %>% 
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
-  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-
-ggplot(model_14_df, aes(x = correlation)) + 
-  geom_density(alpha = 0.5)
-```
-
-```{r}
-set.seed(454)
-my_data <- data.frame(negative_rate = .9, State = "IL", percent_black = .12)
-
- # Simulate a set of predictions for each case in newdata
-my_prediction <- posterior_predict(
-   model_14,
-   newdata = my_data)
-
-my_prediction <- data.frame(y_new = my_prediction[,1])
-
-ggplot(my_prediction, aes(x = y_new)) +
-  geom_density()
-
-summary(my_prediction)
-```
-
-```{r}
-model_15<-stan_glmer(
-  ChinaVirusInterest ~ (Day|State) + negative_rate,
-  data=mod_data, family=gaussian, chains =4, iter = 5000
-)
-```
-
 ```{r}
 head(data.frame(summary(model_15)),-2)
-```
-
-```{r}
-# Store the chains
-model_15_df <- as.array(model_15) %>%
-  melt %>%
-  pivot_wider(names_from = parameters, values_from = value)
-
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_15_df <- model_15_df %>%
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
-  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-
-ggplot(model_15_df, aes(x = correlation)) +
-  geom_density(alpha = 0.5)
 ```

### 2020-04-30 Checkpoint 4.Rmd
Changes

@@
 )
-
 ```
@@
 
-ChinaVirusInterest ~ StateColor + percent_asian + (Day | State)								
+ChinaVirusInterest ~ StateColor + percent_asian + totalTestResults + (Day | State)								
 	(Intercept)	4.36E+01	3.80E-02	3.16E+00	3.96E+01	4.35E+01	4.76E+01	6895
@@
 	percent_asian	-8.57E+00	3.33E-01	3.10E+01	-4.82E+01	-8.11E+00	3.03E+01	8710
-
-ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State)								
-	(Intercept)	4.27E+01	7.19E-02	3.00E+00	3.90E+01	4.27E+01	4.65E+01	1741
-	StateColorpurple	-2.52E-01	9.18E-02	4.05E+00	-5.38E+00	-2.01E-01	4.85E+00	1949
-	StateColorred	-3.82E+00	9.17E-02	3.77E+00	-8.63E+00	-3.87E+00	8.40E-01	1685
-	percent_asian	-1.07E+01	5.48E-01	2.86E+01	-4.61E+01	-1.05E+01	2.60E+01	2720
-	totalTestResults	3.17E-04	4.75E-06	2.78E-04	-4.82E-05	3.19E-04	6.61E-04	3409
 
@@
 model_16<-stan_glmer(
-  ChinaVirusInterest~ (1|State) + percent_black + negative_rate, 
+  ChinaVirusInterest~ (1|State) + percent_white + negative_rate, 
   data = mod_data, family = gaussian, chains = 4, iter = 5000
@@
 # model_17<-stan_glmer(
-#   ChinaVirusInterest~ (Day|State) + percent_black + negative_rate, 
+#   ChinaVirusInterest~ (Day|State) + percent_white + negative_rate, 
 #   data = mod_data, family = gaussian, chains = 4, iter = 2*5000

### 2020-04-30 Checkpoint3.Rmd
Changes

@@
 
-### `Demographic:`
+`Demographic:`
 Our dataset, `Demographic`, was created by merging three other datasets which all contained different demographic and election information.
@@
 
-### `COVID-19 Cases`
+`COVID-19 Cases`
 The COVID-19 data is provided by The COVID Tracking Project(CTP).

### 2020-04-30 Draft-Report.Rmd
Changes

--- 2020-04-30 Checkpoint3.Rmd
@@
 ---
-title: "Checkpoint 3"
-author: "Quinn Rafferty, Sofia Pozsonyiova, Will Madairy, Federico Chung"
-date: "4/24/2020"
-output: 
-  html_document:
-    toc: true
-    toc_float: true
+title: "Draft Final Project"
+author: "Sofia Pozsonyiova"
+date: "4/30/2020"
+output: html_document
 ---
-
-\
-\
 
@@
 
+```{r, include=FALSE, warning=FALSE}
+prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
+  # Calculate summary statistics of simulated 
+  # posterior predictive models for each case
+  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
+  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
+  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
+  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
+  df <- data.frame(yrep) %>% 
+    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
+    unlist() %>% 
+    matrix(., length(y), 8) %>% 
+    data.frame()
+  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
+  data.frame(cbind(y, df))
+}
+
+prediction_summary <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
+  # This function summarizes the predictions across all cases
+  pred_data <- prediction_summary_data(y, yrep, prob_inner = prob_inner, prob_outer = prob_outer) %>% 
+    mutate(error = y - post_median) %>% 
+    mutate(error_scaled = error / post_mad) %>% 
+    mutate(within_inner = (y >= l_inner) & (y <= u_inner)) %>% 
+    mutate(within_outer = (y >= l_outer) & (y <= u_outer))
+
+  pred_summary <- pred_data %>% 
+    summarize(mae = median(abs(error)), 
+      mae_scaled = median(abs(error_scaled)),
+      within_inner = mean(within_inner),
+      within_outer = mean(within_outer)
+    )
+  names(pred_summary)[3] <- paste0("within_", prob_inner*100)
+  names(pred_summary)[4] <- paste0("within_", prob_outer*100)
+
+  pred_summary
+}
+```
+
 \
@@
 
-# Data
-```{r}
-Finaldata<- read.csv("time_series_final_Data.csv")
+# 1. Introduction
+
+\
+\
+
+# 2 The Data Set
+
+```{r results = "hide", echo=FALSE, warning=FALSE}
+Finaldata<-read_csv("time_series_final_Data.csv")
+
+Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
+day_initial<- as.Date("2020-03-14")
+day_final<- as.Date("2020-03-21")
+Finaldata<- Finaldata%>%
+  filter(Day>=day_initial)%>%
+  filter(Day<=day_final)
 ```
 
-```{r}
-google<-read.csv("Google/googlefinal.csv")
-names(google)
-```
-
-## Re-Cleaned 
-```{r} 
-google <- google %>%  select(-c(X.1))
-Finaldata <- Finaldata %>% select(-c(X)) 
-Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
-```
-
-## Dataset Description
+## 2.1 Data Description
 
@@
 
-`COVID-19 Cases`
+`COVID-19 Cases:`
 The COVID-19 data is provided by The COVID Tracking Project(CTP).
@@
 
-### `Google Search Interest`
+`Google Search Interest:`
 This data set includes two search interest indexes over time, measuring how people in each of the state’s interest in searching either “Kung Flu” or “China Virus” based on the time frame selected in the search.
@@
 
-## Dataset Details 
-```{r}
+## 2.2 Data Information
+
+```{r warning=FALSE}
 dim(Finaldata)
@@
 
-## Variables of Interest
+## 2.3 Variables of Interest
 
@@
 
-\
-\
+##2.4 Visualizations
 
-# Visualizations
-
-## Google Set
-```{r}
-Trump<- as.Date("03/16/2020", format = "%m/%d/%Y")
-day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
-day2<-as.Date("03/24/2020",format = "%m/%d/%Y")
-
-google_ts<-google%>%
-  mutate(Day = as.Date(as.character(Day)))
-
-a<-google_ts %>% 
-  #filter(Day<=day2)%>%
-  #filter(Day>=day1)%>%
-  group_by(Region, Day) %>% 
-  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
-  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
-  geom_point()
-
-ggplotly(a)
-```
-
-This plot shows the relationship of “China Virus” search interest over grouped by region.
-This plots shows that there are certainly key events that trigger an uptick in searches overall.
-In this plot it is not clear which region may search China Virus more or less often, but it does show a that the regions move together in search interest, which would imply federal level events like a Donald Trump tweet to trigger these interest spikes.
-
-## Demographic 
+###Demographic 
 ```{r}
 #Demographic: Identification 
-## Might not use, how helpful is this? Possibly combine into a shiny app so people could adjust for which race to look at? 
 Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
@@
 
+MAKE VISUAL FOR STATE COLOR
+
 ```{r}
-#By income 
-plot_usmap(data = Finaldata, values = "per_capita_income", color = "white") + 
-  scale_fill_continuous(low = "sky blue", high = "black", name = "$ Per Capita", label = scales::comma) + 
-  theme(legend.position = "right") + ggtitle("Income per Capita")+
-  theme(
-plot.title = element_text(color="Black", size=14, face="bold")
-) 
+ggplot(data = Finaldata, x = StateColor) + stat_count()
 ```
 
-We also wanted to take a look at the `per capita income` variable, as we believe it could be valuable within our analysis.
-Specifically, we are thinking that it could possibly be an indicator for the amount COVID Cases and or could really affect an individuals reaction to Trump's tweet.
-This visualization however, is just uni-variate as we wanted to understand the variable a bit more.
-As you can see, the Northeast and the West coast tend to have higher incomes per capita than places like the South for instance.
+###Google TS
 
-```{r}
-#Income by state affiliation 
-g <- ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")
+###COVID-19
 
-g + scale_fill_manual(values=c("blue", "purple", "red"))
-```
-
-After learning more about the `per capita income` variable we wanted to see how the variable would change when we added `State Color` into the mix.
-Where `State Color` signifies a state's political leaning during the election.
-What is interesting is that the states that were red had much lower incomes per capita than states that were blue.
-We see that the blue states had a much wider and higher spread of income per capita ranging all the way to $45,000.
-Purple states on the other hand tended to be in the middle.
-
-```{r}
-#Trump Support 
-ggplot(Finaldata, aes(x = percent_republican2016)) + 
-    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density") + facet_wrap(~Region)
-```
-
-This visualization is looking at Trump Support during the 2016 elections across different U.S.
-regions.
-From these visualizations it seems as though each region had pretty varying support.
-The Northeast had this interesting peak at 0.4 but also has another slope at around 0.
-The Western and Mountain regions have a similar pattern happening where there are strong peaks but then those peaks start dipping down fairly drastically.
-The South and the Midwest tend to lean more towards higher Trump support and we don't see the "dipping" occur as much.
-This leads us to believe that during that election those regions had more states that favored Trump and the Republican party.
-
-```{r}
-ggplot(Finaldata, aes(x = percent_asian, y = percent_republican2016, color = Winner)) + 
-    scale_color_manual(values = c("blue","purple","red")) + 
-    geom_point(alpha = 0.8) + geom_text(aes(label=ifelse(percent_asian>.2,as.character(state),"")),hjust=1.2,vjust=0)+ geom_text(aes(label=ifelse(percent_republican2016<.2,as.character(state),"")),hjust=-.1,vjust=0) + ggtitle("Percent of Asians and Trump Support by Election Outcome") + xlab("Percent Asian") + ylab("Trump Support")
-
-```
-
-This final demographic visualization is depicting Trump support across all states among those who identify as Asian, and is then classifying whether or not Trump won in that specific state.
-The two outliers are labeled as Hawaii and DC.
-These are interesting because we see that DC had a small percent of Asian residents and also had low Trump support this is kinda expected.
-However, we see that Hawaii had a much larger percentage of Asian identifying residents but also still had a decent amount of Trump support.
-All in all though, this visualization tells us that in a way the states that had lower Asian identifying residents tended to have higher Trump support.
-
-## COVID-19 Cases
-
-```{r}
-## Creating a df of just the cases the week before 3/17
-weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.Date("2020-03-17"))
-
-plot1<- plot_usmap(data = weekbefore, values = "positive", color = "white") + 
-  scale_fill_gradient2(low = "white", high ="blue", mid = "skyblue",midpoint = 30,
-                          name = "Cases (#)",label = scales::comma,
-                          limits = c(0,500)) + 
-  theme(legend.position = "right")+ ggtitle("# of COVID Cases Before 3/17") + 
-  theme(
-plot.title = element_text(color="Black", size=8)
-)
-
-## Creating a df of just the cases the week after 3/17
-weekafter <- data.frame(Finaldata) %>% filter(Day >= as.Date("2020-03-17"))
-
-plot2<-plot_usmap(data = weekafter, values = "positive", color = "white") + 
-   scale_fill_gradient2(low = "white", high ="red", mid = "blue",midpoint = 500,
-                          name = "Cases (#)",label = scales::comma,
-                          limits = c(0,10000)) + 
-  theme(legend.position = "right")+ ggtitle("# of COVID Cases After 3/17") + 
-  theme(
-plot.title = element_text(color="Black", size=5)
-)
-
-# The number of Positive Covid Cases, comparison before and after the China Virus announcement 
-grid.arrange(plot1, plot2, ncol=2)
-```
-
-This visualization allows us to compare the raw count of positive COVID-19 cases among the US before and after March 17th (Trump says "China Virus").
-The goal of this visualization is to show the number of positive COVID-19 cases as the time progresses.
-From the first plot we can see there are very few states that have positive cases above 0-100.
-However, we see states like Washington, Michigan, California and New York have higher numbers.
-The second plot shows that while there are very few states above ~2,000 there overall a higher number of positive cases among the US.
-This intuitively makes sense given this is an infectious disease and we would only expect there to be more positive cases over time.
-
-## Final Dataset
-```{r}
-b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
-  geom_density(alpha = 0.5)
-
-ggplotly(b)
-```
-
-We can see that the variability in Google interest in the term China Virus is has quite a large range between states.
-There are very few states that have high densities among the upper echelons of the interest scale but there are some interesting peaks of densities among the lower values.
-For example, we can see that Alaska, Wyoming and Iowa have unusal peaksaround the 25-50 range.
-It is is also interesitng interesting to note that there isn't an *obvious* mean or median value of China Virus interest among the states.
-
-```{r}
-c<- ggplot(Finaldata, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
-    geom_point() + 
-    geom_smooth(method = "lm", se = FALSE) + 
-    facet_wrap(~ State) + 
-    theme(legend.position = "none")
-
-ggplotly(c)
-```
-
-With this visualization we wanted to observe the different slopes of each slope of interest in the term China Virus over time.
-Arguably, the slopes of interest among the states are not significantly different.
-There are some interesting downward slopes in states like Wyoming but we would need to dig a bit deeper into this to fully understand what it means.
-However, a really interesting facet of this viusalization is that we can see a pattern among all states ofpeaks and valleys.
-In other words, from observation, the majority of states demonstrate a pattern correlated to the day.
-This would be interesting to explore further and see how it interacts with other aspects like number of COVID cases by state.
+###Final Data Set
 
@@
 
-# Building Model
+# 3. Models
 
-$$\begin{aligned}
-i = \text{region, } j = \text{date, } Y = \text{China Virus Interest}\\
-Y_{ij}|b_0,b_1 \sim N(b_{0i} + b_{1i}Day_{i},\sigma^2)\\
-b_{0i} \sim N(...)\\
-b_{1i} \sim N(...)\\
-\end{aligned}$$
+## Model(s)
 
-```{r cache=TRUE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
+## Model Evaluation
 
-model_1 <- stan_glmer(
-  ChinaVirusInterest ~ (1 | Region),
-  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
-)
-```
+\
+\
 
-```{r}
-mcmc_trace(model_1)
-mcmc_dens_overlay(model_1)
-```
-
-From what we can see from the trace plot the intercepts for each region are not very different from each other.
-We could see that it is possible that the midwest and the north east have a higher intercept compared to the west, but the mean is centered around 0 for almost all of them.
-We would rather use states to see if we see differing intercepts through states but unfortunatelly our code did not run.
-
-Our model shows that the chains are stable maybe telling us that the model might work with lower chain iterations.
-
-```{r}
-# Store the chains
-model_1_df <- as.array(model_1) %>% 
-  melt %>% 
-  pivot_wider(names_from = parameters, values_from = value)
-
-# Wrangle the chains
-# Note the need for `...` around the sigma_sq_b
-model_1_df <- model_1_df %>% 
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[Region:(Intercept),(Intercept)]`) %>% 
-  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
-
-ggplot(model_1_df, aes(x = correlation)) + 
-  geom_density(alpha = 0.5)
-```
-
-In our correlation density plot we can see that the values are not very correlated accross regions meaning that regions is probably a bad way to segment them.
-
-```{r}
-head(data.frame(summary(model_1)),-2)
-```
-
-# Next Steps
-The obvious improvements we need to make is exploring more models.
-We can see from our visualizations that are there are a wide variety of relationships we can dig into with our dataset.
-However, as a group, we need to decide what path(s) to take.
-Once we decide on which relationship(s) we want to analyze further, then this project can be enhanced with possibly animiated visualizations or even a shiny app.
-
-# Project Contributions
-- Quinn: Cleaned the COVID-19 data set, provided all visualizations and descriptions of COVID-19, provided the data description, ran analysis of the model, cleaned/formated checkpoint 3 document and knitted/turned in final checkpoint 3 product.
-- Sofia: Cleaned the demographic data set, provided all visualizations and descriptions of demographic aspects, provided the data descriptions for the dataset and created variables of interest table.
-- Will:  Cleaned the Google Trend data set, provided all visualizations and descriptions of the CHina Virus and Kung Flu virus relationships and provided the data descriptions for the dataset.
-- Federico: Merged the datasets and provided brief descriptions of our building model section.
+# 4. Results

### 2020-04-30 Draft-Report.Rmd
introduction

@@
 # 1. Introduction
+
+On March 17, 2020 President Trump referred to the Coronavirus as the "China Virus." Shortly after, the number of anti-Chinese incidents started to increase across the United States.
+One aspect of public health that is often thrown to the wayside is how influential public officials and leaders are in disseminating public health information.
+Moreover, not only can their words change the public's views on a health matter but it can also shift a nation's perspective on someone's identity.
+In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identies and states.
+Thus,our project aims to explore the relationship and variability of intrest in the term "China Virus" across states through  political, demographic and COVID-19 characteristics.
+This was done using _____.
+(Conclusion)
 
@@
 # 4. Results
+
+# 5. Contributions and progress
+
+## 5.1 Contributions
+
+- Specify what each group member (including yourself) contributed to this checkpoint.
+- Quinn: 
+- Sofia:
+- Will:
+- Federico:
+
+## 5.2 Outline progress
+- Summarize what progress your group made between checkpoints 3 and 4.

### 2020-04-30 Draft-Report.Rmd
adding stuff

@@
 
+```{r}
+model_1 <- stan_glmer(
+  ChinaVirusInterest ~ StateColor + positive + percent_white +State, #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+)
+
+model_2 <- stan_glmer(
+  ChinaVirusInterest ~ StateColor + positive + percent_white + (1 | State), #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+)
+
+model_3<- stan_glmer(
+  ChinaVirusInterest ~ Day + StateColor + positive + percent_white + (Day | State), #Gives us random intercepts
+  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+)
+```
+
 ## Model Evaluation

### 2020-05-01 Draft-Report.Rmd
Complex mod

--- 2020-04-30 Draft-Report.Rmd
@@
 ```{r results = "hide", echo=FALSE, warning=FALSE}
+
 Finaldata<-read_csv("time_series_final_Data.csv")
@@
 
-## Model(s)
+## 3.1 Model(s)
 
-## Model Evaluation
+###Complex Model
+
+*White, StateColor, Day, Positive Cases, State
+
+```{r results = "hide", include = FALSE}
+View(Finaldata)
+set.seed(454)
+Finaldata<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day))
+
+complexmod <- stan_glmer(
+  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (Day | State), 
+  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+)
+```
+
+```{r}
+head(data.frame(summary(complexmod)),-2)
+```
+
+## 3.2 Model Evaluation
+
+###Complex Model
+
+```{r}
+# Trace plots
+mcmc_trace(complexmod)
+
+# Density plots
+mcmc_dens_overlay(complexmod)
+```
+
+```{r}
+pp_check(complexmod, nreps = 50)
+```
+
+```{r}
+# Store the chains
+model_complex_df <- as.array(complexmod) %>%
+  melt %>%
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+model_complex_df <- model_complex_df %>%
+  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
+  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))
+
+#Correlation Plot
+ggplot(model_complex_df, aes(x = correlation)) +
+  geom_density(alpha = 0.5)
+```
+
+## 3.3 Model Predictions
+
+###Complex Model
+
+```{r}
+set.seed(454)
+
+new_data <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) 
+new_pred <- posterior_predict(
+  complexmodel,
+  newdata = new_data)
+
+my_pred <- data.frame(y_new = new_pred[-1])
+
+ggplot(my_pred, aes(x=y_new))+geom_density()
+
+summary(my_pred)
+```
 

### 2020-05-01 Draft-Report.Rmd
report changews

@@
 
+```{r}
+Finaldata%>%
+  ggplot(aes(x = ChinaVirusInterest))+
+  geom_density()
+```
+During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns accross states.
+
+As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relativelly normal with a small bump at 0.
+As a group we believe this bump occurs as 0 is the lowest value it can take and because of that limitation of the China Virus Interest we see a small bump around 0.
+One could argue against a normal distribution as it kinda looks a bit right skewed.
+But our team believes that a normal distribution is the best at describing the density.
+
+When China Virus Interest equals 0 it means that no one in the state looked up the term in Google and this is prevalent at the 14 of March where there are 5 occurrences and the 21 of March where there are 4 occurences.
+And in states such as DC, ND, SD, and VT.
+
+```{r}
+Finaldata%>%
+  filter(ChinaVirusInterest ==0)%>%
+  group_by(Day)%>%
+  summarize(n = n())
+```
+
+Because our density plot showed a fairly normal distribution, we decided to use a Normal-Normal model to plot our most simple model.
+As a team we decided to also include 3 variable specifications, to explain the differences in demographic variables we decided to use `percent_white` as it was one of the best variables when we used lasso for variable selection, and it made sense as higher white percentage populations tend to have lower diversity and potentially it can lead to the search of more derrogatory terms such as "China Virus".
+To explain the differences in political factors in the state we decided to use `StateColor`.
+The variable was inspired by a study conducted by Pew Research Center that concluded that Liberal Democrats are more likely to use social media and look up information in the internet.
+By dividing states by their color we could use the color as a proxy to understand which ones had more democrats in their state.
+And finally, we believed that states more affected by COVID-19 would be more inclined to search terms like China Virus, as the virus has had a bigger impact on them which is why we decided to use `positive` (# of positive cases).
+
+```{r}
+model_data<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day)-as.numeric(min(Day)))%>%
+  select(ChinaVirusInterest, Day, percent_white, StateColor, positive)
+
+model_data<- na.omit(model_data)
+```
+
+For our first model we decided to use a simple Normal regression model.
+
+In this model i= the nth observation
+
+$$\begin{aligned}
+Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3,\sigma^2)\\
+\beta_0,\beta_1, \beta_2,\beta_3 \sim N(...,...)\\
+\sigma,\sigma \sim Exp(...)\\
+\end{aligned}$$
+
+```{r}
+set.seed(454)
+model_1 <- stan_glm(
+  ChinaVirusInterest ~ Day + percent_white+StateColor+positive,
+  data = model_data, family = gaussian,
+  chains = 4, iter = 1000, refresh = 0
+)
+model_1
+```
+As we can see in our summary table, we see that the higher the percent_white we see a higher median of China Virus Interest states with higher percent_white populations tend to have higher searches for "China Virus".
+And we also see that compared to State Color Blue state Color Red tends to have -3.2% less searches.
+We also see that the positive number of cases did not change the mean value for China Virus Interest which we found interesting.
+Basically telling us that maybe COVID-related variables do not have a big effect on how much people search for these terms.
+
+```{r}
+head(data.frame(summary(model_1)),-2)
+```
+
+```{r}
+pp_check(model_1)
+```
+Overall, we can see that our simple model it tells us that the structure of our model is fairly reasonable, In other words, the assumption of using a normal model is fairly reasonable outside of the fact that the tails are a bit thicker than we would want them to be.
+
+```{r}
+set.seed(454)
+pred_1 <- posterior_predict(
+  model_1,
+  newdata = model_data, transform = TRUE)
+
+prediction_summary(y = model_data$ChinaVirusInterest,
+  yrep = pred_1)
+```
+In this simple model, we see that the mae value is 10.5, and 55% of the datapoints are within the 50% confidence interval, and 92% are within the 95% confidence interval.
+To be a simple model, it does a fairly good job at capturing the trends.
+
+##Repeated Measures + Normal Regression (WILL) (1|State)**
+
 ###Complex Model
@@
 # 4. Results
+
+# Contributions
+
+Federico did the "Normal Regression Model", and evaluated the model.
+Provided some visualization help by allowing for mcmc_dens plots to be seen without being clustered.
+And I have also evaluated the density plot and why a normal distribution is a good idea.

### 2020-05-01 Draft-Report.Rmd
update

@@
 ---
-title: "Draft Final Project"
-author: "Sofia Pozsonyiova"
-date: "4/30/2020"
-output: html_document
+title: "Checkpoint 4"
+author: "Quinn Rafferty, Sofia Pozsonyiova, Will Madairy, Federico Chung"
+date: "4/24/2020"
+output: 
+  html_document:
+    toc: true
+    toc_float: true
 ---
@@
 
-MAKE VISUAL FOR STATE COLOR
+###Google TS
+```{r}
+Trump<- as.Date("03/16/2020", format = "%m/%d/%Y")
+day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
+day2<-as.Date("03/24/2020",format = "%m/%d/%Y")
+
+google_ts<-google%>%
+  mutate(Day = as.Date(as.character(Day)))
+
+a<-google_ts %>% 
+  #filter(Day<=day2)%>%
+  #filter(Day>=day1)%>%
+  group_by(Region, Day) %>% 
+  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
+  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
+  geom_point()
+
+ggplotly(a)
+```
+
+This plot shows the relationship of “China Virus” search interest over grouped by region.
+This plots shows that there are certainly key events that trigger an uptick in searches overall.
+In this plot it is not clear which region may search China Virus more or less often, but it does show a that the regions move together in search interest, which would imply federal level events like a Donald Trump tweet to trigger these interest spikes.
 
 ```{r}
-ggplot(data = Finaldata, x = StateColor) + stat_count()
+b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
+  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State")
+
+ggplotly(b)
 ```
 
-###Google TS
+We can see that the variability in Google interest in the term China Virus is has quite a large range between states.
+There are very few states that have high densities among the upper echelons of the interest scale but there are some interesting peaks of densities among the lower values.
+For example, we can see that Alaska, Wyoming and Iowa have unusal peaksaround the 25-50 range.
+It is is also interesitng interesting to note that there isn't an *obvious* mean or median value of China Virus interest among the states.
 
@@
 
-###Final Data Set
+```{r}
+c <-  ggplot(Finaldata, aes(y=positive, x=Winner, fill=(Winner)))+
+      geom_boxplot() +
+      facet_wrap(~Region)+
+      theme(legend.position = "none") +
+      scale_fill_manual(values = c("Democrat"="blue3", "Republican"= "red3"))+
+      lims(y= c(0,1000))+
+      ggtitle("Positive COVID-19 Cases by State Political Party Winner & Region")
+ggplotly(c)
+```
 
+(PUT DESCRIPTION)
 \

### 2020-05-01 Draft-Report.Rmd
stuff

@@
 ```
+
 As we can see in our summary table, we see that the higher the percent_white we see a higher median of China Virus Interest states with higher percent_white populations tend to have higher searches for "China Virus".

### 2020-05-01 Draft-Report.Rmd
Update Draft-Report.Rmd
Model 2

@@
 
+*White, StateColor, Day, Positive Cases, State
+
+$$
+Y_{ij}|\theta_i, \mu_, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3,\sigma^2) \\
+\theta|\mu, \sigma_b   \sim N(\mu,\sigma_b) \\
+\mu \sim N(..., ...) \\ 
+\beta_2 \sim N(..., ...) \\
+\beta_3 \sim N(..., ...) \\
+\beta_4 \sim N(..., ...) \\
+$$
+
+In this model using repeated measures the outcome of $Y_{ij}$ is the interest in China Virus on a given day within a state.
+$\mu$ represents the mean value of the interest on Day 0 of the study and how much we would expect.
+The $\theta_{i}$ represents the change from the intercept that each of the states experiences.
+$\beta_2$ represents the variable for the percent of the population that is white and $\beta_3$ represents the variable that corresponds with state color.
+Finally, $\beta_4$ represents the proportion of the population that tests positive for the coronavirus.
+
+```{r}
+View(Finaldata)
+set.seed(454)
+Finaldata<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day))
+
+model_2 <- stan_glmer(
+  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (1 | State), 
+  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
+)
+```
+
+```{r}
+head(data.frame(summary(model_2)),-2)
+```
+
+The output from the table above shows that within our timeframe as day increases, the interest in the coronavirus also increases.
+State color=blue is the default intercept of the model and having state color=purple decreases the interept by 1.89 while in a red state the intercept decreases by 3.7 in the interest index.
+Two other variables fo interest show that percent white and the positive rate both increase interest on average yet neither variable is specifically significant in this model.
+
+```{r}
+pp_check(model_2)
+```
+
+This pp-check is similar to our other models showing a following of the trend with a specific hump around 0.
+This is due to 0 receiving extra weight in our data set than other values we would expect to see.
+
+```{r}
+set.seed(454)
+pred_2 <- posterior_predict(
+  model_2,
+  newdata = Finaldata, transform = TRUE)
+
+prediction_summary(y = Finaldata$ChinaVirusInterest,
+  yrep = pred_2)
+```
+
+Finallly in our analysis of the model we see that the MAE of this model is 8.98 with a within-50 rate of 0.59 and within-95 ratet of 0.965 showing some relaive gains from the first model.
+
 ###Complex Model

### 2020-05-01 Draft-Report.Rmd
F

--- 2020-05-01 Draft-Report.Rmd
@@
 
+################ FEDDY PREDICT FOR FLORIDA TOO please. ALSO MOVE YOUR STUFF TO THE RIGHT PLACES ############
+
 ##Repeated Measures + Normal Regression (WILL) (1|State)**
@@
 
-*White, StateColor, Day, Positive Cases, State
+*White, StateColor, Day, Total test Results, State
 
@@
 complexmod <- stan_glmer(
-  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (Day | State), 
+  ChinaVirusInterest ~ Day + StateColor + percent_white + totalTestResults + (Day | State), 
   data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
@@
 ```
+The assumption of using a Normal model is fairly reasonable besides the fact that we observe two bumps on both sides of the tails. We can assume these to be outliars.
 
@@
 
-new_data <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) 
+new_data <- Finaldata %>% filter(State == "FL")
 new_pred <- posterior_predict(

### 2020-05-01 Draft-Report.Rmd
cleaning

@@
   data = model_data, family = gaussian,
-  chains = 4, iter = 1000, refresh = 0
+  chains = 4, iter = 10000, refresh = 0
 )
 model_1
+
 ```
@@
 
+#### FIX 
 $$
@@
 
-*White, StateColor, Day, Total test Results, State
+*White, StateColor, Day, Total Test Results, State
+
+$$
+\begin{split}
+Y_{ij} | b_0, b_1, \beta_0, \beta_1, \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N(b_{0i} + b_{1i} X_{ij}, \; \sigma_w^2) \\
+b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
+b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
+\beta_0 & \sim N(..., ...) \\
+\beta_1 & \sim N(..., ...) \\
+\sigma_w & \sim Exp(...) \\
+\sigma_{0b} & \sim Exp(...) \\
+\sigma_{1b} & \sim Exp(...) \\
+\end{split}
+$$
 
@@
 complexmod <- stan_glmer(
-  ChinaVirusInterest ~ Day + StateColor + percent_white + totalTestResults + (Day | State), 
+  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (Day | State), 
   data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
@@
 
+### Feddy model eval (model 1)
+
+###Will model eval (model 2)
+
 ###Complex Model
@@
 ```
+The trace and
 
@@
 ###Complex Model 
+```{r}
+set.seed(454)
+pred_complex <- posterior_predict(
+  complexmodel,
+  newdata = Finaldata, transform = TRUE)
+
+prediction_summary(y = model_data$ChinaVirusInterest,
+  yrep = pred_13)
+```
 

### 2020-05-01 Draft-Report.Rmd
Update Draft-Report.Rmd

@@
 
-*White, StateColor, Day, Total Test Results, State
+Variables of Interest: `White`, `StateColor`, `Day`, `Total Test Results`, `State`
 
@@
 # Trace plots
-mcmc_trace(complexmod)
+mcmc_trace(complexmod,pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[Day State:AK]","b[Day State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
 
 # Density plots
-mcmc_dens_overlay(complexmod)
+mcmc_dens_overlay(complexmod, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[Day State:AK]","b[Day State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
 ```
-The trace and
+
+**Comment:** For our MCMCs graphs we chose to just look at our predictors, intercept, and sigma value.
+We sadly cannot visualize all of our random slopes given that we would have over 50.
+However, we did visualize at least a couple of the random slopes as seen above.
+From the MCMC Dens and Trace we see that our chains are all close to each other meaning that our simulation was stable, which is great!
 
@@
 ```
-The assumption of using a Normal model is fairly reasonable besides the fact that we observe two bumps on both sides of the tails. We can assume these to be outliars.
+**Comment:** The assumption of using a Normal model is fairly reasonable besides the fact that we observe two bumps on both sides of the tails. We can assume these to be outliars.
 
@@
   pivot_wider(names_from = parameters, values_from = value)
+model_complex_df
 
@@
 ```
+
+**Comment:** Unfortunately, when we plot the correlation within our dataset we see that it comes out as empty.
+This can be attributed to the complexity of our model.
+What we found through our initial visualization exploration is that when we add additional parameters the correlation tends to decrease.
+This makes sense as a lot of our parameters are specific to each state.
 
@@
 And I have also evaluated the density plot and why a normal distribution is a good idea.
+
+Sofia created the draft report document and organized it so that it would be easier to follow.
+Along with creating and organizing the document, I helped Quinn and Will write the Introduction.
+In addition, Quinn and I worked on making the complex model.
+After we created the model I focused on the model evaluation section for that model, and was able to get our MCMC plots to show.

### 2020-05-01 Draft-Report.Rmd
adding stuff

--- 2020-05-01 Draft-Report.Rmd
@@
 
+Our data set includes not only repeated measures on our response variable $Y$ for each state, it also includes corresponding observations for our preditor variables as well.
+In order to increase the complexity of our model to include these aspects we will use the model strcuture below as a fundamental start point:
+
 $$
@@
 $$
+With this structure our model will be able to account for the differing intercepts based on the day and also the differing slopes we expect to see by state.
 
 ```{r results = "hide", include = FALSE}
-View(Finaldata)
+
 set.seed(454)
@@
 ```
+The output from the table above shows that within our timeframe as day increases, the interest in the China Virus term also increases.
+State color=blue is the default intercept of the model and having state color=purple decreases the interept by 1.02 while in a red state the intercept decreases by 3.6 in the interest index.
+Two other variables fo interest show that percent white and the positive rate both increase interest on average yet neither variable is specifically significant in this model.
 
@@
 pred_complex <- posterior_predict(
-  complexmodel,
+  complexmod,
   newdata = Finaldata, transform = TRUE)
 
-prediction_summary(y = model_data$ChinaVirusInterest,
-  yrep = pred_13)
+prediction_summary(y = Finaldata$ChinaVirusInterest,
+  yrep = pred_complex)
 ```
+Finallly in our analysis of the model we see that the MAE of this model is 9.01.
+Our within-50 rate is 0.60 which means that 60%  of the predictions that fall within our middle 50% of our predictive model.
+Our within our 95 rate is .97 which means that 97% of our predictions fall within the middle 95% of our predictive model.
 
@@
 new_pred <- posterior_predict(
-  complexmodel,
+  complexmod,
   newdata = new_data)
@@
 summary(my_pred)
+
+actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
+
+actual_FL_pred
 ```
+To test the accuracy of the complex model we decided to test our prediction on one case too. We chose Florida as our test state and as you can see from the summaries above our predictions are
+relatively close. The actual mean of interest in the term China Virus in Florida is 47.625 and our model predicted 46.10, this is only a 1.5 difference!
 

### 2020-05-01 Draft-Report.Rmd
Update Draft-Report.Rmd

@@
 
-Our data set includes not only repeated measures on our response variable $Y$ for each state, it also includes corresponding observations for our preditor variables as well.
+**Comment:** Our data set includes not only repeated measures on our response variable $Y$ for each state, it also includes corresponding observations for our preditor variables as well.
 In order to increase the complexity of our model to include these aspects we will use the model strcuture below as a fundamental start point:
@@
 $$
-With this structure our model will be able to account for the differing intercepts based on the day and also the differing slopes we expect to see by state.
+
+**Comment:** With this structure our model will be able to account for the differing intercepts based on the day and also the differing slopes we expect to see by state.
 
@@
 ```
-Finallly in our analysis of the model we see that the MAE of this model is 9.01.
+**Comment:** Finallly in our analysis of the model we see that the MAE of this model is 9.01.
 Our within-50 rate is 0.60 which means that 60%  of the predictions that fall within our middle 50% of our predictive model.
@@
 ```
-To test the accuracy of the complex model we decided to test our prediction on one case too. We chose Florida as our test state and as you can see from the summaries above our predictions are
-relatively close. The actual mean of interest in the term China Virus in Florida is 47.625 and our model predicted 46.10, this is only a 1.5 difference!
+**Comment:**To test the accuracy of the complex model we decided to test our prediction on one case too.
+We chose Florida as our test state and as you can see from the summaries above our predictions are relatively close.
+The actual mean of interest in the term China Virus in Florida is 47.625 and our model predicted 46.10, this is only a 1.5 difference!
 

### 2020-05-01 Draft-Report.Rmd
Update Draft-Report.Rmd

@@
 Moreover, not only can their words change the public's views on a health matter but it can also shift a nation's perspective on someone's identity.
-In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identies and states.
-Thus,our project aims to explore the relationship and variability of intrest in the term "China Virus" across states through  political, demographic and COVID-19 characteristics.
+In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identities and states.
+Thus,our project aims to explore the relationship and variability of interest in the term "China Virus" across states through  political, demographic and COVID-19 characteristics.
 This was done using _____.
@@
 +------------------------+---------------------------------------------------+
-|`hospitalized`          | Total Number of indivudals hopitalized due        |
+|`hospitalized`          | Total Number of individuals hospitalized due        |
 |                        | to COVID-19                                       |
@@
 +------------------------+---------------------------------------------------+
-|`KungFluInterest`       | Interest index from google searches by state.     |
+|`KungFluInterest`       | Interest index from Google searches by state.     |
 |                        | Peak search day=100, all other days in set are    |
@@
 +------------------------+---------------------------------------------------+
-|`ChinaVirusInterest`    | Interest index from google searches by state.     |
+|`ChinaVirusInterest`    | Interest index from Google searches by state.     |
 |                        | Peak search day=100, all other days in set are    |
@@
 Our first visualization is looking at the percent of residents that identify as white within the United States.
-As you can see, there is a higher percent of white identifying residents in the midwest and northeast states.
+As you can see, there is a higher percent of white identifying residents in the Midwest and northeast states.
 From this visualization we can also see that places like Texas, California, and New Mexico have much lower white identifying residents which could provide important information for us in our actual analysis.
@@
 There are very few states that have high densities among the upper echelons of the interest scale but there are some interesting peaks of densities among the lower values.
-For example, we can see that Alaska, Wyoming and Iowa have unusal peaksaround the 25-50 range.
-It is is also interesitng interesting to note that there isn't an *obvious* mean or median value of China Virus interest among the states.
+For example, we can see that Alaska, Wyoming and Iowa have unusual peaks around the 25-50 range.
+It is is also interesting interesting to note that there isn't an *obvious* mean or median value of China Virus interest among the states.
 
@@
 ```
-During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns accross states.
+During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns across states.
 
-As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relativelly normal with a small bump at 0.
+As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relatively normal with a small bump at 0.
 As a group we believe this bump occurs as 0 is the lowest value it can take and because of that limitation of the China Virus Interest we see a small bump around 0.
@@
 
-When China Virus Interest equals 0 it means that no one in the state looked up the term in Google and this is prevalent at the 14 of March where there are 5 occurrences and the 21 of March where there are 4 occurences.
+When China Virus Interest equals 0 it means that no one in the state looked up the term in Google and this is prevalent at the 14 of March where there are 5 occurrences and the 21 of March where there are 4 occurrences.
 And in states such as DC, ND, SD, and VT.
@@
 Because our density plot showed a fairly normal distribution, we decided to use a Normal-Normal model to plot our most simple model.
-As a team we decided to also include 3 variable specifications, to explain the differences in demographic variables we decided to use `percent_white` as it was one of the best variables when we used lasso for variable selection, and it made sense as higher white percentage populations tend to have lower diversity and potentially it can lead to the search of more derrogatory terms such as "China Virus".
+As a team we decided to also include 3 variable specifications, to explain the differences in demographic variables we decided to use `percent_white` as it was one of the best variables when we used lasso for variable selection, and it made sense as higher white percentage populations tend to have lower diversity and potentially it can lead to the search of more derogatory terms such as "China Virus".
 To explain the differences in political factors in the state we decided to use `StateColor`.
@@
 ```
-In this simple model, we see that the mae value is 10.5, and 55% of the datapoints are within the 50% confidence interval, and 92% are within the 95% confidence interval.
+In this simple model, we see that the Mae value is 10.5, and 55% of the data points are within the 50% confidence interval, and 92% are within the 95% confidence interval.
 To be a simple model, it does a fairly good job at capturing the trends.
@@
 
-The output from the table above shows that within our timeframe as day increases, the interest in the coronavirus also increases.
-State color=blue is the default intercept of the model and having state color=purple decreases the interept by 1.89 while in a red state the intercept decreases by 3.7 in the interest index.
-Two other variables fo interest show that percent white and the positive rate both increase interest on average yet neither variable is specifically significant in this model.
+The output from the table above shows that within our time-frame as day increases, the interest in the coronavirus also increases.
+State color=blue is the default intercept of the model and having state color=purple decreases the interpret by 1.89 while in a red state the intercept decreases by 3.7 in the interest index.
+Two other variables of interest show that percent white and the positive rate both increase interest on average yet neither variable is specifically significant in this model.
 
@@
 
-Finallly in our analysis of the model we see that the MAE of this model is 8.98 with a within-50 rate of 0.59 and within-95 ratet of 0.965 showing some relaive gains from the first model.
+Finally in our analysis of the model we see that the MAE of this model is 8.98 with a within-50 rate of 0.59 and within-95 rate of 0.965 showing some relieve gains from the first model.
 
@@
 
-**Comment:** Our data set includes not only repeated measures on our response variable $Y$ for each state, it also includes corresponding observations for our preditor variables as well.
-In order to increase the complexity of our model to include these aspects we will use the model strcuture below as a fundamental start point:
+**Comment:** Our data set includes not only repeated measures on our response variable $Y$ for each state, it also includes corresponding observations for our predictor variables as well.
+In order to increase the complexity of our model to include these aspects we will use the model structure below as a fundamental start point:
 
@@
 ```
-The output from the table above shows that within our timeframe as day increases, the interest in the China Virus term also increases.
-State color=blue is the default intercept of the model and having state color=purple decreases the interept by 1.02 while in a red state the intercept decreases by 3.6 in the interest index.
-Two other variables fo interest show that percent white and the positive rate both increase interest on average yet neither variable is specifically significant in this model.
+The output from the table above shows that within our time frame as day increases, the interest in the China Virus term also increases.
+State color=blue is the default intercept of the model and having state color=purple decreases the intercept by 1.02 while in a red state the intercept decreases by 3.6 in the interest index.
+Two other variables of interest show that percent white and the positive rate both increase interest on average yet neither variable is specifically significant in this model.
 
@@
 ```
-**Comment:** The assumption of using a Normal model is fairly reasonable besides the fact that we observe two bumps on both sides of the tails. We can assume these to be outliars.
+**Comment:** The assumption of using a Normal model is fairly reasonable besides the fact that we observe two bumps on both sides of the tails. We can assume these to be outliers.
 
@@
 ```
-**Comment:** Finallly in our analysis of the model we see that the MAE of this model is 9.01.
+**Comment:** Finally in our analysis of the model we see that the MAE of this model is 9.01.
 Our within-50 rate is 0.60 which means that 60%  of the predictions that fall within our middle 50% of our predictive model.

### 2020-05-01 Draft-Report.Rmd
a

--- 2020-05-01 Draft-Report.Rmd
@@
 
-```{r}
+```{r, include=FALSE, warning=FALSE}
 c <-  ggplot(Finaldata, aes(y=positive, x=Winner, fill=(Winner)))+
@@
       ggtitle("Positive COVID-19 Cases by State Political Party Winner & Region")
+```
+
+```{r, warning=FALSE}
 ggplotly(c)
 ```
-
-(PUT DESCRIPTION)
+This visualisation depicts the distribution of positive COVID-19 cases by region and by which political party won in the 2016 elections.
+We can see that Democrat states in the Midwest, Mountain, and West have a larger range and higher quantile metrics for positive cases overall.
+For the Northeast and South regions the mean of positive COVID-19 cases are higher but not significantly.
+This is an interesting pattern considering that poltical party affiliation appears to interact with the number of postive cases by region.
 \
@@
 After we created the model I focused on the model evaluation section for that model, and was able to get our MCMC plots to show.
+
+Quinn helped by running and organing the models for members to run.
+She also helped Sofia and Will draft the introduction summary.
+Sofia and Quinn both worked on the complex model's interpretations, code runs, and analyses.
+My main contribution was the model description and the predictions for the complex model.

### 2020-05-02 Draft-Report.Rmd
Update Draft-Report.Rmd

@@
 
-#### FIX 
 $$
-Y_{ij}|\theta_i, \mu_, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3,\sigma^2) \\
+Y_{ij}|\theta_i, \mu_, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_3X_3,\sigma_w^2) \\
 \theta|\mu, \sigma_b   \sim N(\mu,\sigma_b) \\
@@
 \beta_4 \sim N(..., ...) \\
+\sigma_w \sim Exp(...)\\
+\sigma_b \sim Exp(...)\\
 $$
@@
 ```{r}
-View(Finaldata)
 set.seed(454)
@@
 
-The output from the table above shows that within our time-frame as day increases, the interest in the coronavirus also increases.
+**Comment:**The output from the table above shows that within our time-frame as day increases, the interest in the coronavirus also increases.
 State color=blue is the default intercept of the model and having state color=purple decreases the interpret by 1.89 while in a red state the intercept decreases by 3.7 in the interest index.
 Two other variables of interest show that percent white and the positive rate both increase interest on average yet neither variable is specifically significant in this model.
-
-```{r}
-pp_check(model_2)
-```
-
-This pp-check is similar to our other models showing a following of the trend with a specific hump around 0.
-This is due to 0 receiving extra weight in our data set than other values we would expect to see.
-
-```{r}
-set.seed(454)
-pred_2 <- posterior_predict(
-  model_2,
-  newdata = Finaldata, transform = TRUE)
-
-prediction_summary(y = Finaldata$ChinaVirusInterest,
-  yrep = pred_2)
-```
-
-Finally in our analysis of the model we see that the MAE of this model is 8.98 with a within-50 rate of 0.59 and within-95 rate of 0.965 showing some relieve gains from the first model.
 
@@
 
-###Will model eval (model 2)
+### Will model eval (model 2)
+
+```{r}
+mcmc_trace(model_2, pars=c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[(Intercept) State:AK]","b[(Intercept) State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
+mcmc_dens_overlay(model_2, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[(Intercept) State:AK]","b[(Intercept) State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
+```
+**Comment:** This table shows the how the differing parameters appear across different chains.
+While not gaining necessary inference from the graphs, we do see that the chains do stay compact and close together across all of the different parameters which is a good sign.
+
+```{r}
+pp_check(model_2)
+```
+
+**Comment:**This pp-check is similar to our other models showing a following of the trend with a specific hump around 0.
+This is due to 0 receiving extra weight in our data set than other values we would expect to see.
+
+```{r}
+# Store the chains
+model_2_df <- as.array(model_2) %>%
+  melt %>%
+  pivot_wider(names_from = parameters, values_from = value)
+model_2_df
+
+# Wrangle the chains
+model_2_df <- model_2_df %>%
+  mutate(sigma_sq_w = sigma^2, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
+  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))
+
+#Correlation Plot
+ggplot(model_2_df, aes(x = correlation)) +
+  geom_density(alpha = 0.5)
+```
+
+**Comment:**The correlation table above shows that the mean correlation in these models is around 0.2, this decreasing correlation is due to adding complexity in the model through the addition of state fixed effects.
 
@@
 ## 3.3 Model Predictions
+
+### Repeated Measures Model
+
+```{r}
+set.seed(454)
+pred_2 <- posterior_predict(
+  model_2,
+  newdata = Finaldata, transform = TRUE)
+
+prediction_summary(y = Finaldata$ChinaVirusInterest,
+  yrep = pred_2)
+```
+
+**Comment:**Finally in our analysis of the model we see that the MAE of this model is 8.98 with a within-50 rate of 0.59 and within-95 rate of 0.965 showing some relieve gains from the first model.
+
+```{r}
+set.seed(454)
+
+new_data <- Finaldata %>% filter(State == "FL")
+new_pred <- posterior_predict(
+  model_2,
+  newdata = new_data)
+
+my_pred <- data.frame(y_new = new_pred[-1])
+
+ggplot(my_pred, aes(x=y_new))+geom_density()
+
+summary(my_pred)
+
+actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
+
+actual_FL_pred
+```
+**Comment:** To test our model we use Florida as a prediction state and test the outcome.
+The mean value in our test is an interest of 46.08 in searching China Virus while the real value of Florida is 47.625 for a difference slightly greater than 1.5 in interest.
 
@@
 My main contribution was the model description and the predictions for the complex model.
+
+Will built the Repeated Measures model in this report as well as doing the evaluations and predictions for the model as well. 
+In addition to doing all work for Model 2 I also assisted in the writing of the Introduction.

### 2020-05-02 Draft-Report.Rmd
fed changes

@@
 Finaldata<-read_csv("time_series_final_Data.csv")
+google<-read.csv("Google/googlefinal.csv")
 
@@
 This is an interesting pattern considering that poltical party affiliation appears to interact with the number of postive cases by region.
-\
-\
-
-# 3. Models
-
-## 3.1 Model(s)
 
@@
   geom_density()
+```
+```{r}
+Finaldata%>%
+  filter(ChinaVirusInterest ==0)%>%
+  group_by(Day)%>%
+  summarize(n = n())
 ```
@@
 
-```{r}
-Finaldata%>%
-  filter(ChinaVirusInterest ==0)%>%
-  group_by(Day)%>%
-  summarize(n = n())
-```
+\
+\
+
+# 3. Models
+
+## 3.1 Model(s)
 
@@
   mutate(Day=as.numeric(Day)-as.numeric(min(Day)))%>%
-  select(ChinaVirusInterest, Day, percent_white, StateColor, positive)
+  select(ChinaVirusInterest, Day, percent_white, StateColor, positive, State)
 
@@
 
-```{r}
+```{r results = "hide", include = FALSE}
 set.seed(454)
@@
 )
-model_1
 
 ```
-
-As we can see in our summary table, we see that the higher the percent_white we see a higher median of China Virus Interest states with higher percent_white populations tend to have higher searches for "China Virus".
-And we also see that compared to State Color Blue state Color Red tends to have -3.2% less searches.
-We also see that the positive number of cases did not change the mean value for China Virus Interest which we found interesting.
-Basically telling us that maybe COVID-related variables do not have a big effect on how much people search for these terms.
-
-```{r}
-head(data.frame(summary(model_1)),-2)
-```
-
-```{r}
-pp_check(model_1)
-```
-Overall, we can see that our simple model it tells us that the structure of our model is fairly reasonable, In other words, the assumption of using a normal model is fairly reasonable outside of the fact that the tails are a bit thicker than we would want them to be.
-
-```{r}
-set.seed(454)
-pred_1 <- posterior_predict(
-  model_1,
-  newdata = model_data, transform = TRUE)
-
-prediction_summary(y = model_data$ChinaVirusInterest,
-  yrep = pred_1)
-```
-In this simple model, we see that the Mae value is 10.5, and 55% of the data points are within the 50% confidence interval, and 92% are within the 95% confidence interval.
-To be a simple model, it does a fairly good job at capturing the trends.
-
-################ FEDDY PREDICT FOR FLORIDA TOO please. ALSO MOVE YOUR STUFF TO THE RIGHT PLACES ############
 
@@
 ### Feddy model eval (model 1)
+```{r}
+# Trace plots
+mcmc_trace(model_1,pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))
+
+# Density plots
+mcmc_dens_overlay(model_1, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))
+```
+
+As we can see in our mcmc plots,  we see that our chains are all close to each other meaning that our simulation was stable.
+
+```{r}
+model_1
+```
+
+As we can see in our summary table, we see that the higher the percent_white we see a higher median of China Virus Interest states with higher percent_white populations tend to have higher searches for "China Virus".
+And we also see that compared to State Color Blue state Color Red tends to have -3.2% less searches.
+We also see that the positive number of cases did not change the mean value for China Virus Interest which we found interesting.
+Basically telling us that maybe COVID-related variables do not have a big effect on how much people search for these terms.
+
+```{r}
+head(data.frame(summary(model_1)),-2)
+```
+
+```{r}
+pp_check(model_1)
+```
+Overall, we can see that our simple model it tells us that the structure of our model is fairly reasonable, In other words, the assumption of using a normal model is fairly reasonable outside of the fact that the tails are a bit thicker than we would want them to be.
+
+```{r}
+set.seed(454)
+pred_1 <- posterior_predict(
+  model_1,
+  newdata = model_data, transform = TRUE)
+
+prediction_summary(y = model_data$ChinaVirusInterest,
+  yrep = pred_1)
+```
+
+In this simple model, we see that the Mae value is 10.5, and 55% of the data points are within the 50% confidence interval, and 92% are within the 95% confidence interval.
+To be a simple model, it does a fairly good job at capturing the trends.
+
+```{r}
+set.seed(454)
+
+new_data <- model_data %>% filter(State == "FL")
+new_pred <- posterior_predict(
+  model_1,
+  newdata = new_data)
+
+my_pred <- data.frame(y_new = new_pred[-1])
+
+ggplot(my_pred, aes(x=y_new))+geom_density()
+
+summary(my_pred)
+
+actual_FL_pred<-model_data %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
+
+actual_FL_pred
+```
+
+Our actual value in our simple model lies within the mean value of our prediction and it is close to the mean and the third quarter.
 
@@
 ## 3.3 Model Predictions
+
+### Normal Regression Model
+
+```{r}
+set.seed(454)
+
+new_data <- Finaldata %>% filter(State == "FL")
+new_pred <- posterior_predict(
+  model_1,
+  newdata = new_data)
+
+my_pred <- data.frame(y_new = new_pred[-1])
+
+ggplot(my_pred, aes(x=y_new))+geom_density()
+
+summary(my_pred)
+
+actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
+
+actual_FL_pred
+```
 

### 2020-05-03 Draft-Report.Rmd
Update Draft-Report.Rmd

@@
 ---
+
+\
+\
 
@@
 
-##Repeated Measures + Normal Regression (WILL) (1|State)**
+## Repeated Measures + Normal Regression (WILL) (1|State)**
 
@@
 
-###Complex Model
+### Complex Model
 
@@
 
-###Complex Model 
+### Complex Model 
 ```{r}

### 2020-05-03 Draft-Report.Rmd
changes

--- 2020-05-02 Draft-Report.Rmd
@@
 
-For our first model we decided to use a simple Normal regression model.
+For our first model we decided to use a simple Repeated Measures regression model
+
+$$\begin{aligned}
+Y_{ij}|\theta, \mu, \sigma_w, \sigma_b \sim N(\theta_i,\theta_w^2)\\
+\theta|\mu,\sigma_b \overset{ind}{\sim} N(\mu, \sigma_b^2)\\
+\sigma_b,\sigma_w \sim Exp(...)
+\end{aligned}$$
+
+```{r}
+set.seed(454)
+model_0 <- stan_glmer(
+  ChinaVirusInterest ~ (1 | State),
+  data = model_data, family = gaussian,
+)
+```
+
+For this model we decided to use a simple Normal regression model.
 
@@
 $$\begin{aligned}
-Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3,\sigma^2)\\
+i = state, j = \text{days since "2020-03-14"} \\
+Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3,\beta_4 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4,\sigma^2)\\
 \beta_0,\beta_1, \beta_2,\beta_3 \sim N(...,...)\\
-\sigma,\sigma \sim Exp(...)\\
+\sigma \sim Exp(...)\\
 \end{aligned}$$
@@
 *White, StateColor, Day, Positive Cases, State
-
-$$
-Y_{ij}|\theta_i, \mu_, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_3X_3,\sigma_w^2) \\
-\theta|\mu, \sigma_b   \sim N(\mu,\sigma_b) \\
-\mu \sim N(..., ...) \\ 
-\beta_2 \sim N(..., ...) \\
-\beta_3 \sim N(..., ...) \\
-\beta_4 \sim N(..., ...) \\
-\sigma_w \sim Exp(...)\\
-\sigma_b \sim Exp(...)\\
-$$
+$$\begin{aligned}
+i = state, j = \text{days since "2020-03-14"}
+Y_{ij}|\theta,\mu,\beta_0, \beta_1, \beta_2,\beta_3,\beta_4,\sigma_w,\sigma_b \sim N(\theta_i +\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4, \sigma_w^2)\\
+\theta_i|\mu, \sigma_b \overset{ind}{\sim}N (\mu, \sigma_b^2)\\
+\beta_0,\beta_1, \beta_2,\beta_3 \sim N(...,...)\\
+\sigma_w,\sigma_b \sim Exp(...)\\
+\end{aligned}$$
 
@@
 
-Variables of Interest: `White`, `StateColor`, `Day`, `Total Test Results`, `State`
+Variables of Interest: `percent_white`, `StateColor`, `Day`, `Total Test Results`, `State`
 
@@
 \begin{split}
-Y_{ij} | b_0, b_1, \beta_0, \beta_1, \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N(b_{0i} + b_{1i} X_{ij}, \; \sigma_w^2) \\
+Y = \text{ChinaVirusInterest},i = state, j = \text{days since "2020-03-14"}, X_{ij} = \text{Days}\\
+X_2 = \text{percent_white},,X_3 =\text{StateColor},  X_4 =\text{Total Test Results} \\
+Y_{ij} | b_0, b_1, \beta_0, \beta_1, \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N( b_{0i} + b_{1i} X_{ij}+ \beta_2X_2 + \beta_3X_3 +\beta_4X_4, \; \sigma_w^2) \\
 b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
 b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
-\beta_0 & \sim N(..., ...) \\
-\beta_1 & \sim N(..., ...) \\
+\beta_0,\beta_1,\beta_2,\beta_3,\beta_4 & \sim N(..., ...) \\
 \sigma_w & \sim Exp(...) \\

### 2020-05-03 Final-Draft.Rmd
adding final draft

--- 2020-05-03 Draft-Report.Rmd
@@
 ---
-title: "Checkpoint 4"
-author: "Quinn Rafferty, Sofia Pozsonyiova, Will Madairy, Federico Chung"
-date: "4/24/2020"
+title: ""
+author: "Federico Chung, Will Madairy, Sofia Pozsonyiova, Quinn Rafferty"
+date: '`r format(Sys.Date(), "%B %d, %Y")`'
 output:
@@
     toc_float: true
+bibliography: Library.bib
 ---
-
-\
-\
-
-#Libraries
 
@@
 library(plotly)
-require(janitor)
-require(reshape2)
-require(tidyr)
-require(rstan)
-require(rstanarm)
-require(bayesplot)
+library(janitor)
+library(reshape2)
+library(tidyr)
+library(rstan)
+library(rstanarm)
+library(bayesplot)
 ```
@@
 
-# 1. Introduction
+# Introduction
 
-On March 17, 2020 President Trump referred to the Coronavirus as the "China Virus." Shortly after, the number of anti-Chinese incidents started to increase across the United States.
-One aspect of public health that is often thrown to the wayside is how influential public officials and leaders are in disseminating public health information.
-Moreover, not only can their words change the public's views on a health matter but it can also shift a nation's perspective on someone's identity.
-In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identities and states.
-Thus,our project aims to explore the relationship and variability of interest in the term "China Virus" across states through  political, demographic and COVID-19 characteristics.
-This was done using _____.
-(Conclusion)
+Make sure to discuss the time period of interest 
+## Project Motivations
+
+## Project Goals
 
@@
 
-# 2 The Data Set
+# Data
 
-```{r results = "hide", echo=FALSE, warning=FALSE}
+## Data Descriptions
 
-Finaldata<-read_csv("time_series_final_Data.csv")
-google<-read.csv("Google/googlefinal.csv")
+## Variables of interest
 
-Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
-day_initial<- as.Date("2020-03-14")
-day_final<- as.Date("2020-03-21")
-Finaldata<- Finaldata%>%
-  filter(Day>=day_initial)%>%
-  filter(Day<=day_final)
-```
-
-## 2.1 Data Description
-
-`Demographic:`
-Our dataset, `Demographic`, was created by merging three other datasets which all contained different demographic and election information.
-We obtained the main portion of our demographic data from the US Census Bureau’s American Community Survey (ACS) which is an ongoing survey administered by the U.S.
-Census Bureau.
-It  gathers information on income, employment, housing characteristics, etc, annually for all the 50 U.S.
-States on the county and state level.
-To access the county-level dataset we used the R package called Choroplethr which provides API connections to data sources like the ACS.
-The ACS County-Level dataset was then merged with a county-level election outcome dataset that was created by Tony McGoven.
-Tony’s dataset contained presidential election results for 2008,2012, and 2016 but we chose to focus solely on the most recent election,2016.
-That said, the 2016 election results at the county-level were scraped from results published by Townhall.com.
-However, the State of Alaska reports results at the precinct or state level so there was no county-level data available.
-Therefore, another dataset had to be created that contained the election results for Alaska and this was done using the official election results provided by the Alaska Division of Elections and was later merged in.
-The final dataset that was used came from Alicia Johnson and it contained information on a state’s political leaning.
-Meaning it categorizes each county as belonging to a blue/red/purple state based on the state categorizations at 279towin.
-
-`COVID-19 Cases:`
-The COVID-19 data is provided by The COVID Tracking Project(CTP).
-All of the  data points come from state/district/territory public health authorities—or, occasionally, from trusted news reporting, official press conferences, or (very occasionally) tweets or Facebook updates from state public health authorities or governors.
-These numbers are updated daily at 4PM EST.
-The biggest weakness of this dataset is that there is no standardized methods for states to follow for data collection/report.
-For example, some states, like Oregon, provide the **full** set of numbers but others provide some or none of these numbers on an ongoing basis.
-Some crucial states in this outbreak, notably California, Washington, and New York, have not been regularly reporting their total number of people tested.
-The CTP aims to remedy this uncertainty in states by utilizing other reporting/measuring tools such as: "Directly asking state officials, watching news conferences, gleaning information from trusted news sources, and whatever else it takes to present reliable numbers."
-
-`Google Search Interest:`
-This data set includes two search interest indexes over time, measuring how people in each of the state’s interest in searching either “Kung Flu” or “China Virus” based on the time frame selected in the search.
-This data is downloaded directly from Google Trends which uses the same technique to track the interest of all searches on the platform.
-The main downside to this data set is the method of the indexing which makes the comparison from state to state less meaningful since each state is guaranteed to have a 100-level interest on their peak day, and the actual unknown search values can vary greatly across different states.
-
-## 2.2 Data Information
-
-```{r warning=FALSE}
-dim(Finaldata)
-
-names(Finaldata)
-
-head(Finaldata)
-
-summary(Finaldata)
-```
-
-## 2.3 Variables of Interest
-
-+------------------------+---------------------------------------------------+
-| Variables:             | Description:                                      |
-+========================+===================================================+
-| `polyname`             | State Name                                        |
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-| `StateColor`           | Political Leaning                                 |
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`percent_hispanic`      | Percent of the Population that is Hispanic        |
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-| `percent_white`        | Percent of the Population that is White           |
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-| `percent_asian`        | Percent of the Population that is Asian           |  
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-| `percent_black`        | Percent of Population that is Black               |  
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`total_population`      | Total State Population                            | 
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`per_capita_income`     | Income per Capita                                 |
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`percent_democrat2016`  | Percent of votes won by Democrat (Clinton)        |  
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`percent_republican2016`| Percent of votes won by Republican (Trump)        | 
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-| `Winner`               | Indicator for whether a Republican or Democrat Won| 
-|                        |                                                   |  
-+------------------------+---------------------------------------------------+
-|`total_2016`            | Total Number of Votes                             | 
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`Positive`              | Number of reported positive COVID-19 cases        | 
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`Negative`              | Number of reported negative COVID-19 cases        | 
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`date`                  | Date of report                                    | 
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`death`                 | Total Number of reported deaths due to COVID-19   | 
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`hospitalized`          | Total Number of individuals hospitalized due        |
-|                        | to COVID-19                                       |
-+------------------------+---------------------------------------------------+
-|`totalTestResults`      | Total Number test results (Positive +Negative)    | 
-|                        |                                                   | 
-+------------------------+---------------------------------------------------+
-|`FIPS`                  | A five-digit Federal Information Processing       |
-|                        | Standards code which uniquely identified counties |
-|                        | and county                                        | 
-+------------------------+---------------------------------------------------+
-|`KungFluInterest`       | Interest index from Google searches by state.     |
-|                        | Peak search day=100, all other days in set are    |
-|                        | based searches on relative to this peak day.      | 
-+------------------------+---------------------------------------------------+
-|`ChinaVirusInterest`    | Interest index from Google searches by state.     |
-|                        | Peak search day=100, all other days in set are    |
-|                        | based searches on relative to this peak day.      | 
-+------------------------+---------------------------------------------------+
-|`Region`                | States divided into five different regions:       |
-|                        | West, South, Mountain, Northeast, Midwest         |
-+------------------------+---------------------------------------------------+
-|`StayAtHome_date`       | The date states have enforced quarantine          |
-+------------------------+---------------------------------------------------+
-|`Quarantine_Yes`        | An 0,1 indicator of whether states have enforced  |
-|                        | quarantine                                        |
-+------------------------+---------------------------------------------------+
-
-##2.4 Visualizations
-
-###Demographic 
-```{r}
-#Demographic: Identification 
-Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
-plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
-  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
-  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") + 
-  theme(
-plot.title = element_text(color="Black", size=14, face="bold")
-)
-
-```
-
-Our first visualization is looking at the percent of residents that identify as white within the United States.
-As you can see, there is a higher percent of white identifying residents in the Midwest and northeast states.
-From this visualization we can also see that places like Texas, California, and New Mexico have much lower white identifying residents which could provide important information for us in our actual analysis.
-
-```{r}
-plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
-  scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
-  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") +
-  theme(
-plot.title = element_text(color="Black", size=14, face="bold")
-) 
-```
-
-The above visualization is looking at the percent of residents that identify as Asian within the United States.
-As you can see, there is a higher percent of residents that identify as Asian in places like California and Washington, but the most being in Hawaii.
-From this visualization we can also see that that Midwest and the South tend to have a small percentage of residents identifying as Asian.
-We are especially interested in the `percent_asian` variable as it plays a major role in our analysis.
-
-###Google TS
-```{r}
-Trump<- as.Date("03/16/2020", format = "%m/%d/%Y")
-day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
-day2<-as.Date("03/24/2020",format = "%m/%d/%Y")
-
-google_ts<-google%>%
-  mutate(Day = as.Date(as.character(Day)))
-
-a<-google_ts %>% 
-  #filter(Day<=day2)%>%
-  #filter(Day>=day1)%>%
-  group_by(Region, Day) %>% 
-  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
-  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
-  geom_point()
-
-ggplotly(a)
-```
-
-This plot shows the relationship of “China Virus” search interest over grouped by region.
-This plots shows that there are certainly key events that trigger an uptick in searches overall.
-In this plot it is not clear which region may search China Virus more or less often, but it does show a that the regions move together in search interest, which would imply federal level events like a Donald Trump tweet to trigger these interest spikes.
-
-```{r}
-b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
-  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State")
-
-ggplotly(b)
-```
-
-We can see that the variability in Google interest in the term China Virus is has quite a large range between states.
-There are very few states that have high densities among the upper echelons of the interest scale but there are some interesting peaks of densities among the lower values.
-For example, we can see that Alaska, Wyoming and Iowa have unusual peaks around the 25-50 range.
-It is is also interesting interesting to note that there isn't an *obvious* mean or median value of China Virus interest among the states.
-
-###COVID-19
-
-```{r, include=FALSE, warning=FALSE}
-c <-  ggplot(Finaldata, aes(y=positive, x=Winner, fill=(Winner)))+
-      geom_boxplot() +
-      facet_wrap(~Region)+
-      theme(legend.position = "none") +
-      scale_fill_manual(values = c("Democrat"="blue3", "Republican"= "red3"))+
-      lims(y= c(0,1000))+
-      ggtitle("Positive COVID-19 Cases by State Political Party Winner & Region")
-```
-
-```{r, warning=FALSE}
-ggplotly(c)
-```
-This visualisation depicts the distribution of positive COVID-19 cases by region and by which political party won in the 2016 elections.
-We can see that Democrat states in the Midwest, Mountain, and West have a larger range and higher quantile metrics for positive cases overall.
-For the Northeast and South regions the mean of positive COVID-19 cases are higher but not significantly.
-This is an interesting pattern considering that poltical party affiliation appears to interact with the number of postive cases by region.
-
-```{r}
-Finaldata%>%
-  ggplot(aes(x = ChinaVirusInterest))+
-  geom_density()
-```
-```{r}
-Finaldata%>%
-  filter(ChinaVirusInterest ==0)%>%
-  group_by(Day)%>%
-  summarize(n = n())
-```
-During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns across states.
-
-As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relatively normal with a small bump at 0.
-As a group we believe this bump occurs as 0 is the lowest value it can take and because of that limitation of the China Virus Interest we see a small bump around 0.
-One could argue against a normal distribution as it kinda looks a bit right skewed.
-But our team believes that a normal distribution is the best at describing the density.
-
-When China Virus Interest equals 0 it means that no one in the state looked up the term in Google and this is prevalent at the 14 of March where there are 5 occurrences and the 21 of March where there are 4 occurrences.
-And in states such as DC, ND, SD, and VT.
+## Visualizations (Quinn)
 
@@
 
-# 3. Models
+# Methods & Models (Feddy and Will)
 
-## 3.1 Model(s)
+## Markov Chain Algorithm
 
-Because our density plot showed a fairly normal distribution, we decided to use a Normal-Normal model to plot our most simple model.
-As a team we decided to also include 3 variable specifications, to explain the differences in demographic variables we decided to use `percent_white` as it was one of the best variables when we used lasso for variable selection, and it made sense as higher white percentage populations tend to have lower diversity and potentially it can lead to the search of more derogatory terms such as "China Virus".
-To explain the differences in political factors in the state we decided to use `StateColor`.
-The variable was inspired by a study conducted by Pew Research Center that concluded that Liberal Democrats are more likely to use social media and look up information in the internet.
-By dividing states by their color we could use the color as a proxy to understand which ones had more democrats in their state.
-And finally, we believed that states more affected by COVID-19 would be more inclined to search terms like China Virus, as the virus has had a bigger impact on them which is why we decided to use `positive` (# of positive cases).
+## Models of Interest
 
-```{r}
-model_data<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day)-as.numeric(min(Day)))%>%
-  select(ChinaVirusInterest, Day, percent_white, StateColor, positive, State)
-
-model_data<- na.omit(model_data)
-```
-
-For our first model we decided to use a simple Normal regression model.
-
-In this model i= the nth observation
-
-$$\begin{aligned}
-Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3,\sigma^2)\\
-\beta_0,\beta_1, \beta_2,\beta_3 \sim N(...,...)\\
-\sigma,\sigma \sim Exp(...)\\
-\end{aligned}$$
-
-```{r results = "hide", include = FALSE}
-set.seed(454)
-model_1 <- stan_glm(
-  ChinaVirusInterest ~ Day + percent_white+StateColor+positive,
-  data = model_data, family = gaussian,
-  chains = 4, iter = 10000, refresh = 0
-)
-
-```
-
-## Repeated Measures + Normal Regression (WILL) (1|State)**
-
-*White, StateColor, Day, Positive Cases, State
-
-$$
-Y_{ij}|\theta_i, \mu_, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_3X_3,\sigma_w^2) \\
-\theta|\mu, \sigma_b   \sim N(\mu,\sigma_b) \\
-\mu \sim N(..., ...) \\ 
-\beta_2 \sim N(..., ...) \\
-\beta_3 \sim N(..., ...) \\
-\beta_4 \sim N(..., ...) \\
-\sigma_w \sim Exp(...)\\
-\sigma_b \sim Exp(...)\\
-$$
-
-In this model using repeated measures the outcome of $Y_{ij}$ is the interest in China Virus on a given day within a state.
-$\mu$ represents the mean value of the interest on Day 0 of the study and how much we would expect.
-The $\theta_{i}$ represents the change from the intercept that each of the states experiences.
-$\beta_2$ represents the variable for the percent of the population that is white and $\beta_3$ represents the variable that corresponds with state color.
-Finally, $\beta_4$ represents the proportion of the population that tests positive for the coronavirus.
-
-```{r results = "hide", include = FALSE}
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
-
-model_2 <- stan_glmer(
-  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (1 | State), 
-  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
-)
-```
-
-```{r}
-head(data.frame(summary(model_2)),-2)
-```
-
-**Comment:**The output from the table above shows that within our time-frame as day increases, the interest in the coronavirus also increases.
-State color=blue is the default intercept of the model and having state color=purple decreases the interpret by 1.89 while in a red state the intercept decreases by 3.7 in the interest index.
-Two other variables of interest show that percent white and the positive rate both increase interest on average yet neither variable is specifically significant in this model.
-
-### Complex Model
-
-Variables of Interest: `White`, `StateColor`, `Day`, `Total Test Results`, `State`
-
-**Comment:** Our data set includes not only repeated measures on our response variable $Y$ for each state, it also includes corresponding observations for our predictor variables as well.
-In order to increase the complexity of our model to include these aspects we will use the model structure below as a fundamental start point:
-
-$$
-\begin{split}
-Y_{ij} | b_0, b_1, \beta_0, \beta_1, \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N(b_{0i} + b_{1i} X_{ij}, \; \sigma_w^2) \\
-b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
-b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
-\beta_0 & \sim N(..., ...) \\
-\beta_1 & \sim N(..., ...) \\
-\sigma_w & \sim Exp(...) \\
-\sigma_{0b} & \sim Exp(...) \\
-\sigma_{1b} & \sim Exp(...) \\
-\end{split}
-$$
-
-**Comment:** With this structure our model will be able to account for the differing intercepts based on the day and also the differing slopes we expect to see by state.
-
-```{r results = "hide", include = FALSE}
-
-set.seed(454)
-Finaldata<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day))
-
-complexmod <- stan_glmer(
-  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (Day | State), 
-  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
-)
-```
-
-```{r}
-head(data.frame(summary(complexmod)),-2)
-```
-The output from the table above shows that within our time frame as day increases, the interest in the China Virus term also increases.
-State color=blue is the default intercept of the model and having state color=purple decreases the intercept by 1.02 while in a red state the intercept decreases by 3.6 in the interest index.
-Two other variables of interest show that percent white and the positive rate both increase interest on average yet neither variable is specifically significant in this model.
-
-## 3.2 Model Evaluation
-
-### Feddy model eval (model 1)
-```{r}
-# Trace plots
-mcmc_trace(model_1,pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))
-
-# Density plots
-mcmc_dens_overlay(model_1, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))
-```
-
-As we can see in our mcmc plots,  we see that our chains are all close to each other meaning that our simulation was stable.
-
-```{r}
-model_1
-```
-
-As we can see in our summary table, we see that the higher the percent_white we see a higher median of China Virus Interest states with higher percent_white populations tend to have higher searches for "China Virus".
-And we also see that compared to State Color Blue state Color Red tends to have -3.2% less searches.
-We also see that the positive number of cases did not change the mean value for China Virus Interest which we found interesting.
-Basically telling us that maybe COVID-related variables do not have a big effect on how much people search for these terms.
-
-```{r}
-head(data.frame(summary(model_1)),-2)
-```
-
-```{r}
-pp_check(model_1)
-```
-Overall, we can see that our simple model it tells us that the structure of our model is fairly reasonable, In other words, the assumption of using a normal model is fairly reasonable outside of the fact that the tails are a bit thicker than we would want them to be.
-
-```{r}
-set.seed(454)
-pred_1 <- posterior_predict(
-  model_1,
-  newdata = model_data, transform = TRUE)
-
-prediction_summary(y = model_data$ChinaVirusInterest,
-  yrep = pred_1)
-```
-
-In this simple model, we see that the Mae value is 10.5, and 55% of the data points are within the 50% confidence interval, and 92% are within the 95% confidence interval.
-To be a simple model, it does a fairly good job at capturing the trends.
-
-```{r}
-set.seed(454)
-
-new_data <- model_data %>% filter(State == "FL")
-new_pred <- posterior_predict(
-  model_1,
-  newdata = new_data)
-
-my_pred <- data.frame(y_new = new_pred[-1])
-
-ggplot(my_pred, aes(x=y_new))+geom_density()
-
-summary(my_pred)
-
-actual_FL_pred<-model_data %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
-
-actual_FL_pred
-```
-
-Our actual value in our simple model lies within the mean value of our prediction and it is close to the mean and the third quarter.
-
-### Will model eval (model 2)
-
-```{r}
-mcmc_trace(model_2, pars=c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[(Intercept) State:AK]","b[(Intercept) State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
-mcmc_dens_overlay(model_2, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[(Intercept) State:AK]","b[(Intercept) State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
-```
-**Comment:** This table shows the how the differing parameters appear across different chains.
-While not gaining necessary inference from the graphs, we do see that the chains do stay compact and close together across all of the different parameters which is a good sign.
-
-```{r}
-pp_check(model_2)
-```
-
-**Comment:**This pp-check is similar to our other models showing a following of the trend with a specific hump around 0.
-This is due to 0 receiving extra weight in our data set than other values we would expect to see.
-
-```{r}
-# Store the chains
-model_2_df <- as.array(model_2) %>%
-  melt %>%
-  pivot_wider(names_from = parameters, values_from = value)
-model_2_df
-
-# Wrangle the chains
-model_2_df <- model_2_df %>%
-  mutate(sigma_sq_w = sigma^2, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
-  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))
-
-#Correlation Plot
-ggplot(model_2_df, aes(x = correlation)) +
-  geom_density(alpha = 0.5)
-```
-
-**Comment:**The correlation table above shows that the mean correlation in these models is around 0.2, this decreasing correlation is due to adding complexity in the model through the addition of state fixed effects.
-
-### Complex Model
-
-```{r}
-# Trace plots
-mcmc_trace(complexmod,pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[Day State:AK]","b[Day State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
-
-# Density plots
-mcmc_dens_overlay(complexmod, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[Day State:AK]","b[Day State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
-```
-
-**Comment:** For our MCMCs graphs we chose to just look at our predictors, intercept, and sigma value.
-We sadly cannot visualize all of our random slopes given that we would have over 50.
-However, we did visualize at least a couple of the random slopes as seen above.
-From the MCMC Dens and Trace we see that our chains are all close to each other meaning that our simulation was stable, which is great!
-
-```{r}
-pp_check(complexmod, nreps = 50)
-```
-**Comment:** The assumption of using a Normal model is fairly reasonable besides the fact that we observe two bumps on both sides of the tails. We can assume these to be outliers.
-
-```{r}
-# Store the chains
-model_complex_df <- as.array(complexmod) %>%
-  melt %>%
-  pivot_wider(names_from = parameters, values_from = value)
-model_complex_df
-
-# Wrangle the chains
-model_complex_df <- model_complex_df %>%
-  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
-  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))
-
-#Correlation Plot
-ggplot(model_complex_df, aes(x = correlation)) +
-  geom_density(alpha = 0.5)
-```
-
-**Comment:** Unfortunately, when we plot the correlation within our dataset we see that it comes out as empty.
-This can be attributed to the complexity of our model.
-What we found through our initial visualization exploration is that when we add additional parameters the correlation tends to decrease.
-This makes sense as a lot of our parameters are specific to each state.
-
-## 3.3 Model Predictions
-
-### Normal Regression Model
-
-```{r}
-set.seed(454)
-
-new_data <- Finaldata %>% filter(State == "FL")
-new_pred <- posterior_predict(
-  model_1,
-  newdata = new_data)
-
-my_pred <- data.frame(y_new = new_pred[-1])
-
-ggplot(my_pred, aes(x=y_new))+geom_density()
-
-summary(my_pred)
-
-actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
-
-actual_FL_pred
-```
-
-### Repeated Measures Model
-
-```{r}
-set.seed(454)
-pred_2 <- posterior_predict(
-  model_2,
-  newdata = Finaldata, transform = TRUE)
-
-prediction_summary(y = Finaldata$ChinaVirusInterest,
-  yrep = pred_2)
-```
-
-**Comment:**Finally in our analysis of the model we see that the MAE of this model is 8.98 with a within-50 rate of 0.59 and within-95 rate of 0.965 showing some relieve gains from the first model.
-
-```{r}
-set.seed(454)
-
-new_data <- Finaldata %>% filter(State == "FL")
-new_pred <- posterior_predict(
-  model_2,
-  newdata = new_data)
-
-my_pred <- data.frame(y_new = new_pred[-1])
-
-ggplot(my_pred, aes(x=y_new))+geom_density()
-
-summary(my_pred)
-
-actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
-
-actual_FL_pred
-```
-**Comment:** To test our model we use Florida as a prediction state and test the outcome.
-The mean value in our test is an interest of 46.08 in searching China Virus while the real value of Florida is 47.625 for a difference slightly greater than 1.5 in interest.
-
-### Complex Model 
-```{r}
-set.seed(454)
-pred_complex <- posterior_predict(
-  complexmod,
-  newdata = Finaldata, transform = TRUE)
-
-prediction_summary(y = Finaldata$ChinaVirusInterest,
-  yrep = pred_complex)
-```
-**Comment:** Finally in our analysis of the model we see that the MAE of this model is 9.01.
-Our within-50 rate is 0.60 which means that 60%  of the predictions that fall within our middle 50% of our predictive model.
-Our within our 95 rate is .97 which means that 97% of our predictions fall within the middle 95% of our predictive model.
-
-```{r}
-set.seed(454)
-
-new_data <- Finaldata %>% filter(State == "FL")
-new_pred <- posterior_predict(
-  complexmod,
-  newdata = new_data)
-
-my_pred <- data.frame(y_new = new_pred[-1])
-
-ggplot(my_pred, aes(x=y_new))+geom_density()
-
-summary(my_pred)
-
-actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
-
-actual_FL_pred
-```
-**Comment:**To test the accuracy of the complex model we decided to test our prediction on one case too.
-We chose Florida as our test state and as you can see from the summaries above our predictions are relatively close.
-The actual mean of interest in the term China Virus in Florida is 47.625 and our model predicted 46.10, this is only a 1.5 difference!
+## Model Descriptions
 
@@
 
-# 4. Results
+# Model Evaluation
 
-# Contributions
+## Model 1 Evaluation( Repeated measures)
 
-Federico did the "Normal Regression Model", and evaluated the model.
-Provided some visualization help by allowing for mcmc_dens plots to be seen without being clustered.
-And I have also evaluated the density plot and why a normal distribution is a good idea.
+## Model 2 Evaluation (Normal Regression)
 
-Sofia created the draft report document and organized it so that it would be easier to follow.
-Along with creating and organizing the document, I helped Quinn and Will write the Introduction.
-In addition, Quinn and I worked on making the complex model.
-After we created the model I focused on the model evaluation section for that model, and was able to get our MCMC plots to show.
+## Model 3 Evaluation(Repeated Reg + Normal)
 
-Quinn helped by running and organing the models for members to run.
-She also helped Sofia and Will draft the introduction summary.
-Sofia and Quinn both worked on the complex model's interpretations, code runs, and analyses.
-My main contribution was the model description and the predictions for the complex model.
+## Model 4 Evaluation (Longitudinal)
 
-Will built the Repeated Measures model in this report as well as doing the evaluations and predictions for the model as well. 
-In addition to doing all work for Model 2 I also assisted in the writing of the Introduction.
+\
+\
+
+# Results (Will)
+
+## Posterior Predctions All States
+
+### Table
+
+## Posterior Prediction One State
+
+## Final Model
+
+\
+\
+
+# Conclusion
+
+## Limitations
+
+## Future Work
+
+\
+\
+
+# Acknowledgments and References

### 2020-05-04 Final-Draft.Rmd
changing stuff

@@
 ---
-title: ""
+title: "Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics "
 author: "Federico Chung, Will Madairy, Sofia Pozsonyiova, Quinn Rafferty"
-date: '`r format(Sys.Date(), "%B %d, %Y")`'
+date: 'May 8,2020'
 output:
@@
     toc_float: true
-bibliography: Library.bib
 ---
 
-```{r, warning=FALSE, include=FALSE}
+```{r, warning=FALSE, include=FALSE, message=FALSE}
 library(dplyr)
@@
 
-\
+# 1. Introduction
+
+On March 17, 2020 President Trump referred to the Coronavirus as the "China Virus." Shortly after, the number of anti-Chinese incidents started to increase across the United States.
+One aspect of public health that is often thrown to the wayside is how influential public officials and leaders are in disseminating public health information.
+Moreover, not only can their words change the public's views on a health matter but it can also shift a nation's perspective on someone's identity.
+_[ADD SOME BACKGROUND LITERATURE THAT BACKS THIS CLAIM UP]_ In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identities and states.
+_[ADD BACKGROUND LITERATURE + IDENTIFY SUBJECTS OF INTEREST]_.
+There are fewer studies devoted to analyzing these aspects of the pandemic.
+
+Thus,our project aims to explore the relationship and variability of interest in the term "China Virus" across states through  political, demographic and COVID-19 characteristics.
+We ask the question, _[INSERT OUR RESERACH QUESTION]_ ?
+In order to answer this question, we look to gain a better understanding of _[INSERT NAME OF BAYESIAN METHODOLOGY]_.
+Ultimately, we hope our research inspires others to explore and better understand the impact langauge and words have on the public during times of crisis.
+
 \
 
-# Introduction
+# 2. Data
 
-Make sure to discuss the time period of interest 
-## Project Motivations
+## 2.1 Data Descriptions
 
-## Project Goals
+## 2.2 Variables of interest
+
+## 2.3 Visualizations (Quinn)
 
@@
 
-# Data
+# 3. Methods & Models (Feddy and Will)
 
-## Data Descriptions
+## 3.1 Markov Chain Algorithm
 
-## Variables of interest
+## 3.2 Models of Interest
 
-## Visualizations (Quinn)
+## 3.3 Model Descriptions
 
@@
 
-# Methods & Models (Feddy and Will)
+# 4. Model Evaluation
 
-## Markov Chain Algorithm
+## 4.1 Model 1 Evaluation( Repeated measures)
 
-## Models of Interest
+## 4.2 Model 2 Evaluation (Normal Regression)
 
-## Model Descriptions
+## 4.3 Model 3 Evaluation(Repeated Reg + Normal)
+
+## 4.4 Model 4 Evaluation (Longitudinal)
 
@@
 
-# Model Evaluation
+# 5. Results (Will)
 
-## Model 1 Evaluation( Repeated measures)
+## 5.1 Posterior Predctions All States
 
-## Model 2 Evaluation (Normal Regression)
+### 5.1.a Table
 
-## Model 3 Evaluation(Repeated Reg + Normal)
+## 5.2 Posterior Prediction One State
 
-## Model 4 Evaluation (Longitudinal)
+## 5.3 Final Model
 
@@
 
-# Results (Will)
+# 6.Conclusion
 
-## Posterior Predctions All States
+## 6.1 Limitations
 
-### Table
-
-## Posterior Prediction One State
-
-## Final Model
+## 6.2 Future Work
 
@@
 
-# Conclusion
-
-## Limitations
-
-## Future Work
-
-\
-\
-
-# Acknowledgments and References
+# 7. Acknowledgments and References

### 2020-05-04 Final-Draft.Rmd
Adding visualizations

@@
 library(bayesplot)
+library(sf)
+library(remotes)
 ```
@@
 # 2. Data
+```{r results = "hide", echo=FALSE, warning=FALSE, message = FALSE}
+
+Finaldata<-read_csv("time_series_final_Data.csv")
+google<-read.csv("Google/googlefinal.csv")
+
+Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
+day_initial<- as.Date("2020-03-14")
+day_final<- as.Date("2020-03-21")
+Finaldata<- Finaldata%>%
+  filter(Day>=day_initial)%>%
+  filter(Day<=day_final)
+```
 
@@
 
-## 2.3 Visualizations (Quinn)
+## 2.3 Visualizations _NEED TO WEAVE A COHEASIVE MESSAGE BETWEEN THESE VISUALIZATIONS TO TELL A STORY _
+
+### 2.3a Demographic 
+```{r, warning=FALSE, message= FALSE, echo=FALSE}
+#Demographic: Identification 
+Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
+
+p1<- plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
+  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
+  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  scale_fill_viridis_c(option = "plasma") + theme(plot.title = element_text(size=11))+ labs(fill = "% White")
+
+p2<- plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
+  scale_fill_continuous(name = "Percent Asian", label = scales::comma) + 
+  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as Asian") +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  scale_fill_viridis_c(option = "plasma") + theme(plot.title = element_text(size=11))+ labs(fill = "% Asian")
+
+grid.arrange(p1,p2)
+
+```
+Our first visualization is looking at the percent of residents that identify as white within the United States compared to those whom identify as asian.
+As you can see, there is a higher percent of white identifying residents overall but most specifically in the Midwest and northeast states.
+In regards to Asian-Americans, there is practically less than .1% per state with the exception of California and New York.
+From this visualization we can also see that places like Texas, California, and New Mexico have much lower white identifying residents which could provide important information for us in our actual analysis.
+
+### 2.3b Google China Virus
+
+```{r, warning=FALSE, message= FALSE, echo=FALSE}
+e <- Finaldata%>%
+  ggplot(aes(x = ChinaVirusInterest))+
+  geom_density()
+
+ggplotly(e)
+```
+During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns across states.
+
+As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relatively normal with a small bump at 0.
+As a group we believe this bump occurs as 0 is the lowest value it can take and because of that limitation of the China Virus Interest we see a small bump around 0.
+One could argue against a normal distribution as it kinda looks a bit right skewed.
+But our team believes that a normal distribution is the best at describing the density.
+
+When China Virus Interest equals 0 it means that no one in the state looked up the term in Google and this is prevalent at the 14 of March where there are 5 occurrences and the 21 of March where there are 4 occurrences.
+And in states such as DC, ND, SD, and VT.
+
+```{r, warning=FALSE, message= FALSE, echo=FALSE}
+Trump<- as.Date("03/16/2020", format = "%m/%d/%Y")
+day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
+day2<-as.Date("03/24/2020",format = "%m/%d/%Y")
+
+google_ts<-google%>%
+  mutate(Day = as.Date(as.character(Day)))
+
+a<-google_ts %>% 
+  #filter(Day<=day2)%>%
+  #filter(Day>=day1)%>%
+  group_by(Region, Day) %>% 
+  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
+  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
+  geom_point()
+
+ggplotly(a)
+```
+This plot shows the relationship of “China Virus” search interest over grouped by region.
+This plots shows that there are certainly key events that trigger an uptick in searches overall.
+In this plot it is not clear which region may search China Virus more or less often, but it does show a that the regions move together in search interest, which would imply federal level events like a Donald Trump tweet to trigger these interest spikes.
+
+```{r, warning=FALSE, message= FALSE, echo=FALSE}
+b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
+  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State")
+
+ggplotly(b)
+```
+
+We can see that the variability in Google interest in the term China Virus is has quite a large range between states.
+There are very few states that have high densities among the upper echelons of the interest scale but there are some interesting peaks of densities among the lower values.
+For example, we can see that Alaska, Wyoming and Iowa have unusual peaks around the 25-50 range.
+It is is also interesting interesting to note that there isn't an *obvious* mean or median value of China Virus interest among the states.
+
+### 2.3c COVID-19
+
+```{r, warning=FALSE, message= FALSE, echo=FALSE}
+c <-  ggplot(Finaldata, aes(y=positive, x=Winner, fill=(Winner)))+
+      geom_boxplot() +
+      facet_wrap(~Region)+
+      theme(legend.position = "none") +
+      scale_fill_manual(values = c("Democrat"="blue3", "Republican"= "red3"))+
+      lims(y= c(0,1000))+
+      ggtitle("Positive COVID-19 Cases by State Political Party Winner & Region")
+```
+
+```{r, warning=FALSE}
+ggplotly(c)
+```
+This visualisation depicts the distribution of positive COVID-19 cases by region and by which political party won in the 2016 elections.
+We can see that Democrat states in the Midwest, Mountain, and West have a larger range and higher quantile metrics for positive cases overall.
+For the Northeast and South regions the mean of positive COVID-19 cases are higher but not significantly.
+This is an interesting pattern considering that poltical party affiliation appears to interact with the number of postive cases by region.
 

### 2020-05-04 Final-Draft.Rmd
plots

@@
   filter(Day<=day_final)
+
+names(Finaldata)
 ```
@@
 
+ggplotly(p1)
+
 p2<- plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
@@
 
-grid.arrange(p1,p2)
+ggplotly(p2)
 
 ```
+
 Our first visualization is looking at the percent of residents that identify as white within the United States compared to those whom identify as asian.
@@
 
-ggplotly(e)
+e
 ```
+
 During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns across states.

### 2020-05-04 Draft-Report.Rmd

@@
 $$\begin{aligned}
-i = state, j = \text{days since "2020-03-14"}
-Y_{ij}|\theta,\mu,\beta_0, \beta_1, \beta_2,\beta_3,\beta_4,\sigma_w,\sigma_b \sim N(\theta_i +\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4, \sigma_w^2)\\
+i = state, j = \text{days since "2020-03-14"}\\
+Y_{ij}|\theta,\mu,\beta_0, \beta_1, \beta_2,\beta_3,\beta_4,\sigma_w,\sigma_b \sim N(\theta_i +\beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4, \sigma_w^2)\\
 \theta_i|\mu, \sigma_b \overset{ind}{\sim}N (\mu, \sigma_b^2)\\
@@
 X_2 = \text{percent_white},,X_3 =\text{StateColor},  X_4 =\text{Total Test Results} \\
-Y_{ij} | b_0, b_1, \beta_0, \beta_1, \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N( b_{0i} + b_{1i} X_{ij}+ \beta_2X_2 + \beta_3X_3 +\beta_4X_4, \; \sigma_w^2) \\
+Y_{ij} | b_0, b_1, \beta_0, \beta_1,\beta_2,\beta_3,\beta_4 \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N( b_{0i} + b_{1i} X_{ij}+ \beta_2X_2 + \beta_3X_3 +\beta_4X_4, \; \sigma_w^2) \\
 b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\

### 2020-05-04 Final-Draft.Rmd
s

@@
 # 2. Data
-```{r results = "hide", echo=FALSE, warning=FALSE, message = FALSE}
+```{r}
 
@@
 Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
-day_initial<- as.Date("2020-03-14")
-day_final<- as.Date("2020-03-21")
+day_initial<- as.Date("03/14/2020")
+day_final<- as.Date("03/21/2020")
+
 Finaldata<- Finaldata%>%
@@
 
-names(Finaldata)
+View(Finaldata)
 ```
@@
 ### 2.3a Demographic
+
+```{r}
+Finaldata$hover <- with(Finaldata, paste(State, '<br>', "Positive Cases:", positive, "<br>","Positive Negative:", negative,"<br>",
+                           "Total Cases:", totalTestResults,"<br>", "% White:", percent_white,"<br>",
+                            "% Asian:", percent_asian, "<br>", "State Color:", StateColor))
+# give state boundaries a white border
+l <- list(color = toRGB("white"), width = 2)
+# specify some map projection/options
+g <- list(
+  scope = 'usa',
+  projection = list(type = 'albers usa'),
+  showlakes = TRUE,
+  lakecolor = toRGB('white')
+)
+
+fig <- plot_geo(Finaldata, locationmode = 'USA-states')
+fig <- fig %>% add_trace(
+    z = ~ChinaVirusInterest, text = ~hover, locations = ~State,
+    color = ~ChinaVirusInterest, colors = 'Purples'
+  )
+fig <- fig %>% colorbar(title = "Interest")
+fig <- fig %>% layout(
+    title = '2020 COVID-19 Cases, Demographics, & Politics by State<br>(Hover for breakdown)', geo=g
+  )
+
+fig
+```
+
 ```{r, warning=FALSE, message= FALSE, echo=FALSE}
@@
 
-p1<- plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
+plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
   scale_fill_continuous(name = "Percent White", label = scales::comma) + 
@@
   scale_fill_viridis_c(option = "plasma") + theme(plot.title = element_text(size=11))+ labs(fill = "% White")
-
-ggplotly(p1)
+p1
 
@@
   scale_fill_viridis_c(option = "plasma") + theme(plot.title = element_text(size=11))+ labs(fill = "% Asian")
-
-ggplotly(p2)
 
@@
 
-e
+ggplotly(e)
 ```

### 2020-05-04 Final-Draft.Rmd
changes fixing finaldata

@@
 
-Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
-day_initial<- as.Date("03/14/2020")
-day_final<- as.Date("03/21/2020")
+Finaldata <- Finaldata %>% mutate(Day= as.Date(Day, tryFormats = "%m/%d/%Y"))
+
+day_initial<- as.Date("03/14/2020",tryFormats = "%m/%d/%Y")
+day_final<- as.Date("03/21/2020",tryFormats = "%m/%d/%Y")
 
@@
 
-View(Finaldata)
 ```

### 2020-05-04 Final-Draft.Rmd
visuals

--- 2020-05-04 Final-Draft.Rmd
@@
 # 2. Data
-```{r results = "hide", echo=FALSE, warning=FALSE, message = FALSE}
+```{r, message=FALSE, include=FALSE}
 
@@
 
-Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
-day_initial<- as.Date("2020-03-14")
-day_final<- as.Date("2020-03-21")
+Finaldata <- Finaldata %>% mutate(Day= as.Date(Day, tryFormats = "%m/%d/%Y"))
+
+day_initial<- as.Date("03/14/2020",tryFormats = "%m/%d/%Y")
+day_final<- as.Date("03/21/2020",tryFormats = "%m/%d/%Y")
+
 Finaldata<- Finaldata%>%
@@
 
-names(Finaldata)
 ```
@@
 ### 2.3a Demographic
-```{r, warning=FALSE, message= FALSE, echo=FALSE}
-#Demographic: Identification 
-Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
 
-p1<- plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
-  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
-  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") +
-  theme(plot.title = element_text(hjust = 0.5)) +
-  scale_fill_viridis_c(option = "plasma") + theme(plot.title = element_text(size=11))+ labs(fill = "% White")
+```{r}
+Finaldata$hover <- with(Finaldata, paste(polyname, "<br>","Positive Cases:", positive, "<br>","Negative Cases:", negative,"<br>",
+                           "Total Cases:", totalTestResults,"<br>", "% White:", percent_white,"<br>",
+                            "% Asian:", percent_asian, "<br>", "State Color:", StateColor,
+                        "<br>", "Total Population", total_population))
+# give state boundaries a white border
+l <- list(color = toRGB("white"), width = 2)
+# specify some map projection/options
+g <- list(
+  scope = 'usa',
+  projection = list(type = 'albers usa'),
+  showlakes = TRUE,
+  lakecolor = toRGB('white')
+)
 
-ggplotly(p1)
+fig <- plot_geo(Finaldata, locationmode = 'USA-states')
+fig <- fig %>% add_trace(
+    z = ~ChinaVirusInterest, text = ~hover, locations = ~State,
+    color = ~ChinaVirusInterest, colors = 'Oranges'
+  )
+fig <- fig %>% colorbar(title = "Interest")
+fig <- fig %>% layout(
+    title = '2020 Google Search Interest of "China Virus" by State <br>(Hover for additional information)', geo=g
+  )
 
-p2<- plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
-  scale_fill_continuous(name = "Percent Asian", label = scales::comma) + 
-  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as Asian") +
-  theme(plot.title = element_text(hjust = 0.5)) +
-  scale_fill_viridis_c(option = "plasma") + theme(plot.title = element_text(size=11))+ labs(fill = "% Asian")
+fig
+```
+```{r}
+Finaldata$hover <- with(Finaldata, paste(polyname, "<br>","Positive Cases:", positive, "<br>","Negative Cases:", negative,"<br>",
+                           "Total Cases:", totalTestResults,"<br>", "% White:", percent_white,"<br>",
+                            "% Asian:", percent_asian, "<br>", "State Color:", StateColor,
+                        "<br>", "Total Population", total_population))
+# give state boundaries a white border
+l <- list(color = toRGB("white"), width = 2)
+# specify some map projection/options
+g <- list(
+  scope = 'usa',
+  projection = list(type = 'albers usa'),
+  showlakes = TRUE,
+  lakecolor = toRGB('white')
+)
 
-ggplotly(p2)
+fig <- plot_geo(Finaldata, locationmode = 'USA-states')
+fig <- fig %>% add_trace(
+    z = ~percent_white, text = ~hover, locations = ~State,
+    color = ~percent_white, colors = 'Blues'
+  )
+fig <- fig %>% colorbar(title = "Interest")
+fig <- fig %>% layout(
+    title = '2020 Percent White by State <br>(Hover for additional information)', geo=g
+  )
+
+fig
+```
+```{r}
 
@@
 
-```{r, warning=FALSE, message= FALSE, echo=FALSE}
-e <- Finaldata%>%
-  ggplot(aes(x = ChinaVirusInterest))+
-  geom_density()
-
-e
-```
-
 During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns across states.
-
-As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relatively normal with a small bump at 0.
-As a group we believe this bump occurs as 0 is the lowest value it can take and because of that limitation of the China Virus Interest we see a small bump around 0.
-One could argue against a normal distribution as it kinda looks a bit right skewed.
-But our team believes that a normal distribution is the best at describing the density.
-
-When China Virus Interest equals 0 it means that no one in the state looked up the term in Google and this is prevalent at the 14 of March where there are 5 occurrences and the 21 of March where there are 4 occurrences.
-And in states such as DC, ND, SD, and VT.
 
@@
 ```
+
 This plot shows the relationship of “China Virus” search interest over grouped by region.
@@
 b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
-  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State")
+  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State") + labs(fill="State")
 
@@
 ```
+As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relatively normal with a small bump at 0.
+As a group we believe this bump occurs as 0 is the lowest value it can take and because of that limitation of the China Virus Interest we see a small bump around 0.
+One could argue against a normal distribution as it kinda looks a bit right skewed.
+But our team believes that a normal distribution is the best at describing the density.
 

### 2020-05-04 Final-Draft.Rmd
cahnges

--- 2020-05-04 Final-Draft.Rmd
@@
 
-## 3.1 Markov Chain Algorithm
+## Model 1 Repeated Measures Model
 
-## 3.2 Models of Interest
+  For our simplest model we decided to use a repeated measures model.
+Our team decided that the repeated measures model was necessary component because of how our data is set up.
+As we can see in our dataset, each state has a value for their `ChinaVirusInterest` for each day in our target period (2020-03-14 - 2020-03-21).
+Given the ability to use repeated measures and our prior understanding of the varying characteristics (demographic,political,covid-impact) within different states, the repeated measures model allows us to capture these differences in `ChinaVirusInterest` with the $\theta_i$ value which represents each state's mean value.
 
-## 3.3 Model Descriptions
+### Model Structure
+
+$$\begin{aligned}
+Y_{ij}|\theta_i, \mu, \sigma_w, \sigma_b \sim N(\theta_i,\sigma_w^2)\\
+\theta_i|\mu,\sigma_b \overset{ind}{\sim} N(\mu, \sigma_b^2)\\
+\sigma_b,\sigma_w \sim Exp(...)
+\end{aligned}$$
+
+$Y_{ij} = $ `ChinaVirusInterest` per $i=State$, and $j= Day$
+$\theta_i = $ State i's unique mean value
+$\sigma_w = $ within state variation
+$\sigma_b = $ between state variation
+
+```{r}
+model_data<-
+  Finaldata%>%
+  mutate(Day=as.numeric(Day)-as.numeric(min(Day)))%>%
+  select(ChinaVirusInterest, Day, percent_white, StateColor, positive, State)
+
+model_data<- na.omit(model_data)
+```
+
+```{r}
+#Repeated Measures Model
+set.seed(454)
+RM_model <- stan_glmer(
+  ChinaVirusInterest ~ (1 | State),
+  data = model_data, family = gaussian,
+)
+```
+
+### 3.2 Model Descriptions
 
@@
 
-# 4. Model Evaluation
+# 4. Model Evaluation (RESULTS)
 
-## 4.1 Model 1 Evaluation( Repeated measures)
+## 4.1 Model 1 Evaluation (Repeated measures)
 

### 2020-05-04 Final-Draft.Rmd
Update Final-Draft.Rmd
Model 2 Eval

@@
 
+```{r}
+g1 <- mcmc_dens(RM_model, pars = "sigma") + 
+  labs(x = expression(sigma[w])) +
+  lims(x=c(5, 25))
+g2 <- mcmc_dens(RM_model, 
+  pars = "Sigma[State:(Intercept),(Intercept)]", transformations = sqrt) + 
+  labs(x = expression(sigma[b])) +
+   lims(x=c(5, 25))
+grid.arrange(g1,g2,ncol=2)
+```
+
+In the output above we see that the within deviation is much narrow than the between deviation.
+This matches our intuition in the model that utilizing the repeated measures, fixed effects model will be able to explain a greater amount of the variation.
+
+```{r}
+# Store the chains
+rm_df <- as.array(RM_model) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+rm_df <- rm_df %>% 
+  mutate(sigma_sq_w = sigma^2, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = sigma_sq_b / (sigma_sq_b + sigma_sq_w))
+
+ggplot(rm_df, aes(x = correlation)) + 
+    geom_density()
+```
+
+This correlation table shows us that there is relatively strong correlation within each given daily observation within a state.
+Therefore, it is correct for us to utilize a fixed effects model in order to account for these inherent differences between states.
+
 ## 4.2 Model 2 Evaluation (Normal Regression)

### 2020-05-04 Final-Draft.Rmd
visuals

--- 2020-05-04 Final-Draft.Rmd
@@
 library(dplyr)
+library(ggrepel)
 library(usmap)
@@
 
-```{r}
+```{r, echo=FALSE, warning=FALSE}
 Finaldata$hover <- with(Finaldata, paste(polyname, "<br>","Positive Cases:", positive, "<br>","Negative Cases:", negative,"<br>",
@@
 
-fig
-```
-```{r}
-Finaldata$hover <- with(Finaldata, paste(polyname, "<br>","Positive Cases:", positive, "<br>","Negative Cases:", negative,"<br>",
-                           "Total Cases:", totalTestResults,"<br>", "% White:", percent_white,"<br>",
-                            "% Asian:", percent_asian, "<br>", "State Color:", StateColor,
-                        "<br>", "Total Population", total_population))
-# give state boundaries a white border
-l <- list(color = toRGB("white"), width = 2)
-# specify some map projection/options
-g <- list(
-  scope = 'usa',
-  projection = list(type = 'albers usa'),
-  showlakes = TRUE,
-  lakecolor = toRGB('white')
+#########white fig
+whitefig <- plot_geo(Finaldata, locationmode = 'USA-states')
+whitefig <- whitefig %>% add_trace(
+    z = ~percent_white, locations = ~State,
+    color = ~percent_white, colors = 'Blues'
+  )
+whitefig <- whitefig %>% colorbar(title = "% White")
+whitefig <- whitefig %>% layout(
+    title = 'Percent White Identifying by State', geo=g
   )
 
-fig <- plot_geo(Finaldata, locationmode = 'USA-states')
-fig <- fig %>% add_trace(
-    z = ~percent_white, text = ~hover, locations = ~State,
-    color = ~percent_white, colors = 'Blues'
+#### Asian fig
+asianfig <- plot_geo(Finaldata, locationmode = 'USA-states')
+asianfig <- asianfig %>% add_trace(
+    z = ~percent_asian, locations = ~State,
+    color = ~percent_asian, colors = 'Greens'
   )
-fig <- fig %>% colorbar(title = "Interest")
-fig <- fig %>% layout(
-    title = '2020 Percent White by State <br>(Hover for additional information)', geo=g
+asianfig <- asianfig %>% colorbar(title = "% Asian")
+asianfig <- asianfig %>% layout(
+    title = 'Percent Asian Identifying by State', geo=g
   )
@@
 fig
-```
-```{r}
+
+whitefig
+
+asianfig
 
@@
 ```{r, warning=FALSE, message= FALSE, echo=FALSE}
-Trump<- as.Date("03/16/2020", format = "%m/%d/%Y")
-day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
-day2<-as.Date("03/24/2020",format = "%m/%d/%Y")
 
-google_ts<-google%>%
-  mutate(Day = as.Date(as.character(Day)))
-
-a<-google_ts %>% 
+a<-Finaldata %>% 
   #filter(Day<=day2)%>%
@@
   ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
-  geom_point()
+  geom_point()+ geom_line()
 
@@
       ggtitle("Positive COVID-19 Cases by State Political Party Winner & Region")
-```
-
-```{r, warning=FALSE}
 ggplotly(c)
@@
 
-## Model 1 Repeated Measures Model
+## 3.1 Markov Chain Algorithm
 
-  For our simplest model we decided to use a repeated measures model.
-Our team decided that the repeated measures model was necessary component because of how our data is set up.
-As we can see in our dataset, each state has a value for their `ChinaVirusInterest` for each day in our target period (2020-03-14 - 2020-03-21).
-Given the ability to use repeated measures and our prior understanding of the varying characteristics (demographic,political,covid-impact) within different states, the repeated measures model allows us to capture these differences in `ChinaVirusInterest` with the $\theta_i$ value which represents each state's mean value.
+## 3.2 Models of Interest
 
-### Model Structure
-
-$$\begin{aligned}
-Y_{ij}|\theta_i, \mu, \sigma_w, \sigma_b \sim N(\theta_i,\sigma_w^2)\\
-\theta_i|\mu,\sigma_b \overset{ind}{\sim} N(\mu, \sigma_b^2)\\
-\sigma_b,\sigma_w \sim Exp(...)
-\end{aligned}$$
-
-$Y_{ij} = $ `ChinaVirusInterest` per $i=State$, and $j= Day$
-$\theta_i = $ State i's unique mean value
-$\sigma_w = $ within state variation
-$\sigma_b = $ between state variation
-
-```{r}
-model_data<-
-  Finaldata%>%
-  mutate(Day=as.numeric(Day)-as.numeric(min(Day)))%>%
-  select(ChinaVirusInterest, Day, percent_white, StateColor, positive, State)
-
-model_data<- na.omit(model_data)
-```
-
-```{r}
-#Repeated Measures Model
-set.seed(454)
-RM_model <- stan_glmer(
-  ChinaVirusInterest ~ (1 | State),
-  data = model_data, family = gaussian,
-)
-```
-
-### 3.2 Model Descriptions
+## 3.3 Model Descriptions
 
@@
 
-# 4. Model Evaluation (RESULTS)
+# 4. Model Evaluation
 
-## 4.1 Model 1 Evaluation (Repeated measures)
+## 4.1 Model 1 Evaluation( Repeated measures)
 

### 2020-05-04 Final-Draft.Rmd

@@
 
-# 4. Model Evaluation
+# 4. Model Evaluation (RESULTS)
 
-## 4.1 Model 1 Evaluation( Repeated measures)
+## 4.1 Model 1 Evaluation (Repeated measures)
+
+```{r}
+g1 <- mcmc_dens(RM_model, pars = "sigma") + 
+  labs(x = expression(sigma[w])) +
+  lims(x=c(5, 25))
+g2 <- mcmc_dens(RM_model, 
+  pars = "Sigma[State:(Intercept),(Intercept)]", transformations = sqrt) + 
+  labs(x = expression(sigma[b])) +
+   lims(x=c(5, 25))
+grid.arrange(g1,g2,ncol=2)
+```
+
+In the output above we see that the within deviation is much narrow than the between deviation.
+This matches our intuition in the model that utilizing the repeated measures, fixed effects model will be able to explain a greater amount of the variation.
+
+```{r}
+# Store the chains
+rm_df <- as.array(RM_model) %>% 
+  melt %>% 
+  pivot_wider(names_from = parameters, values_from = value)
+
+# Wrangle the chains
+rm_df <- rm_df %>% 
+  mutate(sigma_sq_w = sigma^2, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
+  mutate(correlation = sigma_sq_b / (sigma_sq_b + sigma_sq_w))
+
+ggplot(rm_df, aes(x = correlation)) + 
+    geom_density()
+```
+
+This correlation table shows us that there is relatively strong correlation within each given daily observation within a state.
+Therefore, it is correct for us to utilize a fixed effects model in order to account for these inherent differences between states.
 

### 2020-05-04 Final-Draft.Rmd
changes

--- 2020-05-04 Final-Draft.Rmd
@@
 
-$Y_{ij} = $ `ChinaVirusInterest` per $i=State$, and $j= Day$
-$\theta_i = $ State i's unique mean value
-$\sigma_w = $ within state variation
-$\sigma_b = $ between state variation
+\
+$Y_{ij} =$ `ChinaVirusInterest` per:
+\
+$i=State$
+\
+and $j= Day$ 
+\
+$\theta_i =$ State i's unique mean value
+\
+$\sigma_w =$ within state variation
+\
+$\sigma_b =$ between state variation
+
+ We decided that our MCMC model should take in values from a normal distribution because ChinaVirusInterest's distribution is fairly normal.
+Although the tails are not as flat as we would want them to be, we can decided that a normal distribution was best to model ChinaVirusInterest.
 
@@
 
-```{r}
+```{r results = "hide", include = FALSE, cache=TRUE}
 #Repeated Measures Model
@@
 
-### 3.2 Model Descriptions
+## Model2: Normal Regression
+
+For our second model, we decided that we wanted to understand what made some states more responsive to ChinaVirusInterest than others.
+As you saw in our research motivation section, we wanted to explore what explained the differences in interest for the “China Virus” term.
+Was it a political difference, a demographic or a covid-impact related difference?
+To do this we used a simple Normal Regression model with the following specifications.
+For our demographic specification we used `percent_white`, for our political specification we used `StateColor` and for our Covid-impact specification we used `positive` (#of positive cases).
+
+### Model Structure
+$$\begin{aligned}
+Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3,\beta_4 &\overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4,\sigma^2)\\
+\beta_0,\beta_1, \beta_2,\beta_3 &\sim N(...,...)\\
+\sigma &\sim Exp(...)\\
+\end{aligned}$$
+
+$Y = ChinaVirusInterest\\$
+\
+$i = state\\$
+\
+$j = Days\\$
+\
+$X_{ij} = \text{Days}\\$
+\
+$X_2 = \text{percent_white}\; X_3 =\text{StateColor}\;   X_4 =\text{Total Test Results}\\$
+\
+$\sigma = \text{Variance in }$ `ChinaVirusInterest`
+\
+
+```{r results = "hide", include = FALSE, cache=TRUE}
+#Normal Regression Model
+set.seed(454)
+NR_model <- stan_glm(
+  ChinaVirusInterest ~ Day + percent_white+StateColor+positive,
+  data = model_data, family = gaussian,
+  chains = 4, iter = 10000, refresh = 0
+)
+```
+
+## Model 3: Normal Regression + Repeated Measures
+
+For our third model, we decided to combine the first two models to first understand variations in political, demographic, covid-related variables and also be able to capture variation that we could not explain in model 2.
+Additionally, we kept the correlation structure that we saw in model 1, but we included the variables in model 2 so that we could explain why some states had a larger `ChinaVirusInterest` than others.
+Similar to model 1, model 3 allows us to capture differences in `ChinaVirusInterest` with the $\theta_i$ value which represents each state's mean value.
+### Model Structure
+
+$$\begin{aligned}
+Y_{ij}|\theta,\mu,\beta_0, \beta_1, \beta_2,\beta_3,\beta_4,\sigma_w,\sigma_b &\sim N(\theta_i +\beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4, \sigma_w^2)\\
+\theta_i|\mu, \sigma_b &\overset{ind}{\sim}N (\mu, \sigma_b^2)\\
+\beta_0,\beta_1, \beta_2,\beta_3 &\sim N(...,...)\\
+\sigma_w,\sigma_b &\sim Exp(...)\\
+\end{aligned}$$
+
+$Y = ChinaVirusInterest\\$
+\
+$i = state\\$
+\
+$j = Days\\$
+\
+$X_{ij} = \text{Days}\\$
+\
+$X_2 = \text{percent_white}\; X_3 =\text{StateColor}\;   X_4 =\text{Total Test Results}\\$
+\
+$\sigma_w = \text{within state variation} \\$
+\
+$\sigma_b =  \text{between state variation}\\$
+\
+
+```{r results = "hide", include = FALSE, cache=TRUE}
+set.seed(454)
+
+model_2 <- stan_glmer(
+  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (1 | State), 
+  data = model_data, family = gaussian, chains = 4, iter = 5000*2
+)
+```
+
+## Model 4: Longitudinal Model (state-specific slopes)
+
+Because of the structure of our data, we are also able to create a longitudinal model as we have repeated measures for `ChinaVirusInterest` and corresponding observations for `Day`.
+In this more complex model we allow for state-specific slopes and intercepts to predict their behavior of `ChinaVirusInterest`.
+As the Days increase we get closer to when Trump addressed the Corona Virus as "China Virus".
+Thus if we see increasing slopes we might conclude that in that state, the effect of Trump addressing the Corona Virus as "China Virus" created an increase in the interest of the term and viceversa.
+
+### Model Structure
+
+$$
+\begin{split}
+Y_{ij} | b_0, b_1, \beta_0, \beta_1,\beta_2,\beta_3,\beta_4 \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N( b_{0i} + b_{1i} X_{ij}+ \beta_2X_2 + \beta_3X_3 +\beta_4X_4, \; \sigma_w^2) \\
+b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
+b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
+\beta_0,\beta_1,\beta_2,\beta_3,\beta_4 & \sim N(..., ...) \\
+\sigma_w & \sim Exp(...) \\
+\sigma_{0b} & \sim Exp(...) \\
+\sigma_{1b} & \sim Exp(...) \\
+\end{split}
+$$
+In this hierarchical model each state receives a specific slope and intercept.
+The first step is determined through determining the $\beta_{0} - \beta_{4}$ values which represent the intercept, slope, and our three demographic interactions that we bring in from model 3.
+The $\beta_{0}$ represents the intercept value for all states.
+From this value each state derives its individual $b_{0i}$ which represents that state’s individual intercept value.
+In the diagram below we see that the $b_{0i}$ values are normally distributed around the $\beta_{0}$ and are distributed by $\sigma_{0b}$.
+This same process occurs for determining state specific slopes however we use $\beta_{1}$ and $b_{1i}$.
+
+The main purpose of this model is to find the magnitude of $\sigma_{1b}$ since this deviation is what determines the significance of their truly being state level unique slopes or not, and therefore determines if we need to use this more flexible model to predict `ChinaVirusInterest`.
+
+\
+$Y = ChinaVirusInterest\\$
+\
+$i = state\\$
+\
+$j = Days\\$
+\
+$X_{ij} = \text{Days}\\$
+\
+$X_2 = \text{percent_white}\; X_3 =\text{StateColor}\;   X_4 =\text{Total Test Results}\\$
+\
+$\sigma_w = \text{within state variation} \\$
+\
+$\sigma_{0b} =  \text{between state variation for intercept}\\$
+\
+$\sigma_{1b} = \text{between state variation for slopes}\\$
+\
+$X_{ij} = \text{Days}$
+\
+$b_{0i} = \text{State-Specific-Intercept}$
+\
+$\beta_0 = \text{Population-wide-Intercept}$
+\
+$b_{1i} = \text{State-Specific-Slope}$
+\
+$\beta_1 = \text{Population-wide-Slope}$
+
+```{r results = "hide", include = FALSE, cache=TRUE}
+set.seed(454)
+complexmod <- stan_glmer(
+  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (Day | State), 
+  data = model_data, family = gaussian, chains = 4, iter = 5000*2
+)
+```
 
@@
 
-This correlation table shows us that there is relatively strong correlation within each given daily observation within a state.
-Therefore, it is correct for us to utilize a fixed effects model in order to account for these inherent differences between states.
+This correlation table shows us that there is relatively weak correlation within each given daily observation within a state.
+Although there is not a strong correlation, it is correct for us to utilize a repeated measuress model in order to account for the correlation within states.
+
+##mcmc_ stable
+
+##ppcheck
 
@@
 
+##mcmc_ stable
+
+##ppcheck
+
 ## 4.3 Model 3 Evaluation(Repeated Reg + Normal)
 
+##mcmc_ stable
+
+##ppcheck
+
 ## 4.4 Model 4 Evaluation (Longitudinal)
+
+##mcmc_ stable
+
+##ppcheck
+
+## Are our models strong?: Prediction & classification summaries
+
+```{r}
+#Repeated Measures
+set.seed(454)
+pred_1 <- posterior_predict(
+  RM_model,
+  newdata = model_data, transform = TRUE)
+
+sum1<-prediction_summary(y = model_data$ChinaVirusInterest,
+  yrep = pred_1)
+```
+
+```{r}
+#Normal Regression
+set.seed(454)
+pred_2 <- posterior_predict(
+  NR_model,
+  newdata = model_data, transform = TRUE)
+
+sum2<-prediction_summary(y = model_data$ChinaVirusInterest,
+  yrep = pred_2)
+```
+
+```{r}
+#Repeated Measures + Normal Regression
+set.seed(454)
+pred_3 <- posterior_predict(
+  model_2,
+  newdata = model_data, transform = TRUE)
+
+sum3<-prediction_summary(y = model_data$ChinaVirusInterest,
+  yrep = pred_3)
+```
+
+```{r}
+#Longitudinal Model
+set.seed(454)
+pred_4 <- posterior_predict(
+  complexmod,
+  newdata = model_data, transform = TRUE)
+
+sum4<-prediction_summary(y = model_data$ChinaVirusInterest,
+  yrep = pred_4)
+```
+
+```{r}
+all_summ<-rbind(sum1,sum2,sum3,sum4)
+rownames(all_summ)<- c("Model 1","Model 2","Model 3","Model 4")
+all_summ
+```
 

### 2020-05-04 Final-Draft.Rmd
adding intro

--- 2020-05-04 Final-Draft.Rmd
@@
 
-On March 17, 2020 President Trump referred to the Coronavirus as the "China Virus." Shortly after, the number of anti-Chinese incidents started to increase across the United States.
+On March 17, 2020 President Trump referred to the Coronavirus as the "China Virus." Shortly after, there was an uptick in verbal and physical attacks against Asian-Americans.
 One aspect of public health that is often thrown to the wayside is how influential public officials and leaders are in disseminating public health information.
 Moreover, not only can their words change the public's views on a health matter but it can also shift a nation's perspective on someone's identity.
-_[ADD SOME BACKGROUND LITERATURE THAT BACKS THIS CLAIM UP]_ In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identities and states.
-_[ADD BACKGROUND LITERATURE + IDENTIFY SUBJECTS OF INTEREST]_.
-There are fewer studies devoted to analyzing these aspects of the pandemic.
+The Asian Pacific Policy and Planning Council reported that in their first four weeks of receiving reports on COVID-19 anti-Asian discirimnation, they recieved more than 1,500 incidents [CITE].
+This abrupt spasm of racism mimics the kind faced by American Muslims, Arabs and South Asians in the United States after the terrorist attacks of 9/11.
+However, when President George W.
+Bush urged tolerance of American Muslims, this time President Trump is using language that Asian-Americans say is inciting racist attacks.
 
-Thus,our project aims to explore the relationship and variability of interest in the term "China Virus" across states through  political, demographic and COVID-19 characteristics.
-We ask the question, _[INSERT OUR RESERACH QUESTION]_ ?
-In order to answer this question, we look to gain a better understanding of _[INSERT NAME OF BAYESIAN METHODOLOGY]_.
-Ultimately, we hope our research inspires others to explore and better understand the impact langauge and words have on the public during times of crisis.
+In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identities and states.The Pew Reserach Center discovered that nearly three-quarters of Repbulicans and Republican-leaning indepdents view China unfavoriably[CITE].
+But the majority of reports to the AAPI were from Democrat leaning states like California, Washington and Illinois [CITE].
+Moreover, states that have a higher number of reported positive cases tend to have a higher interest in Googling the term "China Virus" [CITE].
+Thus, this begs the question: What factors of the poltiical, demographic and COVID-19 spheres best predicts the level of interest a state will have in the term "China Virus?"
+
+In order to answer this question, we utilized Monte Carlo Markov Chains to build four predictive models that included some of the variables mentioned above.
+Model 1 is our simplest model while Model 4 is our most complex model.
+We then ran several different diagnostic tests such as MCMC and PP checks to evaluate the quality and structures of our models.
+While all the models had some different levels of predictive strength, our best model was ___________.
+This model proved to provide the best balance between complexity and quality.
 
@@
 
-```{r, echo=FALSE, warning=FALSE}
+```{r, echo=FALSE, warning=FALSE, fig.align=center}
 Finaldata$hover <- with(Finaldata, paste(polyname, "<br>","Positive Cases:", positive, "<br>","Negative Cases:", negative,"<br>",
@@
 asianfig <- asianfig %>% layout(
-    title = 'Percent Asian Identifying by State', geo=g
+    title = 'Comparison of Percent Asian and White Identifying by State',geo=g
   )
@@
 fig
-
-whitefig
-
-asianfig
+subplot(whitefig,asianfig)
 
@@
 
-```{r}
+```{r, message=FALSE, include=FALSE}
 model_data<-
@@
 
-```{r}
+```{r, message=FALSE, include=FALSE}
 #Repeated Measures Model
@@
 
-```{r}
+```{r, message=FALSE, include=FALSE}
 g1 <- mcmc_dens(RM_model, pars = "sigma") + 
@@
 
-```{r}
+```{r, message=FALSE, include=FALSE}
 # Store the chains

### 2020-05-04 Final-Draft.Rmd

--- 2020-05-04 Final-Draft.Rmd
@@
 ```{r results = "hide", include = FALSE, cache=TRUE}
+
 #Repeated Measures Model

### 2020-05-04 Final-Draft.Rmd
Update Final-Draft.Rmd

@@
 
-model_2 <- stan_glmer(
+model_3 <- stan_glmer(
   ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (1 | State), 
@@
 ##mcmc_ stable
+```{r}
+mcmc_trace(RM_model)
+mcmc_dens_overlay(RM_model) 
+```
 
 ##ppcheck
+
+```{r}
+pp_check(RM_model)
+```
 
@@
 
+```{r}
+mcmc_trace(NR_model)
+mcmc_dens_overlay(NR_model) 
+```
 ##ppcheck
@@
 
+```{r}
+mcmc_trace(model_3)
+mcmc_dens_overlay(model_3) 
+```
+
 ##ppcheck
+```{r}
+pp_check(model_3)
+```
 
@@
 
+```{r}
+mcmc_trace(complexmod)
+mcmc_dens_overlay(complexmod) 
+```
+
 ##ppcheck
+
+```{r}
+pp_check(complexmod)
+```
 

### 2020-05-05 Final-Draft.Rmd
changes

--- 2020-05-04 Final-Draft.Rmd
@@
 
-##mcmc_ stable
+##mcmc plots
+```{r}
+mcmc_trace(RM_model, pars = c("(Intercept)","Sigma[State:(Intercept),(Intercept)]"))
+mcmc_dens_overlay(RM_model, pars = c("(Intercept)","Sigma[State:(Intercept),(Intercept)]")) 
+```
+
+As we can see in this mcmc trace plot, it looks like our MCMC is fairly stable but could do with a bit more stability as we see that the peaks are spread around the 40-42.5 range.
+We also see that our values for $\sigma_b^2$ is greater than 0, our value of sigma is around 75 meaning that we must include random intercepts in our final model
 
@@
 
+```{r}
+pp_check(RM_model, nreps=50)
+```
+
+Overall, we can see that our repeated measures model it tells us that the structure of our model is fairly reasonable, In other words, the assumption of using a normal model is fairly reasonable outside of the fact that the tails are a bit thicker than we would want them to be.
+This is because we are expecting a lot of states that will have multiple days with zero value, if no one in the state looks up the term.
+This is why our tails are a bit thicker than we would want them to be, specially around 0.
+
 ## 4.2 Model 2 Evaluation (Normal Regression)
 
-##mcmc_ stable
+##mcmc plots
+
+```{r}
+# Trace plots
+mcmc_trace(NR_model,pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))
+
+# Density plots
+mcmc_dens_overlay(NR_model, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))
+```
+Compared to the previous model, it looks that our chains are more stable and they have closer peaks.
 
@@
 
+```{r}
+pp_check(NR_model, nreps = 50)
+```
+
+Although our posterior predictive check is pretty similar to our previous model, we see that the peaks are a bit more closer together.
+And similar to the previous model the structure of the GLM is fairly reasonable.
+
 ## 4.3 Model 3 Evaluation(Repeated Reg + Normal)
 
-##mcmc_ stable
+```{r}
+mcmc_trace(model_3, pars=c("(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[(Intercept) State:AK]","b[(Intercept) State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
+
+mcmc_trace(model_3, pars = c("sigma","Sigma[State:(Intercept),(Intercept)]"))
+
+mcmc_dens_overlay(model_3, pars = c("(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[(Intercept) State:AK]","b[(Intercept) State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
+
+mcmc_dens_overlay(model_3, pars = c("sigma","Sigma[State:(Intercept),(Intercept)]"))
+```
+
+Compared to the previous model, we see that our chains are more stable for the intercept and the percent_white variables as the peaks are closer together.
+We also see that our $\sigma_b^2$ is almost always above 0, and the density has a mean around 75 similar to our repeated measures model.
+
+##ppcheck
+```{r}
+pp_check(model_3, nreps=50)
+```
+As seen in our prior posterior predictive checks, they have similar errors around the tails. But it seems that our GLM structure is also reasonable for this model. 
+## 4.4 Model 4 Evaluation (Longitudinal)
+
+##mcmc plots
+
+```{r}
+# Trace plots
+mcmc_trace(complexmod,pars = c("(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[Day State:AK]","b[Day State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
+mcmc_trace(complexmod, pars = c("sigma"),regex_pars = "Sigma",facet_args = list(ncol = 2, strip.position = "left"))
+
+# Density plots
+mcmc_dens_overlay(complexmod, pars = c("(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[Day State:AK]","b[Day State:WA]"),regex_pars = "Sigma",facet_args = list(ncol = 4, strip.position = "left"))
+
+mcmc_dens_overlay(complexmod, pars = c("sigma"),regex_pars = "Sigma",facet_args = list(ncol = 2, strip.position = "left"))
+```
+
+In the dens overlay we can see that our value for $\sigma_{1b}^2$ is close to zero we could argue that random slopes are not necessary, but the mean of  $\sigma_{1b}^2$ is around 2-2.5.
+Similar to our previous dens overlay checks our value of $\sigma_b^2$ is almost always above zero and its mean is around 75, which means that random intercepts are necessary.
 
@@
 
-## 4.4 Model 4 Evaluation (Longitudinal)
-
-##mcmc_ stable
-
-##ppcheck
+```{r}
+pp_check(complexmod, nreps = 50)
+```
+Overall all ppchecks tend to have the similar graph because we are assuming a normal relationship on the response variable for all of them.
 
@@
 
-```{r}
+```{r, message=FALSE, include=FALSE}
 #Repeated Measures
@@
 
-```{r}
+```{r, message=FALSE, include=FALSE}
 #Normal Regression
@@
 
-```{r}
+```{r, message=FALSE, include=FALSE}
 #Repeated Measures + Normal Regression
@@
 pred_3 <- posterior_predict(
-  model_2,
+  model_3,
   newdata = model_data, transform = TRUE)
@@
 
-```{r}
+```{r, message=FALSE, include=FALSE}
 #Longitudinal Model
@@
 
+\
+\
+
+# 5. Results (Will)
+
+## 5.1 Posterior Predictions All States
+
+### 5.1.a Table
+
 ```{r}
@@
 
-\
-\
+As we can see in the table above, the lowest mae was achieved by our most complex model, Model 4 which allowed for both random slopes and random intercepts.
+But the mae value is not that different from the mae acchieved by Model 3 which was more simple allowing only for random intercepts.
+Interestingly Model 1 our simplest model had a higher proportion of the data falling within the 95% posterior predictive interval.
 
-# 5. Results (Will)
+### Why we chose Model 3 as our best model?
 
-## 5.1 Posterior Predctions All States
-
-### 5.1.a Table
+We believe that the decreases in mae and increases of the proporiton of values observed within 50% of the posterior predictive interval do not justify increasing the complexity.
+Which is why we argue that Model 3 is the best model because it acchieves similar results to model 4 without making it computationally expensive.
+But if we want a more precise model we would use Model 4.
 

### 2020-05-05 Final-Draft.Rmd
Update Final-Draft.Rmd
changes

@@
 
+\
+\
+
+# 5. Results (Will)
+
+## 5.1 Posterior Predictions All States
+
 ```{r, message=FALSE, include=FALSE}
@@
 
-```{r, message=FALSE, include=FALSE}
+```{r message=FALSE, include=FALSE}
 #Longitudinal Model
@@
 ```
-
-\
-\
-
-# 5. Results (Will)
-
-## 5.1 Posterior Predictions All States
 
@@
 
+```{r}
+### For predicting one case 
+new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) #Doesn't recognize state
+set.seed(454)
+pred_FL_RM <- posterior_predict(
+  RM_model,
+  newdata = new_FL)
+
+pred_FL_RM <- data.frame(y_new = pred_FL[-1])
+
+ggplot(pred_FL_RM, aes(x=y_new))+geom_density()
+
+summary(pred_FL_RM)
+```
+
+```{r}
+### For predicting one case 
+new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple") 
+set.seed(454)
+pred_FL_NR <- posterior_predict(
+  NR_model,
+  newdata = new_FL)
+
+pred_FL_NR <- data.frame(y_new = pred_FL[-1])
+
+ggplot(pred_FL_NR, aes(x=y_new))+geom_density()
+
+summary(pred_FL_NR)
+```
+
+```{r}
+### For predicting one case 
+new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple")
+set.seed(454)
+pred_FL_3 <- posterior_predict(
+  model_3,
+  newdata = new_FL)
+
+pred_FL_3 <- data.frame(y_new = pred_FL[-1])
+
+ggplot(pred_FL_3, aes(x=y_new))+geom_density()
+
+summary(pred_FL_3)
+```
+
+```{r}
+### For predicting one case 
+new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple")
+set.seed(454)
+pred_FL_complex <- posterior_predict(
+  complexmod,
+  newdata = new_FL)
+
+pred_FL_complex <- data.frame(y_new = pred_FL[-1])
+
+ggplot(pred_FL_complex, aes(x=y_new))+geom_density()
+
+summary(pred_FL_complex)
+```
+
+```{r}
+
+actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
+
+actual_FL_pred
+```
+
 ## 5.3 Final Model

### 2020-05-05 Final-Draft.Rmd
changes

@@
 
-pred_FL_RM <- data.frame(y_new = pred_FL[-1])
+pred_FL_RM <- data.frame(y_new = pred_FL_RM[-1])
 
@@
 
-pred_FL_NR <- data.frame(y_new = pred_FL[-1])
+pred_FL_NR <- data.frame(y_new = pred_FL_NR[-1])
 
@@
 
-pred_FL_3 <- data.frame(y_new = pred_FL[-1])
+pred_FL_3 <- data.frame(y_new = pred_FL_3[-1])
 
@@
 
-pred_FL_complex <- data.frame(y_new = pred_FL[-1])
+pred_FL_complex <- data.frame(y_new = pred_FL_complex[-1])
 
@@
 
-summary(pred_FL_complex)
+complex<-summary(pred_FL_complex)
 ```
@@
 ```{r}
+actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
+actual_FL_pred
+```
 
-actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
-
-actual_FL_pred
+```{r}
+modelevalFL<-read_csv("MODELEVAL.csv")
 ```

### 2020-05-05 Final-Draft.Rmd
Update Final-Draft.Rmd
pred changes

@@
 
-```{r}
+```{r, echo=FALSE, warning=FALSE}
 modelevalFL<-read_csv("MODELEVAL.csv")
+modelevalFL
 ```
+
+In this table each model's prediction of Florida on the final day of our target window compared with how the actual value in the set.
+We find that the predictions, especially with our more complex Models 3 & 4 are not particularly close, especially with Model 4 having an error of close to 6.
+However, we are aware that our MAEs have improved with the more sophisticated models.
 

### 2020-05-05 Final-Draft.Rmd
final changes w alicia

@@
 $$\begin{aligned}
-Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3,\beta_4 &\overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4,\sigma^2)\\
+Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3,\beta_4 &\overset{ind}{\sim} N(\beta_0+ \beta_1X_{1i} + \beta_2X_{2i} + \beta_3X_{3i}+ \beta_4X_{4i},\sigma^2)\\
 \beta_0,\beta_1, \beta_2,\beta_3 &\sim N(...,...)\\
@@
 $$\begin{aligned}
-Y_{ij}|\theta,\mu,\beta_0, \beta_1, \beta_2,\beta_3,\beta_4,\sigma_w,\sigma_b &\sim N(\theta_i +\beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4, \sigma_w^2)\\
+Y_{ij}|\theta,\mu,\beta_0, \beta_1, \beta_2,\beta_3,\beta_4,\sigma_w,\sigma_b &\sim N(\theta_i +\beta_1X_1 + \beta_2X_{2i} + \beta_3X_{3i}+ \beta_4X_{4i}, \sigma_w^2)\\
 \theta_i|\mu, \sigma_b &\overset{ind}{\sim}N (\mu, \sigma_b^2)\\
@@
 \begin{split}
-Y_{ij} | b_0, b_1, \beta_0, \beta_1,\beta_2,\beta_3,\beta_4 \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N( b_{0i} + b_{1i} X_{ij}+ \beta_2X_2 + \beta_3X_3 +\beta_4X_4, \; \sigma_w^2) \\
+Y_{ij} | b_0, b_1, \beta_0, \beta_1,\beta_2,\beta_3,\beta_4 ,\sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N( b_{0i} + b_{1i} X_{ij}+ \beta_2X_{2i} + \beta_3X_{3i} +\beta_4X_{4i}, \; \sigma_w^2) \\
 b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
@@
 
-In the dens overlay we can see that our value for $\sigma_{1b}^2$ is close to zero we could argue that random slopes are not necessary, but the mean of  $\sigma_{1b}^2$ is around 2-2.5.
+In the dens overlay we can see that our value for $\sigma_{1b}^2$ is close to zero but we could argue that random slopes are necessary, as the mean of  $\sigma_{1b}^2$ is around 2-2.5 and given that we are talking about slopes with not a very high range 2-2.5 is pretty good range for differing slopes.
 Similar to our previous dens overlay checks our value of $\sigma_b^2$ is almost always above zero and its mean is around 75, which means that random intercepts are necessary.
@@
 But if we want a more precise model we would use Model 4.
+But out mcmc_dens and our visualizations showed that there are different slopes across states and thus a more reasonable approach would be to use Model 4.
 
@@
 We find that the predictions, especially with our more complex Models 3 & 4 are not particularly close, especially with Model 4 having an error of close to 6.
-However, we are aware that our MAEs have improved with the more sophisticated models.
+However, we are aware that our MAEs are smaller in Models 3 and 4.
 
@@
 
+Truncated Normal Model** (0-100), really wide guesses.
+
 ## 6.2 Future Work

### 2020-05-05 Final-Draft.Rmd
finishing intro, addding table, cleaning doc

--- 2020-05-05 Final-Draft.Rmd
@@
 
-On March 17, 2020 President Trump referred to the Coronavirus as the "China Virus." Shortly after, there was an uptick in verbal and physical attacks against Asian-Americans.
+## 1.1 Background
+
+On March 17, 2020 President Trump referred to the Coronavirus as the "China Virus." Shortly after, throughout the subsequent weeks, there was an uptick in verbal and physical attacks against Asian-Americans (Olson, 2020).
 One aspect of public health that is often thrown to the wayside is how influential public officials and leaders are in disseminating public health information.
 Moreover, not only can their words change the public's views on a health matter but it can also shift a nation's perspective on someone's identity.
-The Asian Pacific Policy and Planning Council reported that in their first four weeks of receiving reports on COVID-19 anti-Asian discirimnation, they recieved more than 1,500 incidents [CITE].
-This abrupt spasm of racism mimics the kind faced by American Muslims, Arabs and South Asians in the United States after the terrorist attacks of 9/11.
+The Asian Pacific Policy and Planning Council reported that in their first four weeks of receiving reports on COVID-19 anti-Asian discirimnation, they recieved more than 1,500 incidents (Jeung & Nham 2020).
+This abrupt spasm of racism mimics the kind faced by American Muslims, Arabs and South Asians in the United States after the terrorist attacks of 9/11 (Tavernise & Oppel Jr, 2020).
 However, when President George W.
@@
 
-In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identities and states.The Pew Reserach Center discovered that nearly three-quarters of Repbulicans and Republican-leaning indepdents view China unfavoriably[CITE].
-But the majority of reports to the AAPI were from Democrat leaning states like California, Washington and Illinois [CITE].
-Moreover, states that have a higher number of reported positive cases tend to have a higher interest in Googling the term "China Virus" [CITE].
+In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identities and states.The Pew Reserach Center discovered that nearly three-quarters of Repbulicans and Republican-leaning indepdents view China unfavoriably (Devlin, et al 2020.
+But the majority of reports to the AAPI were from Democrat leaning states like California, Washington and Illinois [Jeung & Nham 2020].
+Moreover, states that have a higher number of reported positive cases tend to have a higher interest in Googling the term "China Virus" (2020).
 Thus, this begs the question: What factors of the poltiical, demographic and COVID-19 spheres best predicts the level of interest a state will have in the term "China Virus?"
 
+## 1.2 Brief Synopsis
 In order to answer this question, we utilized Monte Carlo Markov Chains to build four predictive models that included some of the variables mentioned above.
-Model 1 is our simplest model while Model 4 is our most complex model.
+Model 1, a repeated measures model, is our simplest model, Model 2 is a normal regression based, Model 3 is a combination of normal and repeated measures, and Model 4, our most complex model, is longitudinal based.
 We then ran several different diagnostic tests such as MCMC and PP checks to evaluate the quality and structures of our models.
-While all the models had some different levels of predictive strength, our best model was ___________.
-This model proved to provide the best balance between complexity and quality.
+While all the models had some different levels of predictive strength, our best model was a normal regression and repeated measures model, Model 3.
+This model proved to provide the best balance between complexity and quality.Model 3 captures important attributes that the normal model and repeated measures did not and it achieves similar results to our complex model, Model 4, without the heavy computational toll.
+Overall, we hope this project inspires others to explore the intereconnectdness of health, communication, politics and demography.
 
+\
 \
@@
 ## 2.2 Variables of interest
++------------------------+---------------------------------------------------+
+| Variables:             | Description:                                      |
++========================+===================================================+
+| `State`                | State abbreivation and main identifier            |
++------------------------+---------------------------------------------------+
+| `StateColor`           | Political Leaning of the state. Either red, blue  |
+|                        | or purple.                                        |
++------------------------+---------------------------------------------------+
+| `percent_white`        | Percent of the Population that is White           |
++------------------------+---------------------------------------------------+
+| `percent_asian`        | Percent of the Population that is Asian           |  
++------------------------+---------------------------------------------------+
+|`Positive`              | Number of reported positive COVID-19 cases        | 
++------------------------+---------------------------------------------------+
+|`Negative`              | Number of reported negative COVID-19 cases        | 
++------------------------+---------------------------------------------------+
+|`Day`                   | Date of report                                    | 
++------------------------+---------------------------------------------------+
+|`totalTestResults`      | Total Number test results (Positive +Negative)    | 
++------------------------+---------------------------------------------------+
+|`ChinaVirusInterest`    | Interest index from Google searches by state.     |
+|                        | Peak search day=100, all other days in set are    |
+|                        | based searches on relative to this peak day.      | 
++------------------------+---------------------------------------------------+
+|`Region`                | States divided into five different regions:       |
+|                        | West, South, Mountain, Northeast, Midwest         |
++------------------------+---------------------------------------------------+
 
@@
 
-```{r, warning=FALSE, message= FALSE, echo=FALSE}
+```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
 
@@
 
-```{r, warning=FALSE, message= FALSE, echo=FALSE}
+```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
 b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
@@
 ```
+
 As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relatively normal with a small bump at 0.
@@
 
+```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
+IAtoMT <- Finaldata %>% select(c(State,ChinaVirusInterest,Day)) %>% filter (State %in% c("IA","ID","IL","LA","MA","MD","ME","MI","MN","MO","MS","MT"))
+
+plot1<- ggplot(IAtoMT, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
+    geom_point() + 
+    geom_smooth(method = "lm", se = FALSE) + 
+    theme(legend.position = "none") +
+    facet_wrap(~State)
+
+ggplotly(plot1)
+```
+
 ### 2.3c COVID-19
 
-```{r, warning=FALSE, message= FALSE, echo=FALSE}
+```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
 c <-  ggplot(Finaldata, aes(y=positive, x=Winner, fill=(Winner)))+
@@
 ```
+
 This visualisation depicts the distribution of positive COVID-19 cases by region and by which political party won in the 2016 elections.
@@
 
-## Model 1 Repeated Measures Model
+## 3.1 Model 1 Repeated Measures Model
 
@@
 
-### Model Structure
+### 3.1a Model Structure
 
@@
 
-## Model2: Normal Regression
+## 3. 2 Model 2: Normal Regression
 
@@
 
-### Model Structure
+### 3.2a Model Structure
 $$\begin{aligned}
@@
 
-## Model 3: Normal Regression + Repeated Measures
+## 3.3 Model 3: Normal Regression + Repeated Measures
 
@@
 Similar to model 1, model 3 allows us to capture differences in `ChinaVirusInterest` with the $\theta_i$ value which represents each state's mean value.
-### Model Structure
+
+### 3.3a Model Structure
 
@@
 
-## Model 4: Longitudinal Model (state-specific slopes)
+## 3.4 Model 4: Longitudinal Model (state-specific slopes)
 
@@
 
-### Model Structure
+### 3.4a Model Structure
 
@@
 
-##mcmc plots
-```{r}
+### 4.1a MCMC Plots
+```{r, echo=FALSE, warning=FALSE}
 mcmc_trace(RM_model, pars = c("(Intercept)","Sigma[State:(Intercept),(Intercept)]"))
@@
 
-##ppcheck
+### 4.1b Posterior Predictive Check
 
-```{r}
+```{r, echo=FALSE, warning=FALSE}
 pp_check(RM_model, nreps=50)
@@
 
-##mcmc plots
+### 4.2a MCMC Plots
 
@@
 
-##ppcheck
+### 4.2b Posterior Predictive Check
 
-```{r}
+```{r, echo=FALSE, warning=FALSE}
 pp_check(NR_model, nreps = 50)
@@
 
-```{r}
+### 4.3a MCMC Plots
+```{r, echo=FALSE, warning=FALSE}
 mcmc_trace(model_3, pars=c("(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[(Intercept) State:AK]","b[(Intercept) State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
@@
 
-##ppcheck
-```{r}
+### 4.3b Posterior Predictive Check 
+```{r, echo=FALSE, warning=FALSE}
 pp_check(model_3, nreps=50)
@@
 As seen in our prior posterior predictive checks, they have similar errors around the tails. But it seems that our GLM structure is also reasonable for this model.
+
 ## 4.4 Model 4 Evaluation (Longitudinal)
 
-##mcmc plots
+### 4.4a MCMC Plots
 
-```{r}
+```{r, echo=FALSE, warning=FALSE}
 # Trace plots
@@
 
-##ppcheck
+### 4.4b Posterior Predictive Check
 
-```{r}
+```{r, echo=FALSE, warning=FALSE}
 pp_check(complexmod, nreps = 50)
@@
 
-## Are our models strong?: Prediction & classification summaries
+## 4.5 Are our models strong?: Prediction & classification summaries
 
@@
 
+### 5.1a 
 ```{r, message=FALSE, include=FALSE}
@@
 
+### 5.1b
 ```{r, message=FALSE, include=FALSE}
@@
 
+### 5.1c
 ```{r, message=FALSE, include=FALSE}
@@
 
+### 5.1d
 ```{r message=FALSE, include=FALSE}
@@
 
-### 5.1.a Table
+### 5.2 Table
 
-```{r}
+```{r, echo=FALSE, warning=FALSE}
 all_summ<-rbind(sum1,sum2,sum3,sum4)
@@
 
-### Why we chose Model 3 as our best model?
+### 5.2a Model 3 is the best
 
@@
 
-## 5.2 Posterior Prediction One State
+## 5.3 Posterior Prediction One State
 
-```{r}
+### 5.3a
+```{r, echo=FALSE, warning=FALSE}
 ### For predicting one case 
@@
 
-```{r}
+### 5.3b
+```{r, echo=FALSE, warning=FALSE}
 ### For predicting one case 
@@
 
-```{r}
+###5.3c
+```{r, echo=FALSE, warning=FALSE}
 ### For predicting one case 
@@
 
-```{r}
+### 5.3d
+```{r, echo=FALSE, warning=FALSE}
 ### For predicting one case 
@@
 
-```{r}
+### 5.3e
+```{r, echo=FALSE, warning=FALSE}
 actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
@@
 
-# 7. Acknowledgments and References
+# 7. Acknowledgments
+
+# 8. References
+Devlin, K., Silver, L., Huang, C.
+(2020).
+Amid Coronavirus Outbreak, Americans' Views of China Increasingly Negative.
+Retrieved 5 May 2020, from https://www.pewresearch.org/global/2020/04/21/u-s-views-of-china-increasingly-negative-amid-coronavirus-outbreak/
+
+Google Trends. (2020). Retrieved 5 May 2020, from https://trends.google.com/trends/explore?geo=US&q=china%20virus
+
+Jeung, R.
+Nham, K.
+(2020).
+STOP AAPI HATE MONTHLY REPORT 4/23/20.
+Retrieved 5 May 2020, from http://www.asianpacificpolicyandplanningcouncil.org/wp-content/uploads/STOP_AAPI_HATE_MONTHLY_REPORT_4_23_20.pdf
+
+Olson, H.
+(2020).
+Trump’s not the only one blaming China.
+Americans increasingly are, too.
+Retrieved 5 May 2020, from https://www.washingtonpost.com/opinions/2020/05/04/get-ready-an-election-all-about-china/
+
+Tavernise, S.
+Oppel Jr, R.
+(2020).
+Spit On, Yelled At, Attacked: Chinese-Americans Fear for Their Safety.
+Retrieved 5 May 2020, from https://www.nytimes.com/2020/03/23/us/chinese-coronavirus-racist-attacks.html

### 2020-05-05 Final-Draft.Rmd

@@
 ## 6.1 Limitations
+
+Truncated Normal Model** (0-100), really wide guesses.
 

### 2020-05-05 Final-Draft.Rmd
adding visuals

@@
 ---
-title: "Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics "
+title: "He Said What Now?!: Predicting Interest in the Term *China Virus* by State"
 author: "Federico Chung, Will Madairy, Sofia Pozsonyiova, Quinn Rafferty"
@@
     toc_float: true
+    code_folding: hide
 ---
@@
 
-## 2.3 Visualizations _NEED TO WEAVE A COHEASIVE MESSAGE BETWEEN THESE VISUALIZATIONS TO TELL A STORY _
+## 2.3 Visualizations
+
+The purpose of the visualizations below is to aid us in deepening our understanding of how our variables of interest intereact with one another and how they are structured.
+We chose to investigate the variables that are listed above because in our background reserach, we found that these factors on their own have proven to indicate some kind of infleucne on our outcome variable, interest in the term "China Virus." With our new combined datasets, we hope to see that our intuition, background reserach and the data align with one another to tell an interesting narrative.
+Further, we have broken these visualizations into the categories of demographics, Google interest in China Virus, and COVID-19 statistics since those were the themes that repeatdly appeared in our resreach and disucussions.
 
@@
     z = ~ChinaVirusInterest, text = ~hover, locations = ~State,
-    color = ~ChinaVirusInterest, colors = 'Oranges'
+    color = ~ChinaVirusInterest, colors = 'RdGy'
   )
-fig <- fig %>% colorbar(title = "Interest")
+
+fig <- fig %>% colorbar(title = "Level of Interest") 
 fig <- fig %>% layout(
@@
   )
+fig
+```
 
+This visualization aims to establish our understnading of what our outcome variable looks like in our data across the United States.
+It also provides information on the distribution and geographical patterns of several variables of interest (hover for additional information).
+As we can see, the Google interest in the term "China Virus" is highly varibale across all states.
+The states that are on the higher end of the scale are: Louisianna, Florida, Oklahoma, Michigan, Arizona, Nebraska, and Alaska.
+At first glance, this implies that predicting interest in "China Virus" by region would probably be ineffective.
+
+```{r, echo=FALSE, warning=FALSE, fig.align=center}
 #########white fig
@@
   )
-
-fig
 subplot(whitefig,asianfig)
-
 ```

### 2020-05-05 Final-Draft.Rmd
finishing visuals and introduction

@@
 We chose to investigate the variables that are listed above because in our background reserach, we found that these factors on their own have proven to indicate some kind of infleucne on our outcome variable, interest in the term "China Virus." With our new combined datasets, we hope to see that our intuition, background reserach and the data align with one another to tell an interesting narrative.
-Further, we have broken these visualizations into the categories of demographics, Google interest in China Virus, and COVID-19 statistics since those were the themes that repeatdly appeared in our resreach and disucussions.
 
-### 2.3a Demographic
-
+### Figure 1
 ```{r, echo=FALSE, warning=FALSE, fig.align=center}
@@
     z = ~ChinaVirusInterest, text = ~hover, locations = ~State,
-    color = ~ChinaVirusInterest, colors = 'RdGy'
+    color = ~ChinaVirusInterest, colors = 'OrRd'
   )
@@
 fig <- fig %>% colorbar(title = "Level of Interest") 
-fig <- fig %>% layout(
+fig <- fig %>% layout(      # put legend in center of x-axis
     title = '2020 Google Search Interest of "China Virus" by State <br>(Hover for additional information)', geo=g
   )
+
 fig
@@
 The states that are on the higher end of the scale are: Louisianna, Florida, Oklahoma, Michigan, Arizona, Nebraska, and Alaska.
-At first glance, this implies that predicting interest in "China Virus" by region would probably be ineffective.
+This implies that predicting interest in "China Virus" by region would most likely be ineffective.Additionally, the majority of these high interest states have a large number of positive reported cases.
+This is an interesting obesrvation given that reporting of positive cases differs across states and may be influencing the general public differently by state.
+Moreover, the majority of the high interest states are also designated as "red" with the exception of Michigan which is "blue." This indcates that the variable State Color may be one of the most effective predictors for our models.
+This visual includes information on white and asian percentages by state but Figure 2 provides a more informative depiction of the geographic distribution.
 
+### Figure 2
 ```{r, echo=FALSE, warning=FALSE, fig.align=center}
@@
 whitefig <- whitefig %>% layout(
-    title = 'Percent White Identifying by State', geo=g
-  )
+    title = 'Percent White Identifying by State', geo=g,legend = list(orientation = "h",   # show entries horizontally
+                     xanchor = "center",  # use center of legend as anchor
+                     x = 0.5))             # put legend in center of x-axis
 
@@
 asianfig <- asianfig %>% layout(
-    title = 'Comparison of Percent Asian and White Identifying by State',geo=g
-  )
+    title = 'Comparison of Percent Asian and White Identifying by State',geo=g, 
+    legend = list(orientation = "h",   # show entries horizontally
+                     xanchor = "center",  # use center of legend as anchor
+                     x = 0.5))             # put legend in center of x-axis
+
 subplot(whitefig,asianfig)
 ```
+With this visual we hope to illuminate what the dispersion of white identifying and asian identifying indivudals looks like by state.
+Our background reserach supports the idea that anti-Asian sentiment may occur more in places where there is a low proportion of Asian-Americans.
+However, this comparison of percentages highlights that the Asian population across the entire US is pretty low.
+This suggests that including `percent_asian` in our model will most likley be ineffective thus, it may be more informative to include `percent_white` as an indicator of diversity.
+While it sounds counter-intuitive the idea would be that the lower the `percent_white` is by state means that there is a higher percentage of non-white identifying individuals.
+Thus, this variable may prove influential in our models.
 
-Our first visualization is looking at the percent of residents that identify as white within the United States compared to those whom identify as asian.
-As you can see, there is a higher percent of white identifying residents overall but most specifically in the Midwest and northeast states.
-In regards to Asian-Americans, there is practically less than .1% per state with the exception of California and New York.
-From this visualization we can also see that places like Texas, California, and New Mexico have much lower white identifying residents which could provide important information for us in our actual analysis.
-
-### 2.3b Google China Virus
+#### Figure 3
 
@@
   #filter(Day>=day1)%>%
-  group_by(Region, Day) %>% 
-  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
-  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
-  geom_point()+ geom_line()
+  group_by(StateColor, Day) %>% 
+  summarize(ChinaVirusSearch = mean(ChinaVirusInterest)) %>% 
+  ggplot(aes(x=Day, y=ChinaVirusSearch, color=StateColor)) +
+  geom_point()+ geom_line() + labs(x = " Date", y = "China Virus Interest", title = " China Virus Interest by Day and State Color") +theme_minimal()
 
@@
 
-This plot shows the relationship of “China Virus” search interest over grouped by region.
-This plots shows that there are certainly key events that trigger an uptick in searches overall.
-In this plot it is not clear which region may search China Virus more or less often, but it does show a that the regions move together in search interest, which would imply federal level events like a Donald Trump tweet to trigger these interest spikes.
+This plot shows the relationship of “China Virus” search interest over our time period of interest grouped by State Color.
+For each State Color, we can see an overall increasing interest in the term "China Virus" but especially among the Democratic and Swing states.
+While this seems contradictory to our intuition this pattern can be explained by the  the complicated nature of US poltics.
+We dug deeper into why this pattern would occur and found that Democrats tend to take more initiative in researching terms they have heard on the news, especially from the White House COVID-19 briefings, over Republicans.
+So while interest in the term China Virus is more popular in blue states, the intentions may be different than Red states.
+This finding is very important to note because when we include State Color in our models, we have to be wary on how we interpret the coefficients associated with Red, Blue and Purple.
+
+### Figure 4
 
@@
 b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
-  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State") + labs(fill="State")
+  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State") + labs(fill="State", x = "Interest in China Virus", y = "Density")
 
@@
 
-As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relatively normal with a small bump at 0.
-As a group we believe this bump occurs as 0 is the lowest value it can take and because of that limitation of the China Virus Interest we see a small bump around 0.
-One could argue against a normal distribution as it kinda looks a bit right skewed.
-But our team believes that a normal distribution is the best at describing the density.
-
-We can see that the variability in Google interest in the term China Virus is has quite a large range between states.
+Figure 4 aims to address the question: What structure does intrest in the "China Virus" look like and what is its variance look like too?
+As we can see, the majority of states behave relatively normal with a small bump at 0.
+One could argue against a normal distribution as some states like Deleware,Texas, Washington and Alabama look a bit right skewed but overall a normal distribution is the best at describing these densities as a whole.
+Additionally, we can see that the variability in Google interest in the term China Virus is has quite a large range between states.
 There are very few states that have high densities among the upper echelons of the interest scale but there are some interesting peaks of densities among the lower values.
@@
 It is is also interesting interesting to note that there isn't an *obvious* mean or median value of China Virus interest among the states.
+Again, this prompts more questions about the characteristics of the states themeselves.
+While this shows us that a Normal Regression model may suffice we still explored the possibility of varying slopes among states below.
 
+### Figure 5
 ```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
@@
     theme(legend.position = "none") +
-    facet_wrap(~State)
+    facet_wrap(~State)+ 
+    labs(title="Slopes of China Virus Interest by State and Date", x= "Date", y="China Virus Interest")
 
@@
 
-### 2.3c COVID-19
-
-```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
-c <-  ggplot(Finaldata, aes(y=positive, x=Winner, fill=(Winner)))+
-      geom_boxplot() +
-      facet_wrap(~Region)+
-      theme(legend.position = "none") +
-      scale_fill_manual(values = c("Democrat"="blue3", "Republican"= "red3"))+
-      lims(y= c(0,1000))+
-      ggtitle("Positive COVID-19 Cases by State Political Party Winner & Region")
-ggplotly(c)
-```
-
-This visualisation depicts the distribution of positive COVID-19 cases by region and by which political party won in the 2016 elections.
-We can see that Democrat states in the Midwest, Mountain, and West have a larger range and higher quantile metrics for positive cases overall.
-For the Northeast and South regions the mean of positive COVID-19 cases are higher but not significantly.
-This is an interesting pattern considering that poltical party affiliation appears to interact with the number of postive cases by region.
+Figure 5 helps inform us on what level of complexity our model may need to be.
+We originally visualized all 50 states slopes but for the purposes of this report, it is more effective to observe a select few.
+As we can see states like Iowa and Missouri have a negative slope which indicates that the rate of their interst in the term China Virus decreases over time.
+However states like Louisianna, Maryland, Michigan and Mississippi have upward slopes which indcates the opposite of Iowa and Missouri.
+Then there are the states that have a relatively flat slope which means rate of interest neither increases or decreases overtime.
+Thus, these plots tell us that we will want to explore a longitudinal model because states do seem to have varying rates of interest however, it may not be entirely necessary because the slopes do not seem to varying drastically in steepness.
 
@@
 
-# 3. Methods & Models (Feddy and Will)
+# 3. Methods & Models
 
@@
 
-# 4. Model Evaluation (RESULTS)
+# 4. Model Evaluation
 
@@
 
-# 5. Results (Will)
+# 5. Results
 
@@
 
-###5.3c
+### 5.3c
 ```{r, echo=FALSE, warning=FALSE}

### 2020-05-05 Final-Draft.Rmd
knitting doc

@@
 ### Figure 1
-```{r, echo=FALSE, warning=FALSE, fig.align=center}
+```{r, echo=FALSE, warning=FALSE, fig.align="center"}
 Finaldata$hover <- with(Finaldata, paste(polyname, "<br>","Positive Cases:", positive, "<br>","Negative Cases:", negative,"<br>",
@@
 ### Figure 2
-```{r, echo=FALSE, warning=FALSE, fig.align=center}
+```{r, echo=FALSE, warning=FALSE, fig.align="center"}
 #########white fig
@@
 
-#### Figure 3
+### Figure 3
 
@@
 
-```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
+```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= "center"}
 
@@
 
-```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
+```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= "center"}
 b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
@@
 ### Figure 5
-```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
+```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= "center"}
 IAtoMT <- Finaldata %>% select(c(State,ChinaVirusInterest,Day)) %>% filter (State %in% c("IA","ID","IL","LA","MA","MD","ME","MI","MN","MO","MS","MT"))
@@
 ```
+
 Compared to the previous model, it looks that our chains are more stable and they have closer peaks.
@@
 ```
+
 As seen in our prior posterior predictive checks, they have similar errors around the tails. But it seems that our GLM structure is also reasonable for this model.
@@
 ```
+
 Overall all ppchecks tend to have the similar graph because we are assuming a normal relationship on the response variable for all of them.

### 2020-05-06 Final-Draft.Rmd
Summary

@@
 library(usmap)
+library(readr)
 library(maps)
@@
 Moreover, not only can their words change the public's views on a health matter but it can also shift a nation's perspective on someone's identity.
-The Asian Pacific Policy and Planning Council reported that in their first four weeks of receiving reports on COVID-19 anti-Asian discirimnation, they recieved more than 1,500 incidents (Jeung & Nham 2020).
+The Asian Pacific Policy and Planning Council reported that in their first four weeks of receiving reports on COVID-19 anti-Asian discrimination, they received more than 1,500 incidents (Jeung & Nham 2020).
 This abrupt spasm of racism mimics the kind faced by American Muslims, Arabs and South Asians in the United States after the terrorist attacks of 9/11 (Tavernise & Oppel Jr, 2020).
@@
 
-In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identities and states.The Pew Reserach Center discovered that nearly three-quarters of Repbulicans and Republican-leaning indepdents view China unfavoriably (Devlin, et al 2020.
+In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identities and states.The Pew Research Center discovered that nearly three-quarters of Republicans and Republican-leaning independents view China unfavorably (Devlin, et al 2020.
 But the majority of reports to the AAPI were from Democrat leaning states like California, Washington and Illinois [Jeung & Nham 2020].
 Moreover, states that have a higher number of reported positive cases tend to have a higher interest in Googling the term "China Virus" (2020).
-Thus, this begs the question: What factors of the poltiical, demographic and COVID-19 spheres best predicts the level of interest a state will have in the term "China Virus?"
+Thus, this begs the question: What factors of the political, demographic and COVID-19 spheres best predicts the level of interest a state will have in the term "China Virus"?
 
@@
 This model proved to provide the best balance between complexity and quality.Model 3 captures important attributes that the normal model and repeated measures did not and it achieves similar results to our complex model, Model 4, without the heavy computational toll.
-Overall, we hope this project inspires others to explore the intereconnectdness of health, communication, politics and demography.
+Overall, we hope this project inspires others to explore the interconnectedness of health, communication, politics and demography.
 
@@
 
+Given the complexity of our research question and the limited data on COVID-19, we resorted to creating our own dataset.
+This was done by combining multiple existing datasets from various sources that touch on different political, demographic, and COVID-19 characteristics on the state level.
+Our demographic dataset was created using data from the US Census Bureau’s American Community Survey (ACS) which is an ongoing survey administered by the U.S.
+Census Bureau.
+It  gathers information on income, employment, housing characteristics, etc, annually for all the 50 U.S.
+States on the county and state level.
+The ACS dataset was then merged with a 2016 county level election outcomes dataset that was scraped from Townhall.com and Alicia Johnson’s state political leaning set which categorizes each county as belonging to a blue/red/purple state based on the state categorizations at 279towin.
+The final merged dataset was then then transformed to be on the state level and provided us with our state-level political and demographic characteristics.
+Google Trends data was used to measure people's interest in the term "China Virus" over time.
+The data was directly downloaded from the platform, for our chosen time frame of 2020-03-14 - 2020-03-21.
+Lastly, the COVID-19 data is provided by The COVID Tracking Project(CTP) which is updated regularly.
+The data points come directly from state/district/territory public health authorities—or, occasionally, from trusted news reporting, official press conferences, or from tweets or Facebook updates from state public health authorities or governors.
+Together these datasets allowed us to be able to tackle our question of interest.
+Together these datasets allowed us to be able to analyze which factors of the political, demographic and COVID-19 spheres best predict the level of interest a state will have in the term "China Virus.
+
 ## 2.2 Variables of interest
-+------------------------+---------------------------------------------------+
-| Variables:             | Description:                                      |
-+========================+===================================================+
-| `State`                | State abbreivation and main identifier            |
-+------------------------+---------------------------------------------------+
-| `StateColor`           | Political Leaning of the state. Either red, blue  |
-|                        | or purple.                                        |
-+------------------------+---------------------------------------------------+
-| `percent_white`        | Percent of the Population that is White           |
-+------------------------+---------------------------------------------------+
-| `percent_asian`        | Percent of the Population that is Asian           |  
-+------------------------+---------------------------------------------------+
-|`Positive`              | Number of reported positive COVID-19 cases        | 
-+------------------------+---------------------------------------------------+
-|`Negative`              | Number of reported negative COVID-19 cases        | 
-+------------------------+---------------------------------------------------+
-|`Day`                   | Date of report                                    | 
-+------------------------+---------------------------------------------------+
-|`totalTestResults`      | Total Number test results (Positive +Negative)    | 
-+------------------------+---------------------------------------------------+
-|`ChinaVirusInterest`    | Interest index from Google searches by state.     |
-|                        | Peak search day=100, all other days in set are    |
-|                        | based searches on relative to this peak day.      | 
-+------------------------+---------------------------------------------------+
-|`Region`                | States divided into five different regions:       |
-|                        | West, South, Mountain, Northeast, Midwest         |
-+------------------------+---------------------------------------------------+
++------------------------+---------------------------------------------------+-----------------+
+| Variables:             | Description:                                      | Category:       | 
++========================+===================================================+=================+
+| `State`                | State abbreviation and main identifier            | Demographic     |
++------------------------+---------------------------------------------------+-----------------+
+|`Region`                | States divided into five different regions:       | Demographic     |
+|                        | West, South, Mountain, Northeast, Midwest         |                 |
++------------------------+---------------------------------------------------+-----------------+
+| `percent_white`        | Percent of the Population that is White           | Demographic     | 
++------------------------+---------------------------------------------------+-----------------+
+| `percent_asian`        | Percent of the Population that is Asian           | Demographic     | 
++------------------------+---------------------------------------------------+-----------------+
+| `StateColor`           | Political Leaning of the state. Either red, blue  | Political       | 
+|                        | or purple.                                        |                 |
++------------------------+---------------------------------------------------+-----------------+
+| `ChinaVirusInterest`   | Interest index from Google searches by state.     | Interest        |
+|                        | Peak search day=100, all other days in set are    |                 |
+|                        | based searches on relative to this peak day.      |                 |
++------------------------+---------------------------------------------------+-----------------+
+| `Positive`             | Number of reported positive COVID-19 cases        | COVID-19        |
++------------------------+---------------------------------------------------+-----------------+
+| `Negative`             | Number of reported negative COVID-19 cases        | COVID-19        |
++------------------------+---------------------------------------------------+-----------------+
+| `Day`                  | Date of report                                    | COVID-19        |
++------------------------+---------------------------------------------------+-----------------+
+| `totalTestResults`     | Total Number test results (Positive + Negative)   | COVID-19        |
++------------------------+---------------------------------------------------+-----------------+
+
+For our variable selection process we initially grouped each variable to be either relating to Demographic, Political, COVID-19, or "Interest" characteristics.
+From there we chose the most robust variable out of each category, and used it to create our final models.
+This process resulted in a final dataset containing over 400 observations and 10 out of the original 34 different variables.
 
@@
 
-The purpose of the visualizations below is to aid us in deepening our understanding of how our variables of interest intereact with one another and how they are structured.
-We chose to investigate the variables that are listed above because in our background reserach, we found that these factors on their own have proven to indicate some kind of infleucne on our outcome variable, interest in the term "China Virus." With our new combined datasets, we hope to see that our intuition, background reserach and the data align with one another to tell an interesting narrative.
+The purpose of the visualizations below is to aid us in deepening our understanding of how our variables of interest interact with one another and how they are structured.
+We chose to investigate the variables that are listed above because in our background research, we found that these factors on their own have proven to indicate some kind of influence on our outcome variable, interest in the term "China Virus." With our new combined datasets, we hope to see that our intuition, background research and the data align with one another to tell an interesting narrative.
 
@@
 
-This visualization aims to establish our understnading of what our outcome variable looks like in our data across the United States.
+This visualization aims to establish our understanding of what our outcome variable looks like in our data across the United States.
 It also provides information on the distribution and geographical patterns of several variables of interest (hover for additional information).
-As we can see, the Google interest in the term "China Virus" is highly varibale across all states.
-The states that are on the higher end of the scale are: Louisianna, Florida, Oklahoma, Michigan, Arizona, Nebraska, and Alaska.
+As we can see, the Google interest in the term "China Virus" is highly variable across all states.
+The states that are on the higher end of the scale are: Louisiana, Florida, Oklahoma, Michigan, Arizona, Nebraska, and Alaska.
 This implies that predicting interest in "China Virus" by region would most likely be ineffective.Additionally, the majority of these high interest states have a large number of positive reported cases.
-This is an interesting obesrvation given that reporting of positive cases differs across states and may be influencing the general public differently by state.
-Moreover, the majority of the high interest states are also designated as "red" with the exception of Michigan which is "blue." This indcates that the variable State Color may be one of the most effective predictors for our models.
-This visual includes information on white and asian percentages by state but Figure 2 provides a more informative depiction of the geographic distribution.
+This is an interesting observation given that reporting of positive cases differs across states and may be influencing the general public differently by state.
+Moreover, the majority of the high interest states are also designated as "red" with the exception of Michigan which is "blue." This indicates that the variable State Color may be one of the most effective predictors for our models.
+This visual includes information on white and Asian percentages by state but Figure 2 provides a more informative depiction of the geographic distribution.
 
@@
 ```
-With this visual we hope to illuminate what the dispersion of white identifying and asian identifying indivudals looks like by state.
-Our background reserach supports the idea that anti-Asian sentiment may occur more in places where there is a low proportion of Asian-Americans.
+With this visual we hope to illuminate what the dispersion of white identifying and Asian identifying individuals looks like by state.
+Our background research supports the idea that anti-Asian sentiment may occur more in places where there is a low proportion of Asian-Americans.
 However, this comparison of percentages highlights that the Asian population across the entire US is pretty low.
-This suggests that including `percent_asian` in our model will most likley be ineffective thus, it may be more informative to include `percent_white` as an indicator of diversity.
+This suggests that including `percent_asian` in our model will most likely be ineffective thus, it may be more informative to include `percent_white` as an indicator of diversity.
 While it sounds counter-intuitive the idea would be that the lower the `percent_white` is by state means that there is a higher percentage of non-white identifying individuals.
@@
   ggplot(aes(x=Day, y=ChinaVirusSearch, color=StateColor)) +
-  geom_point()+ geom_line() + labs(x = " Date", y = "China Virus Interest", title = " China Virus Interest by Day and State Color") +theme_minimal()
+  geom_point()+ geom_line() + labs(x = " Date", y = "China Virus Interest", title = " China Virus Interest by Day and State Color") + scale_color_manual(values=c("blue", "purple", "red")) +theme_minimal()
 
@@
 For each State Color, we can see an overall increasing interest in the term "China Virus" but especially among the Democratic and Swing states.
-While this seems contradictory to our intuition this pattern can be explained by the  the complicated nature of US poltics.
+While this seems contradictory to our intuition this pattern can be explained by the  the complicated nature of US politics.
 We dug deeper into why this pattern would occur and found that Democrats tend to take more initiative in researching terms they have heard on the news, especially from the White House COVID-19 briefings, over Republicans.
@@
 
-Figure 4 aims to address the question: What structure does intrest in the "China Virus" look like and what is its variance look like too?
+Figure 4 aims to address the question: What structure does interest in the "China Virus" look like and what is its variance look like too?
 As we can see, the majority of states behave relatively normal with a small bump at 0.
-One could argue against a normal distribution as some states like Deleware,Texas, Washington and Alabama look a bit right skewed but overall a normal distribution is the best at describing these densities as a whole.
+One could argue against a normal distribution as some states like Delaware,Texas, Washington and Alabama look a bit right skewed but overall a normal distribution is the best at describing these densities as a whole.
 Additionally, we can see that the variability in Google interest in the term China Virus is has quite a large range between states.
@@
 It is is also interesting interesting to note that there isn't an *obvious* mean or median value of China Virus interest among the states.
-Again, this prompts more questions about the characteristics of the states themeselves.
+Again, this prompts more questions about the characteristics of the states themselves.
 While this shows us that a Normal Regression model may suffice we still explored the possibility of varying slopes among states below.
@@
 We originally visualized all 50 states slopes but for the purposes of this report, it is more effective to observe a select few.
-As we can see states like Iowa and Missouri have a negative slope which indicates that the rate of their interst in the term China Virus decreases over time.
-However states like Louisianna, Maryland, Michigan and Mississippi have upward slopes which indcates the opposite of Iowa and Missouri.
+As we can see states like Iowa and Missouri have a negative slope which indicates that the rate of their interest in the term China Virus decreases over time.
+However states like Louisiana, Maryland, Michigan and Mississippi have upward slopes which indicates the opposite of Iowa and Missouri.
 Then there are the states that have a relatively flat slope which means rate of interest neither increases or decreases overtime.
@@
  We decided that our MCMC model should take in values from a normal distribution because ChinaVirusInterest's distribution is fairly normal.
-Although the tails are not as flat as we would want them to be, we can decided that a normal distribution was best to model ChinaVirusInterest.
+Meaning that most of the observations cluster around a central peak and then values further away taper off somewhat equally in both directions.
+Even though the tails are not as flat as we would want them, we decided a normal distribution was still the best fit to model ChinaVirusInterest.
 
@@
 For our second model, we decided that we wanted to understand what made some states more responsive to ChinaVirusInterest than others.
-As you saw in our research motivation section, we wanted to explore what explained the differences in interest for the “China Virus” term.
-Was it a political difference, a demographic or a covid-impact related difference?
+As you saw in our research motivation section, we wanted to explore what explained the differences in interest for the “China Virus” term: Was it a political difference, a demographic or a covid-impact related difference?
 To do this we used a simple Normal Regression model with the following specifications.
@@
 ### 3.2a Model Structure
+
 $$\begin{aligned}
@@
 
-For our third model, we decided to combine the first two models to first understand variations in political, demographic, covid-related variables and also be able to capture variation that we could not explain in model 2.
+For our third model, we decided to combine the first two models to be able to understand variations in political, demographic, covid-related variables and to also be able to capture variation that we could not explain in model 2.
 Additionally, we kept the correlation structure that we saw in model 1, but we included the variables in model 2 so that we could explain why some states had a larger `ChinaVirusInterest` than others.
@@
 
+### 4.1a MCMC Plots
+```{r, echo=FALSE, warning=FALSE}
+mcmc_trace(RM_model, pars = c("(Intercept)","Sigma[State:(Intercept),(Intercept)]"))
+mcmc_dens_overlay(RM_model, pars = c("(Intercept)","Sigma[State:(Intercept),(Intercept)]")) 
+```
+
+By looking at the mcmc trace plot and density overlay we see that our MCMC chains are fairly stable.
+However, looking at the density overlay we can see it could do with a bit more stability as the peaks for our Intercept become more spread out around the 40-42.5 range.
+From the above plots, we also see that our value of $\sigma_b^2$ is greater than 0.
+Our value of sigma is around 75 meaning that we must include random intercepts in our final model
+
 ```{r, message=FALSE, include=FALSE}
@@
 
-In the output above we see that the within deviation is much narrow than the between deviation.
-This matches our intuition in the model that utilizing the repeated measures, fixed effects model will be able to explain a greater amount of the variation.
+In the output above we see that the within deviation is much more narrow than the between deviation.
+This matches our intuition in the model that utilizing the repeated measures fixed effects model will be able to explain a greater amount of the variation.
 
@@
 This correlation table shows us that there is relatively weak correlation within each given daily observation within a state.
-Although there is not a strong correlation, it is correct for us to utilize a repeated measuress model in order to account for the correlation within states.
-
-### 4.1a MCMC Plots
-```{r, echo=FALSE, warning=FALSE}
-mcmc_trace(RM_model, pars = c("(Intercept)","Sigma[State:(Intercept),(Intercept)]"))
-mcmc_dens_overlay(RM_model, pars = c("(Intercept)","Sigma[State:(Intercept),(Intercept)]")) 
-```
-
-As we can see in this mcmc trace plot, it looks like our MCMC is fairly stable but could do with a bit more stability as we see that the peaks are spread around the 40-42.5 range.
-We also see that our values for $\sigma_b^2$ is greater than 0, our value of sigma is around 75 meaning that we must include random intercepts in our final model
+Although there is not a strong correlation, it is correct for us to utilize a repeated measures model in order to account for the correlation within states.
 
@@
 
-Overall, we can see that our repeated measures model it tells us that the structure of our model is fairly reasonable, In other words, the assumption of using a normal model is fairly reasonable outside of the fact that the tails are a bit thicker than we would want them to be.
+Overall, we can see that our repeated measures model tells us that the structure of our model is fairly reasonable.
+In other words, the assumption of using a normal model is fairly reasonable outside of the fact that the tails are a bit thicker than we would want them to be.
 This is because we are expecting a lot of states that will have multiple days with zero value, if no one in the state looks up the term.
@@
 
-Compared to the previous model, it looks that our chains are more stable and they have closer peaks.
+For this mcmc overlay and trace plot, we looked at our sigma and intercept along with our predictor values. Compared to model 1, it looks that our chains are more stable and they have closer peaks.
 
@@
 
-Although our posterior predictive check is pretty similar to our previous model, we see that the peaks are a bit more closer together.
-And similar to the previous model the structure of the GLM is fairly reasonable.
+Although our posterior predictive check is pretty similar to our previous model, we see that the peaks are a bit more closer together, and similar to the previous model the structure of the GLM is fairly reasonable.
 
@@
 
-Compared to the previous model, we see that our chains are more stable for the intercept and the percent_white variables as the peaks are closer together.
+Compared to our previous model, we see that our chains are more stable for the intercept and the percent_white variable as the peaks are closer together.
 We also see that our $\sigma_b^2$ is almost always above 0, and the density has a mean around 75 similar to our repeated measures model.
@@
 As we can see in the table above, the lowest mae was achieved by our most complex model, Model 4 which allowed for both random slopes and random intercepts.
-But the mae value is not that different from the mae acchieved by Model 3 which was more simple allowing only for random intercepts.
+But the mae value is not that different from the mae achieved by Model 3 which was more simple allowing only for random intercepts.
 Interestingly Model 1 our simplest model had a higher proportion of the data falling within the 95% posterior predictive interval.
@@
 
-We believe that the decreases in mae and increases of the proporiton of values observed within 50% of the posterior predictive interval do not justify increasing the complexity.
-Which is why we argue that Model 3 is the best model because it acchieves similar results to model 4 without making it computationally expensive.
+We believe that the decreases in mae and increases of the proportion of values observed within 50% of the posterior predictive interval do not justify increasing the complexity.
+Which is why we argue that Model 3 is the best model because it achieves similar results to model 4 without making it computationally expensive.
 But if we want a more precise model we would use Model 4.
@@
 ### For predicting one case 
-new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) #Doesn't recognize state
+new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) 
 set.seed(454)
@@
 ```
+
+After creating predictions for all the states, we wanted to focus on just one state.
+That said, we looked at Florida and created future "China Virus" interest predictions for it using each of our models.
+Our first model, predicts "'China Virus" interest for Florida on Day 7, with the positive rate being 11% and assumes the percentage of white residents is to be 5%.
+Model 1 predicts the mean interest to be 45.27%, however, as one could see from the above visualization the interest could vary greatly, but there is a higher chance for it to be between 20% - 80%.
 
@@
 ```
+Model 2 looks at Florida on day 7, with the number of positive cases being 658 with the percentage of white residents being 5%.
+Model 2 predicts the mean interest to be 46.95% which is a lot better than model 1.
+However, the interest could vary greatly, and the space under the curve is much more condescended to the mean.
 
@@
 ```
+Model 3 looks at Florida on day 7, with the number of positive cases being 658 with the percentage of white residents being 5%, and also classifies Florida as a purple state.
+Model 3 predicts the mean interest to be 50.04%.
+For this model we see that the peak is around that 50%, but the range can vary from 0 to 100%.
 
@@
 complex<-summary(pred_FL_complex)
+complex
 ```
+Our final model predicts the same aspects as model 3.
+Our model predicted "China Virus" interest to be 53.16, which is a lot higher than our other models.
+Also, we see that the area under the curve is a lot more spread out as well.
 
@@
 ```
+The actual mean of interest in the term China Virus in Florida is 47.625! We can use this value to assess how closely our models predicted the interest to be.
 
@@
 
-Truncated Normal Model** (0-100), really wide guesses.
+Our data itself brings about a couple of limitations:
+
+COVID-19 Dataset: 
+One of the biggest weakness of this dataset is the fact there there is no designed standardized method for states to follow for data collection and reporting.
+For example, some states, like Oregon, provide the full set of numbers but others provide some or none of these numbers on an ongoing basis.
+Some crucial states in this outbreak, notably California, Washington, and New York, have not been regularly reporting their total number of people tested.
+This is rather concerning as there could be important trends  that are not being captured due to the under and over reporting.
+
+Google Trends: 
+The main downside to the Google Trends dataset is the method of the indexing that the platform uses.
+Since each state is guaranteed to have a 100-level interest on their peak interest day the comparison from state to state becomes less meaningful.
+Additionally, the actual unknown search values can vary greatly across different states.
+
+Demographics & Political: 
+Overall, the demographics and political dataset is rather comprehensive and accurate.
+However, the biggest limitation arises with the State of Alaska.
+Since the State of Alaska reports results at the precinct or state level so there was no county-level data available and many datasets excluded the state.
+Therefore, demographic and election information for Alaska had to be manually entered.
+
+In addition to our data limitation, a couple of limitations arose with our final models.
+For our models we used a Normal distribution which goes from 0 - 100, however, our final distributions turn our to be rather truncated with values going above and below 0 and 100 this causes us to have wider guesses.
+Also, when running a ppcheck on each of our models we saw that our resulting distribution wasn't a perfect normal as there were two visible bumps on each of the tail ends.
+These bumps would need further exploring, however, we assume them to be outliers within our data.
 
 ## 6.2 Future Work
+
+The Google Trends platform provided us with some interesting findings, however, it doesn't tell us how people actually responded to the term "China Virus".
+Thus, it would be interesting to incorporate Twitter data into the analysis.
+Scrapping Twitter would allow us to analyze the actual emotional response to Trump's statement and incorporate a sentimental analysis.
+Additionally, in the future we hope to look at how the stay at home orders impacted "China Virus" interest as well.
 
@@
 # 7. Acknowledgments
+
+We thank Alicia Johnson for not only providing us an aspect of our final dataset but also for helping us throughout the entirety of the project.
 

### 2020-05-06 Final-Draft.Rmd
cleaning and running html

@@
 This model proved to provide the best balance between complexity and quality.Model 3 captures important attributes that the normal model and repeated measures did not and it achieves similar results to our complex model, Model 4, without the heavy computational toll.
-Overall, we hope this project inspires others to explore the interconnectedness of health, communication, politics and demography.
+Overall, we hope this project inspires others to explore the interconnection of health, communication, politics and demography.
 
@@
 
-Given the complexity of our research question and the limited data on COVID-19, we resorted to creating our own dataset.
-This was done by combining multiple existing datasets from various sources that touch on different political, demographic, and COVID-19 characteristics on the state level.
-Our demographic dataset was created using data from the US Census Bureau’s American Community Survey (ACS) which is an ongoing survey administered by the U.S.
+Given the complexity of our research question and the limited data on COVID-19, we resorted to creating our own data set.
+This was done by combining multiple existing data sets from various sources that touch on different political, demographic, and COVID-19 characteristics on the state level.
+Our demographic data set was created using data from the US Census Bureau’s American Community Survey (ACS) which is an ongoing survey administered by the U.S.
 Census Bureau.
@@
 States on the county and state level.
-The ACS dataset was then merged with a 2016 county level election outcomes dataset that was scraped from Townhall.com and Alicia Johnson’s state political leaning set which categorizes each county as belonging to a blue/red/purple state based on the state categorizations at 279towin.
-The final merged dataset was then then transformed to be on the state level and provided us with our state-level political and demographic characteristics.
+The ACS data set was then merged with a 2016 county level election outcomes data set that was scraped from Town hall.com and Alicia Johnson’s state political leaning set which categorizes each county as belonging to a blue/red/purple state based on the state categorizations at 279town.
+The final merged data set was then then transformed to be on the state level and provided us with our state-level political and demographic characteristics.
 Google Trends data was used to measure people's interest in the term "China Virus" over time.
@@
 The data points come directly from state/district/territory public health authorities—or, occasionally, from trusted news reporting, official press conferences, or from tweets or Facebook updates from state public health authorities or governors.
-Together these datasets allowed us to be able to tackle our question of interest.
-Together these datasets allowed us to be able to analyze which factors of the political, demographic and COVID-19 spheres best predict the level of interest a state will have in the term "China Virus.
+Together these data sets allowed us to be able to tackle our question of interest.
+Together these data sets allowed us to be able to analyze which factors of the political, demographic and COVID-19 spheres best predict the level of interest a state will have in the term "China Virus.
 
@@
 From there we chose the most robust variable out of each category, and used it to create our final models.
-This process resulted in a final dataset containing over 400 observations and 10 out of the original 34 different variables.
+This process resulted in a final data set containing over 400 observations and 10 out of the original 34 different variables.
 
@@
 The purpose of the visualizations below is to aid us in deepening our understanding of how our variables of interest interact with one another and how they are structured.
-We chose to investigate the variables that are listed above because in our background research, we found that these factors on their own have proven to indicate some kind of influence on our outcome variable, interest in the term "China Virus." With our new combined datasets, we hope to see that our intuition, background research and the data align with one another to tell an interesting narrative.
+We chose to investigate the variables that are listed above because in our background research, we found that these factors on their own have proven to indicate some kind of influence on our outcome variable, interest in the term "China Virus." With our new combined data sets, we hope to see that our intuition, background research and the data align with one another to tell an interesting narrative.
 
@@
 ```
+
 With this visual we hope to illuminate what the dispersion of white identifying and Asian identifying individuals looks like by state.
@@
 b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
-  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State") + labs(fill="State", x = "Interest in China Virus", y = "Density")
+  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State") + labs(fill="State", x = "Interest in China Virus", y = "Density") +theme_minimal()
 
@@
     facet_wrap(~State)+ 
-    labs(title="Slopes of China Virus Interest by State and Date", x= "Date", y="China Virus Interest")
+    labs(title="Slopes of China Virus Interest by State and Date", x= "Date", y="China Virus Interest")+
+    theme_minimal()
 
@@
 Our team decided that the repeated measures model was necessary component because of how our data is set up.
-As we can see in our dataset, each state has a value for their `ChinaVirusInterest` for each day in our target period (2020-03-14 - 2020-03-21).
+As we can see in our data set, each state has a value for their `ChinaVirusInterest` for each day in our target period (2020-03-14 - 2020-03-21).
 Given the ability to use repeated measures and our prior understanding of the varying characteristics (demographic,political,covid-impact) within different states, the repeated measures model allows us to capture these differences in `ChinaVirusInterest` with the $\theta_i$ value which represents each state's mean value.
@@
 
-ggplot(pred_FL_RM, aes(x=y_new))+geom_density()
+ggplot(pred_FL_RM, aes(x=y_new))+geom_density()+theme_minimal()
 
@@
 
-ggplot(pred_FL_NR, aes(x=y_new))+geom_density()
+ggplot(pred_FL_NR, aes(x=y_new))+geom_density()+theme_minimal()
 
@@
 ```
+
 Model 2 looks at Florida on day 7, with the number of positive cases being 658 with the percentage of white residents being 5%.
@@
 
-ggplot(pred_FL_3, aes(x=y_new))+geom_density()
+ggplot(pred_FL_3, aes(x=y_new))+geom_density()+theme_minimal()
 
@@
 ```
+
 Model 3 looks at Florida on day 7, with the number of positive cases being 658 with the percentage of white residents being 5%, and also classifies Florida as a purple state.
@@
 
-ggplot(pred_FL_complex, aes(x=y_new))+geom_density()
+ggplot(pred_FL_complex, aes(x=y_new))+geom_density()+theme_minimal()
 
@@
 ```
+
 Our final model predicts the same aspects as model 3.
@@
 ```
+
 The actual mean of interest in the term China Virus in Florida is 47.625! We can use this value to assess how closely our models predicted the interest to be.
@@
 
-COVID-19 Dataset: 
-One of the biggest weakness of this dataset is the fact there there is no designed standardized method for states to follow for data collection and reporting.
+**COVID-19 Data set:** 
+One of the biggest weakness of this data set is the fact there there is no designed standardized method for states to follow for data collection and reporting.
 For example, some states, like Oregon, provide the full set of numbers but others provide some or none of these numbers on an ongoing basis.
@@
 
-Google Trends: 
-The main downside to the Google Trends dataset is the method of the indexing that the platform uses.
+**Google Trends:** 
+The main downside to the Google Trends data set is the method of the indexing that the platform uses.
 Since each state is guaranteed to have a 100-level interest on their peak interest day the comparison from state to state becomes less meaningful.
@@
 
-Demographics & Political: 
-Overall, the demographics and political dataset is rather comprehensive and accurate.
+**Demographics & Political:** 
+Overall, the demographics and political data set is rather comprehensive and accurate.
 However, the biggest limitation arises with the State of Alaska.
-Since the State of Alaska reports results at the precinct or state level so there was no county-level data available and many datasets excluded the state.
+Since the State of Alaska reports results at the precinct or state level so there was no county-level data available and many data sets excluded the state.
 Therefore, demographic and election information for Alaska had to be manually entered.
@@
 For our models we used a Normal distribution which goes from 0 - 100, however, our final distributions turn our to be rather truncated with values going above and below 0 and 100 this causes us to have wider guesses.
-Also, when running a ppcheck on each of our models we saw that our resulting distribution wasn't a perfect normal as there were two visible bumps on each of the tail ends.
-These bumps would need further exploring, however, we assume them to be outliers within our data.
+Also, when running a pp check on each of our models we saw that our resulting distribution wasn't a perfect normal as there were two visible bumps on each of the tail ends.
+These bumps would need further exploring, however, we assume them to be outliars within our data.
 
@@
 
-We thank Alicia Johnson for not only providing us an aspect of our final dataset but also for helping us throughout the entirety of the project.
+We thank Alicia Johnson for not only providing us an aspect of our final data set but also for helping us throughout the entirety of the project.
 

### 2020-05-06 Final-Draft.Rmd
more proofing

@@
 
-## 4.5 Are our models strong?: Prediction & classification summaries
-
 \
@@
 
-### 5.1a 
 ```{r, message=FALSE, include=FALSE}
@@
   yrep = pred_1)
-```
 
-### 5.1b
-```{r, message=FALSE, include=FALSE}
 #Normal Regression
@@
   yrep = pred_2)
-```
 
-### 5.1c
-```{r, message=FALSE, include=FALSE}
 #Repeated Measures + Normal Regression
@@
   yrep = pred_3)
-```
 
-### 5.1d
-```{r message=FALSE, include=FALSE}
 #Longitudinal Model
@@
 
-## 5.3 Final Model
+## 5.4 Final Model
 

### 2020-05-06 Final-Draft.Rmd
knitting again
Update Final-Draft.Rmd

@@
 
+Before
+
 ### 5.2 Table
@@
 
-## 5.4 Final Model
-
 \
@@
 # 6.Conclusion
+
+As mentioned above we concluded model 3 to be our best model.
+That being said, looking at the model summary we see some interesting patterns arise.
+First off, we see that on average "China Virus" interest is actually a lot higher in blue  states than purple or red.
+In fact, for every percent increase we see that red states actually have almost a 4% decrease in "China Virus" interest as compared to blue states.
+In addition, our model shows that with every increase in percent white residents, "China Virus" interest increases by 1%.
+Model 3 also tells us that there doesn't seem to be much of a change when we consider a state's positive cases.
+Thus, what our model is essentially saying is that "China Virus" interest is a lot higher for blue states that have higher percent white populations.
+These conclusions were interesting to us because we did not expect states that are blue to have a higher interest in the term.
+However, in a way it makes sense as statistics show that blue states tend to have higher rates of political engagement which would make sense as to why they had more searches for the term after Trump's Tweet.
+
+```{r}
+head(data.frame(summary(model_3)),-2)
+```
 
@@
 
-In addition to our data limitation, a couple of limitations arose with our final models.
-For our models we used a Normal distribution which goes from 0 - 100, however, our final distributions turn our to be rather truncated with values going above and below 0 and 100 this causes us to have wider guesses.
-Also, when running a pp check on each of our models we saw that our resulting distribution wasn't a perfect normal as there were two visible bumps on each of the tail ends.
-These bumps would need further exploring, however, we assume them to be outliars within our data.
+In addition to our data limitation, our final model has clear limitations as well.
+Firstly, our model has a very high Mae, which is attributed to the fact that we expect the interest over time to be linear, but as seen in the visualizations there are states that do not behave linearly.
+We believe that using a Bayesian time series approach would resolve this limitation.
+
+Additionally, our variable of interest only goes from 0-100, but as seen above, our models predict far beyond that range meaning that our predictions are very wide.
+In other words, our models are not as certain about where the interests lies for each state.
+Also, when running a pp check on each of our models we saw that our resulting distribution wasn’t a perfect normal as there were two visible bumps on each of the tail ends.
+These bumps would need further exploring, however, we assume them to occur naturally specially at 0, as it is possible no one in the state looked for that term during that day.
 
@@
 Scrapping Twitter would allow us to analyze the actual emotional response to Trump's statement and incorporate a sentimental analysis.
-Additionally, in the future we hope to look at how the stay at home orders impacted "China Virus" interest as well.
+Additionally, in the future we hope to explore our analysis using Bayesian time series to better understand the variables that we chose.
 

### 2020-05-06 Final-Draft.Rmd
Update Final-Draft.Rmd

@@
 
-Before
-
 ### 5.2 Table
@@
 First off, we see that on average "China Virus" interest is actually a lot higher in blue states than purple or red.
-In fact, for every percent increase we see that red states actually have almost a 4% decrease in "China Virus" interest as compared to blue states.
+In fact, for every percent increase, we see that red states actually have almost a 4% decrease in "China Virus" interest as compared to blue states.
 In addition, our model shows that with every increase in percent white residents, "China Virus" interest increases by 1%.
@@
 These conclusions were interesting to us because we did not expect states that are blue to have a higher interest in the term.
-However, in a way it makes sense as statistics show that blue states tend to have higher rates of political engagement which would make sense as to why they had more searches for the term after Trump's Tweet.
+However, in a way, our results make sense as statistics show that blue states tend to have higher rates of political engagement which could explain why blue states had much more searches for the term after it was tweeted.
 

### 2020-05-06 Final-Draft.Rmd
final-Draft
Update Final-Draft.Rmd

@@
 ### 5.3a
-```{r, echo=FALSE, warning=FALSE}
+```{r, echo=FALSE, warning=FALSE, include=FALSE}
 ### For predicting one case 
-new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) 
+new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658) 
 set.seed(454)
@@
 pred_FL_RM <- data.frame(y_new = pred_FL_RM[-1])
+```
 
+```{r echo=FALSE, warning=FALSE}
 ggplot(pred_FL_RM, aes(x=y_new))+geom_density()+theme_minimal()
@@
 That said, we looked at Florida and created future "China Virus" interest predictions for it using each of our models.
-Our first model, predicts "'China Virus" interest for Florida on Day 7, with the positive rate being 11% and assumes the percentage of white residents is to be 5%.
+Our first model, predicts "'China Virus" interest for Florida on Day 7, with the amount of positive cases being 658 and assumes the percentage of white residents is to be 5%.
 Model 1 predicts the mean interest to be 45.27%, however, as one could see from the above visualization the interest could vary greatly, but there is a higher chance for it to be between 20% - 80%.
@@
 ### 5.3b
-```{r, echo=FALSE, warning=FALSE}
+
+```{r, echo=FALSE, warning=FALSE, include=FALSE}
 ### For predicting one case 
@@
 
+```
+
+```{r echo=FALSE, warning=FALSE}
 ggplot(pred_FL_NR, aes(x=y_new))+geom_density()+theme_minimal()
@@
 ### 5.3c
-```{r, echo=FALSE, warning=FALSE}
+```{r, echo=FALSE, warning=FALSE, include=FALSE}
 ### For predicting one case 
@@
 
+```
+
+```{r echo=FALSE, warning=FALSE}
 ggplot(pred_FL_3, aes(x=y_new))+geom_density()+theme_minimal()
@@
 ### 5.3d
-```{r, echo=FALSE, warning=FALSE}
+```{r, echo=FALSE, warning=FALSE, include=FALSE}
 ### For predicting one case 
@@
 
+```
+
+```{r echo=FALSE, warning=FALSE}
 ggplot(pred_FL_complex, aes(x=y_new))+geom_density()+theme_minimal()

### 2020-05-06 Final-Draft.Rmd
changes

@@
 
-```{r, message=FALSE, include=FALSE}
+```{r, message=FALSE, include=TRUE}
 g1 <- mcmc_dens(RM_model, pars = "sigma") + 
@@
 ### 4.2a MCMC Plots
+
+```{r}
+NR_model
+```
 
@@
 
-### 5.2 Table
-
 ```{r, echo=FALSE, warning=FALSE}
@@
 
-### 5.2a Model 3 is the best
+### 5.2 Model 3 is the best
 
@@
 ```{r}
-head(data.frame(summary(model_3)),-2)
+head(data.frame(summary(model_3)))
 ```

### 2020-05-06 Final-Draft.Rmd
final stuff

@@
 ```
+As we see in here, we see that as the days increase we see our China Virus Interest increasing by 0.9 percent.
+The percent white showed us that as percent white increases, the median China Virus Interest increases by 1.1%.
+And if a state is red, it will have -3.2 percentage points less compared to a state that is blue.
+And finally, interestingly the positive count has no influence on how much the percent white changes.
 
@@
 
+Also as seen in Model2, we see that our Covid-related variable, positive does not show any effect on how many people look up the term.
+But political differences such as state color show us that red states tend to have the lowest interest while purple and blue states tend to have the highest interest.
+This is in par with the statistics that show that democrats tend to have a higher political engagement.
+Finally, after Trump mentioned "China Virus" the interest of the term saw a significant increase 1.1 per Day closer to when Trump held his press conference.
+
 ```{r}
